### 2017-11-27 includes/abstract.tex
Initial paper commit.

\begin{abstract}

    Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and practically useful. Moreover a standard input language, SMT-LIB, has been developed, and many mature solvers support it. In this paper we present StringFuzz, a fuzzer and problem generator for string solvers. With it we analyse four mature string solvers: Z3str3, Norn, CVC4, and ABC. We use it to craft inputs that elicit poor performance in Z3str3 and CVC4, and present algorithmic improvements to mitigate it. Finally, we present several minor bugs in Z3str3 that were exposed by StringFuzz.

\end{abstract}

### 2018-01-05 includes/abstract.tex
Adjusting the abstract.

@@
 Moreover a standard input language, SMT-LIB, has been developed, and many mature solvers support it.
-In this paper we present StringFuzz, a fuzzer and problem generator for string solvers.
+In this paper we present StringFuzz: a fuzzer and SMT-LIB problem generator for string solvers.
 With it we analyse four mature string solvers: Z3str3, Norn, CVC4, and ABC.
-We use it to craft inputs that elicit poor performance in Z3str3 and CVC4, and present algorithmic improvements to mitigate it.
-Finally, we present several minor bugs in Z3str3 that were exposed by StringFuzz.
+We use it to craft inputs that elicit poor performance in Z3str3 and CVC4, and provide algorithmic analyses of the causes of the performance degradations.
+Finally, we present several minor bugs in Z3str3 that were exposed by StringFuzz, to justify its further use by other solver authors to likewise improve their solvers.
 

### 2018-01-05 includes/abstract.tex
Added paragraph stubs.

--- 2017-11-27 includes/abstract.tex
@@
 
-    Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and practically useful.
-Moreover a standard input language, SMT-LIB, has been developed, and many mature solvers support it.
-In this paper we present StringFuzz, a fuzzer and problem generator for string solvers.
-With it we analyse four mature string solvers: Z3str3, Norn, CVC4, and ABC.
-We use it to craft inputs that elicit poor performance in Z3str3 and CVC4, and present algorithmic improvements to mitigate it.
-Finally, we present several minor bugs in Z3str3 that were exposed by StringFuzz.
+    In this paper we present StringFuzz: an SMT-LIB problem fuzzer and generator for string solvers.
+With it we analyse \numSolvers{} mature string solvers: \theSolvers{}.
+We use it to craft inputs that elicit poor performance in Z3str3 and CVC4, and provide analyses of the causes of the performance degradations.
+Our experimental data suggest that there are classes of problems that will always be hard for Z3str3 and easy for CVC4, and vice versa, due to the limitations of the core algorithms implemented by those solvers.
+We also present several minor bugs in Z3str3 that were exposed by StringFuzz.
+Finally, we provide a rich repository of problems in SMT-LIB format, generated both by StringFuzz and by hand, to encourage other solver authors to likewise improve their solvers.
 

### 2018-01-05 includes/analysis.tex
Added paragraph stubs.

\section{Experiments}

    Here we present instances we generated, and our empirical results.

    \subsection{Concats-Extracts}

        Here we describe the problem. CVC4 did poorly. Z3str3 did well.

    \subsection{Regex Suite}

        Here we describe the problem. CVC4 did poorly. Z3str3 did well.

    \subsection{Lazy-Hard}

        Here we describe the problem. CVC4 did poorly. Z3str3 did well.

    \subsection{Eager-Hard}

        Here we describe the problem. CVC4 did well. Z3str3 did poorly.

\section{Analysis}

    Here we talk about Lazy-Hard and Eager-Hard, and how the algorithms of CVC4 and Z3str3 differ, eliciting the observed behaviour.

    \subsection{Lazy-Hard}

        Here is why CVC4 does poorly and Z3str3 does well.

    \subsection{Eager-Hard}

        Here is why CVC4 does well and Z3str3 does poorly.

### 2018-01-05 includes/introduction.tex
Added paragraph stubs.

\section{Introduction}

    Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and practically useful.

    Moreover a standard input language, SMT-LIB, has been developed, and many mature solvers support it.

### 2018-01-05 includes/problems.tex
Added paragraph stubs.

\section{Problem Suites}

    \subsection{StringFuzz-Generated}

        Here we describe the StringFuzz-generated suite.

    \subsection{StringFuzz-Transformed}

        Here we describe the StringFuzz-transformed suite.

    \subsection{Unit Tests}

        Here we describe the unit test suite.

### 2018-01-05 includes/stringfuzz.tex
Added paragraph stubs.

\section{StringFuzz}

    Here we present StringFuzz.

    \subsection{Generators}

        Here we describe our generators (concats, overlaps, etc.).

    \subsection{Transformers}

        Here we describe our transformers (graft, fuzz, etc.).

    \subsection{Utilities}

        Here we describe our utilities (stringstats).

### 2018-01-11 includes/abstract.tex
Writing sections in paper.

@@
 
-    In this paper we present StringFuzz: an SMT-LIB problem fuzzer and generator for string solvers.
+    In this paper we present \fuzzer{}: an \smt{} problem fuzzer and generator for string solvers.
 With it we analyse \numSolvers{} mature string solvers: \theSolvers{}.
-We use it to craft inputs that elicit poor performance in Z3str3 and CVC4, and provide analyses of the causes of the performance degradations.
-Our experimental data suggest that there are classes of problems that will always be hard for Z3str3 and easy for CVC4, and vice versa, due to the limitations of the core algorithms implemented by those solvers.
-We also present several minor bugs in Z3str3 that were exposed by StringFuzz.
-Finally, we provide a rich repository of problems in SMT-LIB format, generated both by StringFuzz and by hand, to encourage other solver authors to likewise improve their solvers.
+We use it to craft inputs that elicit poor performance in \us{} and \cvc{}, and provide analyses of the causes of the performance degradations.
+Our experimental data suggest that there are classes of problems that will always be hard for \us{} and easy for \cvc{}, and vice versa, due to the limitations of the core algorithms implemented by those solvers.
+We also present several minor bugs in \us{} that were exposed by \fuzzer{}.
+Finally, we provide a rich repository of problems in \smt{} format, generated both by \fuzzer{} and by hand, to encourage other solver authors to likewise improve their solvers.
 

### 2018-01-11 includes/analysis.tex
Added section about partial order eqc comparison solution.
Writing sections in paper.

@@
 
-    Here we present instances we generated, and our empirical results.
+    Here we present two particular sets of problems generated by \fuzzer{}: Eager-Hard and Lazy-Hard.
+These two problem sets were unique in their ability to elicit poor performance in one solver, but not another.
+Full details of test scripts, configurations, and problems that were used in the experiment can be found in the Appendix.
+
+    \textbf{TODO:}
+
+    \begin{enumerate}
+        \item supply machine environment description
+        \item supply install scripts that produce trace builds
+        \item supply test scripts that invoke the solvers and produce traces
+    \end{enumerate}
+
+\section{Results}
+
+    \subsection{Performance on Lazy-Hard}
+
+        On this problem set \cvc{} did poorly, but \us{} did well. The graphs in figure X show the performance results for both solvers.
+
+        \cvc{} showed the following behaviour in its log file:
+
+        \begin{enumerate}
+            \item Loads all facts
+            \item Flattens concats
+            \item Computes equivalence classes
+            \item Discovers conflict early
+                {\scriptsize\begin{verbatim}
+CONFLICT: Eq engine conflict : (and (= "woof" (str.++ "woof" lsym_5 lsym_5 lsym_5 lsym_5
+lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5)) (= "" lsym_5)
+(= "" var3) (= "" var5) (= "" var7) (= "" var9) (= "" var11) (= "" var13) (= "" var15)
+(= "" var17) (= "" var19) (= "" var21) (= "" var23) (= "" var25) (= "" var27) (= "" var29)
+(= "" var30) (= (str.++ "woof" var3 var5 var7 var9 var11 var13 var15 var17 var19 var21
+var23 var25 var27 var29 var30) (str.++ "meow" var43 var45 var47 var49 var51 var53 var55
+var57 var59 var61 var63 var65 var67 var69 var70)) (= "" var43) (= "" var45) (= "" var47)
+(= "" var49) (= "" var51) (= "" var53) (= "" var55) (= "" var57) (= "" var59) (= "" var61)
+(= "" var63) (= "" var65) (= "" var67) (= "" var69) (= "" var70) (= "meow" (str.++ "meow"
+lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5 lsym_5
+lsym_5 lsym_5)))
+                \end{verbatim}}
+            \item Gets caught doing some sort of check
+            \item Infers inequality
+        \end{enumerate}
+
+        \us{} showed the following behaviour in its log file:
+
+        \begin{enumerate}
+            \item loads all facts
+            \item immediately spots inconsistency:
+                {\scriptsize\begin{verbatim}
+-------- [str] new_eq_check ../src/smt/theory_str.cpp:1864 ---------
+checking whether (str.++ "woof" var2) and (str.++ "meow" var42) can be equal
+------------------------------------------------
+-------- [str] new_eq_check ../src/smt/theory_str.cpp:1867 ---------
+inconsistency detected: (str.++ "woof" var2) cannot be equal to (str.++ "meow" var42)
+------------------------------------------------
+-------- [str] assert_axiom ../src/smt/theory_str.cpp:179 ---------
+asserting (not (= (str.++ "woof" var2) (str.++ "meow" var42)))
+------------------------------------------------
+                \end{verbatim}}
+        \end{enumerate}
+
+        \textbf{TODO:}
+
+        \begin{enumerate}
+            \item \us{} cactus plot
+            \item \cvc{} cactus plot
+            \item comparison plot
+        \end{enumerate}
+
+    \subsection{Eager-Hard}
+
+        On this problem set \cvc{} did well, but \us{} did poorly. The graphs in figure X show the performance results for both solvers.
+
+        \cvc{} showed the following behaviour in its log file:
+
+        \begin{enumerate}
+            \item Loads all facts
+            \item Flattens concats
+            \item Computes equivalence classes
+            \item Finds solution
+        \end{enumerate}
+
+        \us{} showed the following behaviour in its log file:
+
+        \begin{enumerate}
+            \item Loads all facts
+            \item Tries assigning solution by "dragging" it across the variables
+            \item Creates a ton of equivalence classes
+            \item Gets caught comparing equivalence classes
+            \item Finds solution
+        \end{enumerate}
+
+        \textbf{TODO:}
+
+        \begin{enumerate}
+            \item \us{} cactus plot
+            \item \cvc{} cactus plot
+            \item comparison plot
+        \end{enumerate}
 
@@
 
-        Here we describe the problem. CVC4 did poorly. Z3str3 did well.
+        No data on this yet.
 
@@
 
-        Here we describe the problem. CVC4 did poorly. Z3str3 did well.
+        No data on this yet.
+
+\section{Analysis}
+
+    This section presents our analysis of the observed behaviour of \cvc{} and \us{} on Lazy-Hard and Eager-Hard problems.
 
@@
 
-        Here we describe the problem. CVC4 did poorly. Z3str3 did well.
+        Here is why \cvc{} does poorly and \us{} does well.
 
@@
 
-        Here we describe the problem. CVC4 did well. Z3str3 did poorly.
+        Here is why \cvc{} does well and \us{} does poorly.
 
-\section{Analysis}
+\section{\us{} Recommendation}
 
-    Here we talk about Lazy-Hard and Eager-Hard, and how the algorithms of CVC4 and Z3str3 differ, eliciting the observed behaviour.
+    This section outlines a change for \us{}, which we believe will improve its performance on the Eager-Hard problem set and similar problems.
+We recommend a partial order treatment of equivalence class comparisons.
+First, we describe a partial order of equivalence classes.
+Then, we use it in equivalence class comparisons and more closely approximate equality between them.
 
-    \subsection{Lazy-Hard}
+    \textbf{TODO:}
 
-        Here is why CVC4 does poorly and Z3str3 does well.
-
-    \subsection{Eager-Hard}
-
-        Here is why CVC4 does well and Z3str3 does poorly.
+    \begin{enumerate}
+        \item definition of partial order
+        \item definition of current class relation
+        \item definition of class relation under partial order
+    \end{enumerate}

### 2018-01-11 includes/introduction.tex
Writing sections in paper.

@@
     Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and practically useful.
+Moreover a standard input language, \smt{} (versions 2, 2.1, and 2.5), has been developed and many mature solvers support it.
 
-    Moreover a standard input language, SMT-LIB, has been developed, and many mature solvers support it.
+    \subsection{Prior Work}
+
+        Other fuzzers exist, but none of them support the theory of strings. We found these:
+
+        \begin{itemize}
+            \item http://fmv.jku.at/ddsmt/
+            \item http://fmv.jku.at/fuzzsmtbv/
+            \item http://fmv.jku.at/fuzzsmt/
+            \item http://fmv.jku.at/deltasmt/
+            \item http://fmv.jku.at/votesmt/
+            \item http://www.verit-solver.org/papers/smt2015.pdf
+            \item http://smt2015.csl.sri.com/wp-content/uploads/2015/07/smt2015-slides-deharbe.pdf
+        \end{itemize}
+
+    \subsection{Contributions}
+
+        In this paper, we present the following contributions:
+
+        \begin{itemize}
+            \item StringFuzzG, a generator of \smt{} string problems
+            \item StringFuzzX, a transformer of \smt{} string problems
+            \item Experiments that show evidence of poor performance in \us{} and \cvc{}
+            \item A recommended fix to \us{} that alleviates the poor performance
+            \item A suite of \smt{} problems
+        \end{itemize}
+
+        In the following sections, we elaborate on each of these items.

### 2018-01-11 includes/problems.tex
Writing sections in paper.

@@
 
-    \subsection{StringFuzz-Generated}
+    Along with this paper we present several suites of ready-made problems produced by StringFuzz. These suites can be found on \problemRepo{}.
 
-        Here we describe the StringFuzz-generated suite.
+    \subsection{\fuzzer{}-Generated}
 
-    \subsection{StringFuzz-Transformed}
+        This suite contains the following problem sets:
 
-        Here we describe the StringFuzz-transformed suite.
+        \begin{itemize}
+            \item Lengths
+            \item Lengths-Concats
+            \item Concats
+            \item Concats-Extracts
+            \item Overlaps
+            \item Regex
+            \item Many-Regexes
+            \item Regex-Deep
+            \item Regex-Pair
+            \item Regex-Lengths
+            \item Random??
+        \end{itemize}
+
+        Most of these problem sets either have a dedicated generator in \generator{}, or are variations of one.
+While it is likely that some of the pre-made suites will be immediately useful in analysing a solver, we also found that mass randomisation was helpful in finding some bugs, and we encourage this pattern as well.
+\generator{} is designed to be used in an exploratory fashion, and the following usage has helped us in our own experiments:
+
+\begin{verbatim}
+while true; do stringfuzzg --random regex | z3str3 -in; done
+\end{verbatim}
+
+    \subsection{\fuzzer{}-Transformed}
+
+        This suite contains the following problem sets:
+
+        \begin{itemize}
+            \item Amazon??
+            \item Regex??
+        \end{itemize}
+
+        Most of these problem sets were generated by using one root problem and transforming it with \transformer{} into many similar problems.
 
@@
 
-        Here we describe the unit test suite.
+        This suite covers corner cases of solver behaviour. We have used the instances in this suite to find bugs in \us{}.
+
+    \subsection{Results}
+
+        This section describes the bugs in \us{} that were discovered (and subsequently fixed) by testing it with the \fuzzer{} problem suites.
+
+        \begin{enumerate}
+            \item length lookup using eqc root
+            \item length-testing bug
+        \end{enumerate}

### 2018-01-11 includes/stringfuzz.tex
Writing sections in paper.

@@
-\section{StringFuzz}
+\section{\fuzzer{}}
 
-    Here we present StringFuzz.
+    This section presents \fuzzer{}.
+\fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyse \smt{} string problems.
+Its source code repository is available at \sourceRepo{}.
+It can either be installed from source, or from the Python PIP package repository.
 
-    \subsection{Generators}
+    \subsection{Generators: \generator{}}
 
-        Here we describe our generators (concats, overlaps, etc.).
+        \generator{} is available as a command-line tool, \texttt{stringfuzzg}. It supports several generators and options that control its output. The generators it implements are:
 
-    \subsection{Transformers}
+        \begin{itemize}
+            \item concats
+            \item lengths
+            \item overlaps
+            \item regex
+            \item random-text
+        \end{itemize}
 
-        Here we describe our transformers (graft, fuzz, etc.).
+    \subsection{Transformers: \transformer{}}
+
+        \transformer is available as a command-line tool, \texttt{stringfuzzx}. It supports several transformers and options that control its output and input. The transformers it implements are:
+
+        \begin{itemize}
+            \item concats
+            \item lengths
+            \item overlaps
+            \item regex
+            \item random-text
+        \end{itemize}
 
@@
 
-        Here we describe our utilities (stringstats).
+        Some utilities are also provided with \fuzzer{}. They are: \texttt{stringstats}, \texttt{stringmerge}, \texttt{smtparse}, and \texttt{smtscan}.
+
+        \begin{description}
+
+            \item[\texttt{stringstats}] \hfill \\ \\
+                This tool takes as input an \smt{} problem, and outputs its properties. The properties are:
+
+                \begin{itemize}
+                    \item number of string variables
+                    \item number of string literals
+                    \item max/median syntactic depth of expressions
+                    \item max/median length of literals
+                \end{itemize}
+
+                \hfill
+
+            \item[\texttt{stringmerge}] \hfill \\ \\
+                This tool takes as input two \smt{} problems and combines them into one problem.
+
+        \end{description}
+
+    \subsection{Architecture}
+
+        Should I describe its architecture?

### 2018-01-14 includes/experiment.tex
Applying first round of feedback.

\section{Experiments}

    Here we present two particular sets of problems generated by \fuzzer{}: Eager-Hard and Lazy-Hard. These two problem sets were unique in their ability to elicit poor performance in one solver, but not another. Full details of test scripts, configurations, and problems that were used in the experiment can be found in the Appendix.

    % TODO:
    % - supply machine environment description
    % - supply install scripts that produce trace builds
    % - supply test scripts that invoke the solvers and produce traces

    \subsection{Data}

        \subsubsection{Performance on Lazy-Hard}

            On this problem set \cvc{} did poorly, but \us{} did well. The graphs in figure X show the performance results for both solvers. We produce and analyse the execution trace files both solvers' execution on the problem set, and present them in the Appendix.

            The \cvc{} trace file indicates that it performs the following operations:

            \begin{enumerate}
                \item Loads all facts into its database.
                \item Flattens binary concatenations into n-ary concatenations.
                \item Computes equivalence classes for strings and integers.
            \end{enumerate}

            At this stage it discovers that there is a conflict in one of its equivalence classes, as shown in figure X. After discovering the conflict, the rest of the trace is filled with apparently the same operation repeated hundreds of thousands of times. After this operation is finished, \cvc{} recalls the earlier conflict and returns \texttt{unsat}.

            \us{} showed different behaviour on this problem set. It follows a similar process as \cvc{}, except it does not flatten concatenations. In contrast to \cvc{}, \us{} immediately returns \texttt{unsat} as soon as it verifies consistency of equivalence classes as it constructs them, as shown in figure X.

            {\scriptsize\begin{verbatim}
-------- [str] new_eq_check ../src/smt/theory_str.cpp:1864 ---------
checking whether (str.++ "woof" var2) and (str.++ "meow" var42) can be equal
------------------------------------------------
-------- [str] new_eq_check ../src/smt/theory_str.cpp:1867 ---------
inconsistency detected: (str.++ "woof" var2) cannot be equal to (str.++ "meow" var42)
------------------------------------------------
-------- [str] assert_axiom ../src/smt/theory_str.cpp:179 ---------
asserting (not (= (str.++ "woof" var2) (str.++ "meow" var42)))
------------------------------------------------
            \end{verbatim}}

            {\scriptsize\begin{verbatim}
CONFLICT: Eq engine conflict : (and
(= "woof" (str.++ "woof" lsym_5 ... lsym_5))
(= "" lsym_5)
(= "" var3) ... (= "" var30)
(= (str.++ "woof" var3 ... var30) (str.++ "meow" var43 ... var70))
(= "" var43) ... (= "" var70)
(= "meow" (str.++ "meow" lsym_5 ... lsym_5)))
            \end{verbatim}}

            % TODO:
            % - \us{} cactus plot
            % - \cvc{} cactus plot
            % - comparison plot

        \subsubsection{Performance on Eager-Hard}

            On this problem set \cvc{} did well, but \us{} did poorly. The graphs in figure X show the performance results for both solvers. We produce and analyse the execution trace files both solvers' execution on the problem set, and present them in the Appendix.

            Both solvers exhibit similar patterns in their trace files. They differ in their strategies for assigning possible satisfying assignments. \cvc{} assigns the first variable to a constant and all other variables to the empty string. \us{} however seems to ``drag'' the constant across the equation, splitting its characters among the variables in it.

            % TODO:
            % - \us{} cactus plot
            % - \cvc{} cactus plot
            % - comparison plot

        \subsubsection{Concats-Extracts}

            No data on this yet.

    \subsection{Analysis}

        This section presents our analysis of the observed behaviour of \cvc{} and \us{} on Lazy-Hard and Eager-Hard problems.

        On Lazy-Hard, \cvc{} does poorly and \us{} does well because ...

        On Eager-Hard, \cvc{} does well and \us{} does poorly because ...

### 2018-01-14 includes/introduction.tex
Applying first round of feedback.

--- 2018-01-05 includes/introduction.tex
@@
     Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and practically useful.
+Moreover a standard input language, \smt{}, has been developed and many mature solvers support it.
 
-    Moreover a standard input language, SMT-LIB, has been developed, and many mature solvers support it.
+    In this paper, we present the following contributions:
+
+    \begin{enumerate}
+        \item StringFuzzG and StringFuzzX: a generator and transformer of \smt{} string and regex problems.
+        \item Experiments on generated inputs that show evidence of poor performance in \us{} and \cvc{}.
+        \item A recommended fix to \us{} that alleviates the poor performance.
+        \item A large suite of \smt{} string and regex problems we generated with \fuzzer{}.
+    \end{enumerate}

### 2018-01-14 includes/prior.tex
Applying first round of feedback.

\section{Prior Work}

    There are several fuzzers and problem generators currently available, but none of them support string or regex generation or transformation. For example the FuzzSMT [ref] tool generates \smt{} problems with bit vectors and arrays, but does not support strings or regexes. The SMTpp [ref] tool preprocesses and simplifies problems, but does not generate new ones or fuzz existing ones.

% FuzzSMT: http://fmv.jku.at/papers/BrummayerBiere-SMT09.pdf
% SMTpp: http://www.verit-solver.org/papers/smt2015.pdf

### 2018-01-14 includes/problems.tex
Applying first round of feedback.

@@
 
-    Along with this paper we present several suites of ready-made problems produced by StringFuzz. These suites can be found on \problemRepo{}.
+    We generated several suites of string and regex problems using \fuzzer{}, and they are available at \problemRepo{}. They are described in more detail below.
 
@@
 While it is likely that some of the pre-made suites will be immediately useful in analysing a solver, we also found that mass randomisation was helpful in finding some bugs, and we encourage this pattern as well.
-\generator{} is designed to be used in an exploratory fashion, and the following usage has helped us in our own experiments:
+\generator{} is designed to be used in an exploratory fashion.
+For example the following usage has helped us find bugs in \us{}:
 
@@
 
-    \subsection{Results}
+    \subsection{Bugs Found}
 

### 2018-01-14 includes/recommendation.tex
Applying first round of feedback.

--- 2018-01-05 includes/analysis.tex
@@
-\section{Experiments}
+\section{\us{} Recommendation}
 
-    Here we present instances we generated, and our empirical results.
+    This section outlines a change for \us{}, which we believe will improve its performance on the Eager-Hard problem set and similar problems.
+We recommend a partial order treatment of equivalence class comparisons.
+First, we describe a partial order of equivalence classes.
+Then, we use it in equivalence class comparisons and more closely approximate equality between them.
 
-    \subsection{Concats-Extracts}
-
-        Here we describe the problem. CVC4 did poorly. Z3str3 did well.
-
-    \subsection{Regex Suite}
-
-        Here we describe the problem. CVC4 did poorly. Z3str3 did well.
-
-    \subsection{Lazy-Hard}
-
-        Here we describe the problem. CVC4 did poorly. Z3str3 did well.
-
-    \subsection{Eager-Hard}
-
-        Here we describe the problem. CVC4 did well. Z3str3 did poorly.
-
-\section{Analysis}
-
-    Here we talk about Lazy-Hard and Eager-Hard, and how the algorithms of CVC4 and Z3str3 differ, eliciting the observed behaviour.
-
-    \subsection{Lazy-Hard}
-
-        Here is why CVC4 does poorly and Z3str3 does well.
-
-    \subsection{Eager-Hard}
-
-        Here is why CVC4 does well and Z3str3 does poorly.
+    % TODO:
+    % - definition of partial order
+    % - definition of current class relation
+    % - definition of class relation under partial order

### 2018-01-14 includes/stringfuzz.tex
Applying first round of feedback.

@@
 
-    This section presents \fuzzer{}.
+    This section describes the fuzzer \fuzzer{}.
 \fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyse \smt{} string problems.
@@
 
-    \subsection{Generators: \generator{}}
+    The \fuzzer{} code is organised to be easily extended with more generators and transformers.
+It is also implemented in the spirit of a Unix "filter", to be easily integrated into other tools.
+For example, the outputs of generators can be piped directly into transformers, and transformers can be chained to produce a tuned stream of challenging inputs to a solver.
 
-        \generator{} is available as a command-line tool, \texttt{stringfuzzg}. It supports several generators and options that control its output. The generators it implements are:
+    Below are descriptions of the tools that come with \fuzzer{}:
+
+    \begin{description}
+
+        \item[\texttt{stringfuzzg}] \hfill \\
+            This tool generates \smt{} problems. It supports several generators and options that control its output. The generators it implements are:
 
@@
 
-    \subsection{Transformers: \transformer{}}
-
-        \transformer is available as a command-line tool, \texttt{stringfuzzx}. It supports several transformers and options that control its output and input. The transformers it implements are:
+        \item[\texttt{stringfuzzx}] \hfill \\
+            This tool transforms \smt{} problems.. It supports several transformers and options that control its output and input. The transformers it implements are:
 
             \begin{itemize}
-            \item concats
-            \item lengths
-            \item overlaps
-            \item regex
-            \item random-text
+                \item fuzz
+                \item graft
+                \item multiply
+                \item nop
+                \item reverse
+                \item rotate
+                \item translate
+                \item unprintable
             \end{itemize}
 
-    \subsection{Utilities}
-
-        Some utilities are also provided with \fuzzer{}. They are: \texttt{stringstats}, \texttt{stringmerge}, \texttt{smtparse}, and \texttt{smtscan}.
-
-        \begin{description}
-
-            \item[\texttt{stringstats}] \hfill \\ \\
+        \item[\texttt{stringstats}] \hfill \\
             This tool takes as input an \smt{} problem, and outputs its properties. The properties are:
@@
 
-            \item[\texttt{stringmerge}] \hfill \\ \\
+        \item[\texttt{stringmerge}] \hfill \\
             This tool takes as input two \smt{} problems and combines them into one problem.
@@
     \end{description}
-
-    \subsection{Architecture}
-
-        Should I describe its architecture?

### 2018-01-15 includes/experiment.tex
Revising paper. Adding figures and tables.

@@
             On this problem set \cvc{} did poorly, but \us{} did well.
-The graphs in figure X show the performance results for both solvers.
-We produce and analyse the execution trace files both solvers' execution on the problem set, and present them in the Appendix.
+The graphs in Figures~\ref{fig:z3str3-lazy-hard} and ~\ref{fig:cvc4-lazy-hard} show the performance results for both solvers.
+We produce and analyse the execution trace files both solvers' execution on the problem set.
+
+            \begin{figure}[h]
+                \begin{subfigure}{.5\textwidth}
+                    \includegraphics[width=\textwidth]{data/graphs/z3str3-lazy-hard.png}
+                    \caption{Performance of \us{} on Lazy-Hard}
+                    \label{fig:z3str3-lazy-hard}
+                \end{subfigure}
+                \begin{subfigure}{.5\textwidth}
+                    \includegraphics[width=\textwidth]{data/graphs/cvc4-lazy-hard.png}
+                    \caption{Performance of \cvc{} on Lazy-Hard}
+                    \label{fig:cvc4-lazy-hard}
+                \end{subfigure}
+            \end{figure}
 
@@
 
-            At this stage it discovers that there is a conflict in one of its equivalence classes, as shown in figure X.
+            At this stage it discovers that there is a conflict in one of its equivalence classes, as shown in Figure~\ref{fig:cvc4-conflict}.
 After discovering the conflict, the rest of the trace is filled with apparently the same operation repeated hundreds of thousands of times.
@@
 It follows a similar process as \cvc{}, except it does not flatten concatenations.
-In contrast to \cvc{}, \us{} immediately returns \texttt{unsat} as soon as it verifies consistency of equivalence classes as it constructs them, as shown in figure X.
+In contrast to \cvc{}, \us{} immediately returns \texttt{unsat} as soon as it verifies consistency of equivalence classes as it constructs them, as shown in Figure~\ref{fig:z3str3-conflict}.
 
+            \begin{figure}[h]
                 {\scriptsize\begin{verbatim}
@@
 asserting (not (= (str.++ "woof" var2) (str.++ "meow" var42)))
-------------------------------------------------
-            \end{verbatim}}
+------------------------------------------------\end{verbatim}}
+                \caption{Evidence of \us{} detecting conflict}
+                \label{fig:z3str3-conflict}
+            \end{figure}
 
+            \begin{figure}[h]
                 {\scriptsize\begin{verbatim}
@@
 (= "" var43) ... (= "" var70)
-(= "meow" (str.++ "meow" lsym_5 ... lsym_5)))
-            \end{verbatim}}
+(= "meow" (str.++ "meow" lsym_5 ... lsym_5)))\end{verbatim}}
+                \caption{Evidence of \cvc{} detecting conflict}
+                \label{fig:cvc4-conflict}
+            \end{figure}
 
@@
             On this problem set \cvc{} did well, but \us{} did poorly.
-The graphs in figure X show the performance results for both solvers.
+The graphs in Figures~\ref{fig:z3str3-eager-hard} and ~\ref{fig:cvc4-eager-hard} show the performance results for both solvers.
 We produce and analyse the execution trace files both solvers' execution on the problem set, and present them in the Appendix.
+
+            \begin{figure}[h]
+                \begin{subfigure}{.5\textwidth}
+                    \includegraphics[width=\textwidth]{data/graphs/z3str3-eager-hard.png}
+                    \caption{Performance of \us{} on Eager-Hard}
+                    \label{fig:z3str3-eager-hard}
+                \end{subfigure}
+                \begin{subfigure}{.5\textwidth}
+                    \includegraphics[width=\textwidth]{data/graphs/cvc4-eager-hard.png}
+                    \caption{Performance of \cvc{} on Eager-Hard}
+                    \label{fig:cvc4-eager-hard}
+                \end{subfigure}
+            \end{figure}
 

### 2018-01-15 includes/introduction.tex
Revising paper. Adding figures and tables.

@@
     \begin{enumerate}
-        \item StringFuzzG and StringFuzzX: a generator and transformer of \smt{} string and regex problems.
-        \item Experiments on generated inputs that show evidence of poor performance in \us{} and \cvc{}.
+        \item \fuzzer{}: a fuzzer of \smt{} string and regex problems.
+        \item Generated inputs that elicit poor performance in \us{} and \cvc{}.
         \item A recommended fix to \us{} that alleviates the poor performance.

### 2018-01-15 includes/problems.tex
Revising paper. Adding figures and tables.

@@
 
-    \subsection{\fuzzer{}-Generated}
+    \subsubsection{\fuzzer{}-Generated}
 
-        This suite contains the following problem sets:
+        This suite contains the following problem sets: \\
 
-        \begin{itemize}
-            \item Lengths
-            \item Lengths-Concats
-            \item Concats
-            \item Concats-Extracts
-            \item Overlaps
-            \item Regex
-            \item Many-Regexes
-            \item Regex-Deep
-            \item Regex-Pair
-            \item Regex-Lengths
-            \item Random??
-        \end{itemize}
+        \begin{tabular}{|c|c|}
+            \hline
+            \textbf{Name}    & \textbf{Description} \\ \hline
+            Lengths          & \\ \hline
+            Lengths-Concats  & \\ \hline
+            Concats          & \\ \hline
+            Concats-Extracts & \\ \hline
+            Overlaps         & \\ \hline
+            Regex            & \\ \hline
+            Many-Regexes     & \\ \hline
+            Regex-Deep       & \\ \hline
+            Regex-Pair       & \\ \hline
+            Regex-Lengths    & \\ \hline
+            Random??         & \\ \hline
+        \end{tabular}
+
+        \hfill \\
 
@@
 \generator{} is designed to be used in an exploratory fashion.
-For example the following usage has helped us find bugs in \us{}:
+For example the following usage has helped us find bugs in \us{}: \\
 
-\begin{verbatim}
-while true; do stringfuzzg --random regex | z3str3 -in; done
-\end{verbatim}
+        {\scriptsize\begin{verbatim}
+while true; do stringfuzzg --random regex | z3str3 -in; done\end{verbatim}}
 
-    \subsection{\fuzzer{}-Transformed}
+    \subsubsection{\fuzzer{}-Transformed}
 
-        This suite contains the following problem sets:
+        This suite contains the following problem sets: \\
 
-        \begin{itemize}
-            \item Amazon??
-            \item Regex??
-        \end{itemize}
+        \begin{tabular}{|c|c|}
+            \hline
+            \textbf{Name} & \textbf{Description} \\ \hline
+            Amazon??      & \\ \hline
+            Regex??       & \\ \hline
+        \end{tabular}
+
+        \hfill \\
 
@@
 
-    \subsection{Unit Tests}
+    \subsubsection{Unit Tests}
 
@@
 
-        This section describes the bugs in \us{} that were discovered (and subsequently fixed) by testing it with the \fuzzer{} problem suites.
+        This section describes the bugs in \us{} that were discovered (and subsequently fixed) by testing it with the \fuzzer{} problem suites, as follows: \\
 
-        \begin{enumerate}
-            \item length lookup using eqc root
-            \item length-testing bug
-        \end{enumerate}
+        \begin{tabular}{|c|c|c|c|}
+            \hline
+            \textbf{Name} & \textbf{Description} & \textbf{Before Fix} & \textbf{After Fix} \\ \hline
+            length lookup  & & & \\ \hline
+            length-testing & & & \\ \hline
+        \end{tabular}

### 2018-01-15 includes/stringfuzz.tex
Revising paper. Adding figures and tables.

@@
 
-    This section describes the fuzzer \fuzzer{}.
+    This section describes the fuzzer \fuzzer{}, which generates new \smt{} problems or transforms existing ones.
 \fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyse \smt{} string problems.
@@
 
-    The \fuzzer{} code is organised to be easily extended with more generators and transformers.
-It is also implemented in the spirit of a Unix "filter", to be easily integrated into other tools.
+    The \fuzzer{} code is organised to be easily extended: all generators and transformers are independent modules.
+It is also implemented as a Unix "filter", to enable easy integration with other tools (including itself).
 For example, the outputs of generators can be piped directly into transformers, and transformers can be chained to produce a tuned stream of challenging inputs to a solver.
@@
         \item[\texttt{stringfuzzg}] \hfill \\
-            This tool generates \smt{} problems. It supports several generators and options that control its output. The generators it implements are:
+            This tool generates \smt{} problems. It supports several generators and options that control its output. The generators it implements are: \\
 
-            \begin{itemize}
-                \item concats
-                \item lengths
-                \item overlaps
-                \item regex
-                \item random-text
-            \end{itemize}
+            \begin{tabular}{|c|c|}
+                \hline
+                \textbf{Name} & \textbf{Description} \\ \hline
+                concats       & \\ \hline
+                lengths       & \\ \hline
+                overlaps      & \\ \hline
+                regex         & \\ \hline
+                random-text   & \\ \hline
+            \end{tabular}
+
+            \hfill \\
 
         \item[\texttt{stringfuzzx}] \hfill \\
-            This tool transforms \smt{} problems.. It supports several transformers and options that control its output and input. The transformers it implements are:
+            This tool transforms \smt{} problems.. It supports several transformers and options that control its output and input. The transformers it implements are:\\
 
-            \begin{itemize}
-                \item fuzz
-                \item graft
-                \item multiply
-                \item nop
-                \item reverse
-                \item rotate
-                \item translate
-                \item unprintable
-            \end{itemize}
+            \begin{tabular}{|c|c|}
+                \hline
+                \textbf{Name} & \textbf{Description} \\ \hline
+                fuzz          & \\ \hline
+                graft         & \\ \hline
+                multiply      & \\ \hline
+                nop           & \\ \hline
+                reverse       & \\ \hline
+                rotate        & \\ \hline
+                translate     & \\ \hline
+                unprintable   & \\ \hline
+            \end{tabular}
+
+            \hfill \\
 

### 2018-01-18 includes/abstract.tex
Applying paper feedback.

--- 2018-01-05 includes/abstract.tex
@@
 
-    Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and practically useful.
-Moreover a standard input language, SMT-LIB, has been developed, and many mature solvers support it.
-In this paper we present StringFuzz: a fuzzer and SMT-LIB problem generator for string solvers.
-With it we analyse four mature string solvers: Z3str3, Norn, CVC4, and ABC.
-We use it to craft inputs that elicit poor performance in Z3str3 and CVC4, and provide algorithmic analyses of the causes of the performance degradations.
-Finally, we present several minor bugs in Z3str3 that were exposed by StringFuzz, to justify its further use by other solver authors to likewise improve their solvers.
+    In this paper we present \fuzzer{}: an \smtlib{} problem fuzzer and generator for string solvers.
+We provide a rich repository of problems we generated with \fuzzer{} in \smt{} format.
+We also analyse \numSolvers{} mature string solvers: \theSolvers{}.
+We use \fuzzer{} to craft inputs that elicit poor performance in \us{} and \cvc{}, and analyse the causes of the performance degradations.
+We then describe an algorithm to mitigate the performance degradation in \us{}.
+Finally, we describe several bugs in \us{} that were exposed by \fuzzer{}.
 

### 2018-01-18 includes/experiment.tex
Applying paper feedback.

@@
 
-    Here we present two particular sets of problems generated by \fuzzer{}: Eager-Hard and Lazy-Hard.
+    Here we present two particular sets of problems generated by \fuzzer{}: \cHard{} and \zHard{}.
 These two problem sets were unique in their ability to elicit poor performance in one solver, but not another.
@@
 
-        \subsubsection{Performance on Lazy-Hard}
+        \subsubsection{Performance on \cHard{}}
 
             On this problem set \cvc{} did poorly, but \us{} did well.
-The graphs in Figures~\ref{fig:z3str3-lazy-hard} and ~\ref{fig:cvc4-lazy-hard} show the performance results for both solvers.
+The graphs in Figures~\ref{fig:z3str3-cvc4-hard} and ~\ref{fig:cvc4-cvc4-hard} show the performance results for both solvers.
 We produce and analyse the execution trace files both solvers' execution on the problem set.
@@
                 \begin{subfigure}{.5\textwidth}
-                    \includegraphics[width=\textwidth]{data/graphs/z3str3-lazy-hard.png}
-                    \caption{Performance of \us{} on Lazy-Hard}
-                    \label{fig:z3str3-lazy-hard}
+                    \includegraphics[width=\textwidth]{data/graphs/cvc4-cvc4-hard.png}
+                    \caption{Performance of \cvc{} on \cHard{}}
+                    \label{fig:cvc4-cvc4-hard}
                 \end{subfigure}
                 \begin{subfigure}{.5\textwidth}
-                    \includegraphics[width=\textwidth]{data/graphs/cvc4-lazy-hard.png}
-                    \caption{Performance of \cvc{} on Lazy-Hard}
-                    \label{fig:cvc4-lazy-hard}
+                    \includegraphics[width=\textwidth]{data/graphs/z3str3-cvc4-hard.png}
+                    \caption{Performance of \us{} on \cHard{}}
+                    \label{fig:z3str3-cvc4-hard}
                 \end{subfigure}
+                \caption{Results on \cHard}
+                \label{fig:cvc4-hard}
             \end{figure}
@@
 After this operation is finished, \cvc{} recalls the earlier conflict and returns \texttt{unsat}.
+
+            \begin{figure}[h]
+                {\scriptsize\begin{verbatim}
+CONFLICT: Eq engine conflict : (and
+(= "woof" (str.++ "woof" lsym_5 ... lsym_5))
+(= "" lsym_5)
+(= "" var3) ... (= "" var30)
+(= (str.++ "woof" var3 ... var30) (str.++ "meow" var43 ... var70))
+(= "" var43) ... (= "" var70)
+(= "meow" (str.++ "meow" lsym_5 ... lsym_5)))\end{verbatim}}
+                \caption{Evidence of \cvc{} detecting conflict}
+                \label{fig:cvc4-conflict}
+            \end{figure}
 
@@
 
-            \begin{figure}[h]
-                {\scriptsize\begin{verbatim}
-CONFLICT: Eq engine conflict : (and
-(= "woof" (str.++ "woof" lsym_5 ... lsym_5))
-(= "" lsym_5)
-(= "" var3) ... (= "" var30)
-(= (str.++ "woof" var3 ... var30) (str.++ "meow" var43 ... var70))
-(= "" var43) ... (= "" var70)
-(= "meow" (str.++ "meow" lsym_5 ... lsym_5)))\end{verbatim}}
-                \caption{Evidence of \cvc{} detecting conflict}
-                \label{fig:cvc4-conflict}
-            \end{figure}
-
             % TODO:
@@
 
-        \subsubsection{Performance on Eager-Hard}
+        \subsubsection{Performance on \zHard{}}
 
             On this problem set \cvc{} did well, but \us{} did poorly.
-The graphs in Figures~\ref{fig:z3str3-eager-hard} and ~\ref{fig:cvc4-eager-hard} show the performance results for both solvers.
+The graphs in Figures~\ref{fig:z3str3-z3str3-hard} and ~\ref{fig:cvc4-z3str3-hard} show the performance results for both solvers.
 We produce and analyse the execution trace files both solvers' execution on the problem set, and present them in the Appendix.
@@
                 \begin{subfigure}{.5\textwidth}
-                    \includegraphics[width=\textwidth]{data/graphs/z3str3-eager-hard.png}
-                    \caption{Performance of \us{} on Eager-Hard}
-                    \label{fig:z3str3-eager-hard}
+                    \includegraphics[width=\textwidth]{data/graphs/cvc4-z3str3-hard.png}
+                    \caption{Performance of \cvc{} on \zHard{}}
+                    \label{fig:cvc4-z3str3-hard}
                 \end{subfigure}
                 \begin{subfigure}{.5\textwidth}
-                    \includegraphics[width=\textwidth]{data/graphs/cvc4-eager-hard.png}
-                    \caption{Performance of \cvc{} on Eager-Hard}
-                    \label{fig:cvc4-eager-hard}
+                    \includegraphics[width=\textwidth]{data/graphs/z3str3-z3str3-hard.png}
+                    \caption{Performance of \us{} on \zHard{}}
+                    \label{fig:z3str3-z3str3-hard}
                 \end{subfigure}
+                \caption{Results on \zHard}
+                \label{fig:z3str3-hard}
             \end{figure}
@@
 
-        \subsubsection{Concats-Extracts}
+        \subsubsection{Performance Concats-Extracts}
 
-            No data on this yet.
+            \todo{}: No data on this yet.
 
@@
 
-        This section presents our analysis of the observed behaviour of \cvc{} and \us{} on Lazy-Hard and Eager-Hard problems.
+        This section presents our analysis of the observed behaviour of \cvc{} and \us{} on \cHard{} and \zHard{} problems.
 
-        On Lazy-Hard, \cvc{} does poorly and \us{} does well because ...
+        \todo{}: On \cHard{}, \cvc{} does poorly and \us{} does well because ...
 
-        On Eager-Hard, \cvc{} does well and \us{} does poorly because ...
+        \todo{}: On \zHard{}, \cvc{} does well and \us{} does poorly because ...

### 2018-01-18 includes/introduction.tex
Applying paper feedback.

@@
     Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and practically useful.
-Moreover a standard input language, \smt{}, has been developed and many mature solvers support it.
+Moreover a standard input language, \smt{}\cite{smt}, has been developed and many mature solvers support it.
 
-    In this paper, we present the following contributions:
-
-    \begin{enumerate}
-        \item \fuzzer{}: a fuzzer of \smt{} string and regex problems.
-        \item Generated inputs that elicit poor performance in \us{} and \cvc{}.
-        \item A recommended fix to \us{} that alleviates the poor performance.
-        \item A large suite of \smt{} string and regex problems we generated with \fuzzer{}.
-    \end{enumerate}
+    Our contributions follow.
+We describe the \fuzzer{} tool: a fuzzer of \smt{} string and regex problems.
+We then present a large suite of \smt{} string and regex problems we generated with \fuzzer{}.
+Then we describe two specific inputs - \cHard{} and \zHard{} - and experiments that show uniquely poor performance in \cvc{} and \us{} on those inputs, respectively.
+Finally, we recommend an algorithm to alleviate the poor performance in \us{}.

### 2018-01-18 includes/prior.tex
Applying paper feedback.

@@
     There are several fuzzers and problem generators currently available, but none of them support string or regex generation or transformation.
-For example the FuzzSMT [ref] tool generates \smt{} problems with bit vectors and arrays, but does not support strings or regexes.
-The SMTpp [ref] tool preprocesses and simplifies problems, but does not generate new ones or fuzz existing ones.
+For example the FuzzSMT\cite{fuzzsmt} tool generates \smt{} problems with bit vectors and arrays, but does not support strings or regexes.
+The SMTpp\cite{smtpp} tool preprocesses and simplifies problems, but does not generate new ones or fuzz existing ones.
 
@@
 % SMTpp: http://www.verit-solver.org/papers/smt2015.pdf
+
+    \hfill \\
+    \todo{}: references

### 2018-01-18 includes/problems.tex
Applying paper feedback.

--- 2018-01-14 includes/problems.tex
@@
 
-    \subsection{\fuzzer{}-Generated}
+    \subsubsection{\fuzzer{}-Generated}
 
-        This suite contains the following problem sets:
+        This suite contains the following problem sets: \\
 
-        \begin{itemize}
-            \item Lengths
-            \item Lengths-Concats
-            \item Concats
-            \item Concats-Extracts
-            \item Overlaps
-            \item Regex
-            \item Many-Regexes
-            \item Regex-Deep
-            \item Regex-Pair
-            \item Regex-Lengths
-            \item Random??
-        \end{itemize}
+        \begin{tabular}{|c|c|}
+            \hline
+            \textbf{Name}    & \textbf{Description} \\ \hline
+            Lengths          & \todo{} \\ \hline
+            Lengths-Concats  & \todo{} \\ \hline
+            Concats          & \todo{} \\ \hline
+            Concats-Extracts & \todo{} \\ \hline
+            Overlaps         & \todo{} \\ \hline
+            Regex            & \todo{} \\ \hline
+            Many-Regexes     & \todo{} \\ \hline
+            Regex-Deep       & \todo{} \\ \hline
+            Regex-Pair       & \todo{} \\ \hline
+            Regex-Lengths    & \todo{} \\ \hline
+            Random??         & \todo{} \\ \hline
+        \end{tabular}
+
+        \hfill \\
 
@@
 
-\begin{verbatim}
-while true; do stringfuzzg --random regex | z3str3 -in; done
-\end{verbatim}
+        {\scriptsize\begin{verbatim}
+while true; do stringfuzzg --random regex | z3str3 -in; done\end{verbatim}}
 
-    \subsection{\fuzzer{}-Transformed}
+        Some simple UNIX scripting can yield more interesting results. For example the following script finds a regex problem on which \us{} times out after 5 seconds:
 
-        This suite contains the following problem sets:
+        {\scriptsize\begin{verbatim}while true; do
+    stringfuzzg --random regex --coincide --num-regexes 2 --num-terms 5 --depth 3 > hard-problem.smt2
+    result=`z3str3 -T:5 hard-problem.smt2`
+    echo $result
+    if [ "$result" == "timeout" ]; then
+        cat hard-problem.smt2
+        break
+    fi
+done\end{verbatim}}
 
-        \begin{itemize}
-            \item Amazon??
-            \item Regex??
-        \end{itemize}
+    \subsubsection{\fuzzer{}-Transformed}
+
+        This suite contains the following problem sets: \\
+
+        \begin{tabular}{|c|c|}
+            \hline
+            \textbf{Name} & \textbf{Description} \\ \hline
+            Amazon??      & \todo{} \\ \hline
+            Regex??       & \todo{} \\ \hline
+        \end{tabular}
+
+        \hfill \\
 
@@
 
-        \begin{enumerate}
-            \item length lookup using eqc root
-            \item length-testing bug
-        \end{enumerate}
+        \todo{}: Describe the length lookup bug and length-testing bug, giving the before/after commits.

### 2018-01-18 includes/stringfuzz.tex
Applying paper feedback.

@@
                 \textbf{Name} & \textbf{Description} \\ \hline
-                concats       & \\ \hline
-                lengths       & \\ \hline
-                overlaps      & \\ \hline
-                regex         & \\ \hline
-                random-text   & \\ \hline
+                concats       & \todo{} \\ \hline
+                lengths       & \todo{} \\ \hline
+                overlaps      & \todo{} \\ \hline
+                regex         & \todo{} \\ \hline
+                random-text   & \todo{} \\ \hline
             \end{tabular}
@@
                 \textbf{Name} & \textbf{Description} \\ \hline
-                fuzz          & \\ \hline
-                graft         & \\ \hline
-                multiply      & \\ \hline
-                nop           & \\ \hline
-                reverse       & \\ \hline
-                rotate        & \\ \hline
-                translate     & \\ \hline
-                unprintable   & \\ \hline
+                fuzz          & \todo{} \\ \hline
+                graft         & \todo{} \\ \hline
+                multiply      & \todo{} \\ \hline
+                nop           & \todo{} \\ \hline
+                reverse       & \todo{} \\ \hline
+                rotate        & \todo{} \\ \hline
+                translate     & \todo{} \\ \hline
+                unprintable   & \todo{} \\ \hline
             \end{tabular}
@@
         \item[\texttt{stringmerge}] \hfill \\
-            This tool takes as input two \smt{} problems and combines them into one problem.
+            This tool takes as input two \smt{} problems and combines them into one problem. \textbf{TODO: Add details about merging strategies.}
 

### 2018-01-19 includes/abstract.tex
Rewriting some sections and srestructuring paper. Removing old files.

@@
 
-    In this paper we present \fuzzer{}: an \smtlib{} problem fuzzer and generator for string solvers.
-We provide a rich repository of problems we generated with \fuzzer{} in \smt{} format.
-We also analyse \numSolvers{} mature string solvers: \theSolvers{}.
-We use \fuzzer{} to craft inputs that elicit poor performance in \us{} and \cvc{}, and analyse the causes of the performance degradations.
-We then describe an algorithm to mitigate the performance degradation in \us{}.
-Finally, we describe several bugs in \us{} that were exposed by \fuzzer{}.
+    In this paper we present \fuzzer{}: a modular \smtlib{} problem transformer and generator for string solvers.
+We supply a rich repository of problems we generated with \fuzzer{} in \smt{} format, and demonstrate its usefulness in the development of \us{} by presenting defects it helped find and fix.
+We also use \fuzzer{} to exercise \theSolvers{} with suites of problems that elicit poor performance in one solver but not the other.
+We analyse our experimental results to identify the causes of the performance degradations, and present our findings.
 

### 2018-01-19 includes/experiment.tex
Rewriting some sections and srestructuring paper. Removing old files.

@@
 
-    Here we present two particular sets of problems generated by \fuzzer{}: \cHard{} and \zHard{}.
-These two problem sets were unique in their ability to elicit poor performance in one solver, but not another.
-Full details of test scripts, configurations, and problems that were used in the experiment can be found in the Appendix.
+    We generated several problem suites with \fuzzer{} that made one solver perform poorly, but not another. We call those suites: \cHard{} and \zHard{}.
 
-    % TODO:
-    % - supply machine environment description
-    % - supply install scripts that produce trace builds
-    % - supply test scripts that invoke the solvers and produce traces
+    On \cHard{} \cvc{} did poorly, but \us{} did well. The graphs in Figure~\ref{fig:cvc4-hard} show the performance results for both solvers.
 
-    \subsection{Data}
+    On \zHard{} \cvc{} did well, but \us{} did poorly. The graphs in Figure~\ref{fig:z3str3-hard} show the performance results for both solvers.
 
-        \subsubsection{Performance on \cHard{}}
+    \todo{Add data on Concats-Extracts}
 
-            On this problem set \cvc{} did poorly, but \us{} did well.
-The graphs in Figures~\ref{fig:z3str3-cvc4-hard} and ~\ref{fig:cvc4-cvc4-hard} show the performance results for both solvers.
-We produce and analyse the execution trace files both solvers' execution on the problem set.
+    On Concats-Extracts ...
 
-            \begin{figure}[h]
+    \begin{figure}[H]
         \begin{subfigure}{.5\textwidth}
@@
 
-            The \cvc{} trace file indicates that it performs the following operations:
+    \begin{figure}[H]
+        \begin{subfigure}{.5\textwidth}
+            \includegraphics[width=\textwidth]{data/graphs/cvc4-z3str3-hard.png}
+            \caption{Performance of \cvc{} on \zHard{}}
+            \label{fig:cvc4-z3str3-hard}
+        \end{subfigure}
+        \begin{subfigure}{.5\textwidth}
+            \includegraphics[width=\textwidth]{data/graphs/z3str3-z3str3-hard.png}
+            \caption{Performance of \us{} on \zHard{}}
+            \label{fig:z3str3-z3str3-hard}
+        \end{subfigure}
+        \caption{Results on \zHard}
+        \label{fig:z3str3-hard}
+    \end{figure}
+
+\section{Analyses}
+
+    In this section, we analyse the experimental results from the previous section.
+Although it is satisfying to find a class of problems that makes only one solver behave a certain way, it is only practically useful when the behaviour's cause is also understood.
+
+    \todo{Maybe organise these by solver, instead of by problem?}
+
+    \subsection{\cHard{}}
+
+        The \cvc{} trace file suggests that it performs the following operations:
 
@@
 After discovering the conflict, the rest of the trace is filled with apparently the same operation repeated hundreds of thousands of times.
-After this operation is finished, \cvc{} recalls the earlier conflict and returns \texttt{unsat}.
+This operation dominates the content of the trace.
+After this expensive operation is finished, \cvc{} appears to recall the earlier conflict and returns \texttt{unsat}.
 
@@
 
-            \us{} showed different behaviour on this problem set.
+        \us{} behaves differently.
 It follows a similar process as \cvc{}, except it does not flatten concatenations.
@@
 
-            % TODO:
-            % - \us{} cactus plot
-            % - \cvc{} cactus plot
-            % - comparison plot
+        We were not equipped well enough to debug this behaviour in \cvc{}, but we intend this result to be useful to its authors in improving it.
 
-        \subsubsection{Performance on \zHard{}}
+    \subsection{\zHard{}}
 
-            On this problem set \cvc{} did well, but \us{} did poorly.
-The graphs in Figures~\ref{fig:z3str3-z3str3-hard} and ~\ref{fig:cvc4-z3str3-hard} show the performance results for both solvers.
-We produce and analyse the execution trace files both solvers' execution on the problem set, and present them in the Appendix.
+        Both solvers exhibit similar patterns in their trace files. They differ in their strategies for assigning possible satisfying assignments.
 
-            \begin{figure}[h]
-                \begin{subfigure}{.5\textwidth}
-                    \includegraphics[width=\textwidth]{data/graphs/cvc4-z3str3-hard.png}
-                    \caption{Performance of \cvc{} on \zHard{}}
-                    \label{fig:cvc4-z3str3-hard}
-                \end{subfigure}
-                \begin{subfigure}{.5\textwidth}
-                    \includegraphics[width=\textwidth]{data/graphs/z3str3-z3str3-hard.png}
-                    \caption{Performance of \us{} on \zHard{}}
-                    \label{fig:z3str3-z3str3-hard}
-                \end{subfigure}
-                \caption{Results on \zHard}
-                \label{fig:z3str3-hard}
-            \end{figure}
-
-            Both solvers exhibit similar patterns in their trace files.
-They differ in their strategies for assigning possible satisfying assignments.
-\cvc{} assigns the first variable to a constant and all other variables to the empty string.
-\us{} however seems to ``drag'' the constant across the equation, splitting its characters among the variables in it.
-
-            % TODO:
-            % - \us{} cactus plot
-            % - \cvc{} cactus plot
-            % - comparison plot
-
-        \subsubsection{Performance Concats-Extracts}
-
-            \todo{}: No data on this yet.
-
-    \subsection{Analysis}
-
-        This section presents our analysis of the observed behaviour of \cvc{} and \us{} on \cHard{} and \zHard{} problems.
-
-        \todo{}: On \cHard{}, \cvc{} does poorly and \us{} does well because ...
-
-        \todo{}: On \zHard{}, \cvc{} does well and \us{} does poorly because ...
+        \todo{Explain why \us{} performs poorly.}

### 2018-01-19 includes/introduction.tex
Rewriting some sections and srestructuring paper. Removing old files.

--- 2018-01-15 includes/introduction.tex
@@
 
-    Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and practically useful.
-Moreover a standard input language, \smt{}, has been developed and many mature solvers support it.
+    Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and useful in practice.
+\theSolvers{}\cite{cvc4}\cite{z3str3} are \numSolvers{} such solvers.
+Moreover a standard input language for problem instances, \smt{}\cite{smt}, has been developed and many solvers support it.
+To validate their solvers, many authors have relied on hand-crafted input suites or real-world examples from industrial applications \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}.
+Indeed several suites of industrial and hand-crafted problems have been compiled \cite{kaluza} \cite{kausler} to both verify solvers and benchmark their performance.
+However though these suites help solver developers debug and verify their solvers, they do not age well.
+As solvers grow more complex and expressive, fixed benchmarks fail to exercise new behaviours.
+As a result, more and more solver functionality goes untested or unverified.
 
-    In this paper, we present the following contributions:
+    We introduce a modular fuzzer for string solvers, \fuzzer{}, and describe its utility as an exploratory verification tool.
+We show its effectiveness by presenting defects we were able to find in existing solvers.
+
+    \subsection{Contributions}
 
     \begin{enumerate}
-        \item \fuzzer{}: a fuzzer of \smt{} string and regex problems.
-        \item Generated inputs that elicit poor performance in \us{} and \cvc{}.
-        \item A recommended fix to \us{} that alleviates the poor performance.
-        \item A large suite of \smt{} string and regex problems we generated with \fuzzer{}.
+        \item \textbf{The \fuzzer{} tool}: We describe a modular fuzzer which can transform and generate \smt{} string and regex problems.
+We briefly document its components, modular architecture, and usage patterns to demonstrate its usefulness as an exploratory tool for validating not only solver implementations, but also algorithmic assumptions.
+        \item \textbf{A suite of \smt{} problems}: We present a suite of \smt{} string and regex problems we generated with \fuzzer{}.
+We justify the existence of each suite by a motivating example from the development of \us{}.
+We reveal specific defects that this suite helped uncover and fix, as well as specific conjectures that it helped validate or disprove.
+        \item \textbf{Experimental Results}: We present problem classes we found that made one solver perform poorly, but not another.
+We show differences in solver behaviour on the suites \cHard{} and \zHard{}.
+        \item \textbf{Analysis}: We analyse our experimental results by inspecting the execution traces of the solvers on the given problems.
+Where possible, we explain our observations.
+For \cvc{} we draw superficial conclusions based solely on the execution traces, and invite its authors to join us in analysing them.
+For \us{} we pinpoint algorithmic shortcomings that cause the poor performance.
     \end{enumerate}

### 2018-01-19 includes/prior.tex
Rewriting some sections and srestructuring paper. Removing old files.

@@
-\section{Prior Work}
+\section{Related Work}
 
-    There are several fuzzers and problem generators currently available, but none of them support string or regex generation or transformation.
+    Naturally, many solver developers author their own unit test suites to verify their solvers \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}.
+In addition, several popular problem suites are publicly available for solver verification, such as the Kaluza \cite{kaluza} and Kausler \cite{kausler} suites.
+
+    There are likewise several fuzzers and problem generators currently available, but none of them support string or regex generation or transformation.
 For example the FuzzSMT\cite{fuzzsmt} tool generates \smt{} problems with bit vectors and arrays, but does not support strings or regexes.
-The SMTpp\cite{smtpp} tool preprocesses and simplifies problems, but does not generate new ones or fuzz existing ones.
+The SMTpp\cite{smtpp} tool preprocesses and simplifies problems, but does not generate new ones or transform existing ones.
 
@@
 % SMTpp: http://www.verit-solver.org/papers/smt2015.pdf
-
-    \hfill \\
-    \todo{}: references

### 2018-01-19 includes/problems.tex
Rewriting some sections and srestructuring paper. Removing old files.

--- 2018-01-14 includes/problems.tex
@@
 
-    \subsection{\fuzzer{}-Generated}
+    \subsubsection{\fuzzer{}-Generated}
 
-        This suite contains the following problem sets:
+        Most of the problem sets in this suite either have a dedicated generator in \generator{}, or are variations of one. This suite contains the following problem sets: \\
 
-        \begin{itemize}
-            \item Lengths
-            \item Lengths-Concats
-            \item Concats
-            \item Concats-Extracts
-            \item Overlaps
-            \item Regex
-            \item Many-Regexes
-            \item Regex-Deep
-            \item Regex-Pair
-            \item Regex-Lengths
-            \item Random??
-        \end{itemize}
+        \todo{Fill in descriptions.}
 
-        Most of these problem sets either have a dedicated generator in \generator{}, or are variations of one.
-While it is likely that some of the pre-made suites will be immediately useful in analysing a solver, we also found that mass randomisation was helpful in finding some bugs, and we encourage this pattern as well.
-\generator{} is designed to be used in an exploratory fashion.
-For example the following usage has helped us find bugs in \us{}:
+        \begin{tabular}{|c|c|}
+            \hline
+            \textbf{Name}    & \textbf{Description} \\ \hline
+            Lengths          & \\ \hline
+            Lengths-Concats  & \\ \hline
+            Concats          & \\ \hline
+            Concats-Extracts & \\ \hline
+            Overlaps         & \\ \hline
+            Regex            & \\ \hline
+            Many-Regexes     & \\ \hline
+            Regex-Deep       & \\ \hline
+            Regex-Pair       & \\ \hline
+            Regex-Lengths    & \\ \hline
+        \end{tabular}
 
-\begin{verbatim}
-while true; do stringfuzzg --random regex | z3str3 -in; done
-\end{verbatim}
+    \subsubsection{\fuzzer{}-Transformed}
 
-    \subsection{\fuzzer{}-Transformed}
+        Most of the problem sets in this suite were generated by using one root problem and transforming it with \transformer{} into many similar problems.
+This suite contains the following problem sets: \\
 
-        This suite contains the following problem sets:
+        \todo{Fill in descriptions.}
 
-        \begin{itemize}
-            \item Amazon??
-            \item Regex??
-        \end{itemize}
+        \begin{tabular}{|c|c|}
+            \hline
+            \textbf{Name} & \textbf{Description} \\ \hline
+            Amazon        & \\ \hline
+            Regex         & \\ \hline
+        \end{tabular}
 
-        Most of these problem sets were generated by using one root problem and transforming it with \transformer{} into many similar problems.
-
-    \subsection{Unit Tests}
-
-        This suite covers corner cases of solver behaviour. We have used the instances in this suite to find bugs in \us{}.
-
-    \subsection{Bugs Found}
+\subsection{Results}
 
@@
 
-        \begin{enumerate}
-            \item length lookup using eqc root
-            \item length-testing bug
-        \end{enumerate}
+    \todo{Describe the length lookup bug and length-testing bug, giving the before/after commits.}
+
+    While it is likely that some of the pre-generated suites will be immediately useful in analysing a solver, we also found that randomisation was helpful in exploratory debugging, and we encourage this pattern as well.
+For example the following usage can feed random problems to \cvc{} until it returns an error:
+
+    {\scriptsize\begin{verbatim}
+while stringfuzzg random | cvc4 --lang smt2.5 --tlimit=5000; do sleep 0; done\end{verbatim}}
+
+    Some simple UNIX scripting can yield other interesting results. For example the following script finds a regex problem on which \us{} times out after 5 seconds:
+
+    {\scriptsize\begin{verbatim}while true; do
+    stringfuzzg -r regex -c -a increasing -r 2 -t 5 -d 3 > problem.smt25
+    result=`z3str3 -T:5 problem.smt25`
+    echo $result
+    if [ "$result" == "timeout" ]; then
+        cat hard-problem.smt2
+        break
+    fi
+done\end{verbatim}}

### 2018-01-19 includes/stringfuzz.tex
Rewriting some sections and srestructuring paper. Removing old files.

--- 2018-01-15 includes/stringfuzz.tex
@@
 
-    This section describes the fuzzer \fuzzer{}, which generates new \smt{} problems or transforms existing ones.
+    This section describes the fuzzer \fuzzer{}, which generates new \smt{} problems and transforms existing ones.
 \fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyse \smt{} string problems.
-Its source code repository is available at \sourceRepo{}.
-It can either be installed from source, or from the Python PIP package repository.
+
+    % Its source code repository is available at \sourceRepo{}. It can either be installed from source, or from the Python PIP package repository.
 
     The \fuzzer{} code is organised to be easily extended: all generators and transformers are independent modules.
-It is also implemented as a Unix "filter", to enable easy integration with other tools (including itself).
+It is also implemented as a Unix ``filter'', to enable easy integration with other tools (including itself).
 For example, the outputs of generators can be piped directly into transformers, and transformers can be chained to produce a tuned stream of challenging inputs to a solver.
 
-    Below are descriptions of the tools that come with \fuzzer{}:
+    Below are descriptions of the tools that constitute \fuzzer{}:
 
@@
             This tool generates \smt{} problems. It supports several generators and options that control its output. The generators it implements are: \\
+
+            \todo{Fill in descriptions.}
 
@@
         \item[\texttt{stringfuzzx}] \hfill \\
-            This tool transforms \smt{} problems.. It supports several transformers and options that control its output and input. The transformers it implements are:\\
+            This tool transforms \smt{} problems.. It supports several transformers and options that control its output and input. The transformers it implements are: \\
+
+            \todo{Fill in descriptions.}
 
@@
 
+            \todo{Add details about merging strategies.}
+
     \end{description}

### 2018-01-19 includes/experiment.tex
More rewriting and condensing.

@@
 
-    We generated several problem suites with \fuzzer{} that made one solver perform poorly, but not another. We call those suites: \cHard{} and \zHard{}.
+    We generated several problem suites with \fuzzer{} that made one solver perform poorly, but not another.
+We call those suites: \cHard{} and \zHard{}.
+On \cHard{} \cvc{} did poorly, but \us{} did well.
+The graphs in Figures ~\ref{fig:cvc4-hard} and ~\ref{fig:z3str3-hard} show the performance results.
 
-    On \cHard{} \cvc{} did poorly, but \us{} did well. The graphs in Figure~\ref{fig:cvc4-hard} show the performance results for both solvers.
-
-    On \zHard{} \cvc{} did well, but \us{} did poorly. The graphs in Figure~\ref{fig:z3str3-hard} show the performance results for both solvers.
-
+    \todo{Make real graphs}
     \todo{Add data on Concats-Extracts}
-
-    On Concats-Extracts ...
 

### 2018-01-19 includes/introduction.tex
More rewriting and condensing.

@@
 However though these suites help solver developers debug and verify their solvers, they do not age well.
-As solvers grow more complex and expressive, fixed benchmarks fail to exercise new behaviours.
+As solvers grow more complex and expressive, fixed benchmarks fail to exercise those new behaviours.
 As a result, more and more solver functionality goes untested or unverified.
@@
     We introduce a modular fuzzer for string solvers, \fuzzer{}, and describe its utility as an exploratory verification tool.
-We show its effectiveness by presenting defects we were able to find in existing solvers.
+We show its effectiveness by presenting defects we were able to find in leading solvers.
 

### 2018-01-19 includes/problems.tex
More rewriting and condensing.

@@
 
-    We generated several suites of string and regex problems using \fuzzer{}, and they are available at \problemRepo{}. They are described in more detail below.
-
-    \subsubsection{\fuzzer{}-Generated}
-
-        Most of the problem sets in this suite either have a dedicated generator in \generator{}, or are variations of one. This suite contains the following problem sets: \\
+    We generated several suites of string and regex problems using \fuzzer{}, and they are available at \problemRepo{}.
+The \texttt{generated} suite contains problems that were generated using \generator{}, described below:
 
@@
     \end{tabular}
+    \hfill \\ \\
 
-    \subsubsection{\fuzzer{}-Transformed}
-
-        Most of the problem sets in this suite were generated by using one root problem and transforming it with \transformer{} into many similar problems.
-This suite contains the following problem sets: \\
+    The \texttt{transformerd} suite contains problems generated by using one root problem and transforming it with \transformer{} into many similar problems. They are described below:
 
@@
 
-    While it is likely that some of the pre-generated suites will be immediately useful in analysing a solver, we also found that randomisation was helpful in exploratory debugging, and we encourage this pattern as well.
+    \subsection{Patterns}
+
+        While the aforementioned suites are useful in analysing a solver, we also found that randomisation was helpful in exploratory debugging, and we encourage this pattern as well.
 For example the following usage can feed random problems to \cvc{} until it returns an error:
@@
 
-    Some simple UNIX scripting can yield other interesting results. For example the following script finds a regex problem on which \us{} times out after 5 seconds:
+        Some \unix{} scripting can yield other interesting results. For example the following script finds a regex problem on which \us{} times out after 5 seconds:
 

### 2018-01-19 includes/stringfuzz.tex
More rewriting and condensing.

@@
     The \fuzzer{} code is organised to be easily extended: all generators and transformers are independent modules.
-It is also implemented as a Unix ``filter'', to enable easy integration with other tools (including itself).
+Its components are also implemented as \unix{} ``filters'', to enable easy integration with other tools (including themselves).
 For example, the outputs of generators can be piped directly into transformers, and transformers can be chained to produce a tuned stream of challenging inputs to a solver.
@@
         \item[\texttt{stringfuzzg}] \hfill \\
-            This tool generates \smt{} problems. It supports several generators and options that control its output. The generators it implements are: \\
+            This tool generates \smt{} problems. It supports several generators and options that specify its output. The generators it implements are: \\
 
@@
         \item[\texttt{stringfuzzx}] \hfill \\
-            This tool transforms \smt{} problems.. It supports several transformers and options that control its output and input. The transformers it implements are: \\
+            This tool transforms \smt{} problems.. It supports several transformers and options that specify its output and input. The transformers it implements are: \\
 
@@
         \item[\texttt{stringstats}] \hfill \\
-            This tool takes as input an \smt{} problem, and outputs its properties. The properties are:
-
-            \begin{itemize}
-                \item number of string variables
-                \item number of string literals
-                \item max/median syntactic depth of expressions
-                \item max/median length of literals
-            \end{itemize}
+            This tool takes as input an \smt{} problem, and outputs its properties, such as: numbers of string variables and literals, max/median syntactic depth of expressions, and max/median length of literals.
 

### 2018-01-20 includes/introduction.tex
Addressing Federico's feedback.

@@
 To validate their solvers, many authors have relied on hand-crafted input suites or real-world examples from industrial applications \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}.
-Indeed several suites of industrial and hand-crafted problems have been compiled \cite{kaluza} \cite{kausler} to both verify solvers and benchmark their performance.
-However though these suites help solver developers debug and verify their solvers, they do not age well.
-As solvers grow more complex and expressive, fixed benchmarks fail to exercise those new behaviours.
-As a result, more and more solver functionality goes untested or unverified.
+Indeed several suites of industrial and hand-crafted problems have been compiled \cite{kaluza} \cite{kausler} to both validate solvers and benchmark their performance.
+However, though these suites help debug solvers, they do not age well.
+As solvers continue to grow, fixed benchmarks leave more and more functionality untested.
 
-    We introduce a modular fuzzer for string solvers, \fuzzer{}, and describe its utility as an exploratory verification tool.
+    We introduce a modular fuzzer for string solvers, \fuzzer{}, and describe its utility as an exploratory validation tool.
 We show its effectiveness by presenting defects we were able to find in leading solvers.

### 2018-01-20 includes/prior.tex
Addressing Federico's feedback.

@@
 
-    Naturally, many solver developers author their own unit test suites to verify their solvers \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}.
-In addition, several popular problem suites are publicly available for solver verification, such as the Kaluza \cite{kaluza} and Kausler \cite{kausler} suites.
+    Naturally, many solver developers author their own unit test suites to validate their solvers \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}.
+In addition, several popular problem suites are publicly available for solver validation, such as the Kaluza \cite{kaluza} and Kausler \cite{kausler} suites.
 

### 2018-01-21 includes/experiment.tex
Adding graphs and changing experiment section to use them.

@@
-\section{Experiments}
+\section{Experimental Data}
 
-    We generated several problem suites with \fuzzer{} that made one solver perform poorly, but not another.
-We call those suites: \cHard{} and \zHard{}.
-On \cHard{} \cvc{} did poorly, but \us{} did well.
-The graphs in Figures ~\ref{fig:cvc4-hard} and ~\ref{fig:z3str3-hard} show the performance results.
-
-    \todo{Make real graphs}
-    \todo{Add data on Concats-Extracts}
+    We generated several problem suites with \fuzzer{} that made one solver perform poorly, but not others.
+The graphs in the figures below show the performance results.
+All experiments were run in series on the same Linux computer, with a timeout of 15 seconds.
 
@@
         \begin{subfigure}{.5\textwidth}
-            \includegraphics[width=\textwidth]{data/graphs/cvc4-cvc4-hard.png}
-            \caption{Performance of \cvc{} on \cHard{}}
-            \label{fig:cvc4-cvc4-hard}
+            \caption{Performance on concats-balanced}
+            \label{fig:concats-balanced}
+            \includegraphics[width=\textwidth]{data/graphs/concats-balanced.png}
         \end{subfigure}
         \begin{subfigure}{.5\textwidth}
-            \includegraphics[width=\textwidth]{data/graphs/z3str3-cvc4-hard.png}
-            \caption{Performance of \us{} on \cHard{}}
-            \label{fig:z3str3-cvc4-hard}
-        \end{subfigure}
-        \caption{Results on \cHard}
-        \label{fig:cvc4-hard}
-    \end{figure}
-
-    \begin{figure}[H]
-        \begin{subfigure}{.5\textwidth}
-            \includegraphics[width=\textwidth]{data/graphs/cvc4-z3str3-hard.png}
-            \caption{Performance of \cvc{} on \zHard{}}
-            \label{fig:cvc4-z3str3-hard}
+            \caption{Performance on concats-small}
+            \label{fig:concats-small}
+            \includegraphics[width=\textwidth]{data/graphs/concats-small.png}
         \end{subfigure}
         \begin{subfigure}{.5\textwidth}
-            \includegraphics[width=\textwidth]{data/graphs/z3str3-z3str3-hard.png}
-            \caption{Performance of \us{} on \zHard{}}
-            \label{fig:z3str3-z3str3-hard}
+            \caption{Performance on concats-extracts-small}
+            \label{fig:concats-extracts-small}
+            \includegraphics[width=\textwidth]{data/graphs/concats-extracts-small.png}
         \end{subfigure}
-        \caption{Results on \zHard}
-        \label{fig:z3str3-hard}
+        \begin{subfigure}{.5\textwidth}
+            \caption{Performance on different-prefix}
+            \label{fig:different-prefix}
+            \includegraphics[width=\textwidth]{data/graphs/different-prefix.png}
+        \end{subfigure}
+        \caption{Results on selected \fuzzer{} problems}
+        \label{fig:graphs}
     \end{figure}

### 2018-01-22 includes/prior.tex
Addressing Federico's feedback. Adding Makefile target to re-gather data.

--- 2018-01-18 includes/prior.tex
@@
-\section{Prior Work}
+\section{Related Work}
 
-    There are several fuzzers and problem generators currently available, but none of them support string or regex generation or transformation.
+    Naturally, many solver developers author their own test suites to validate their solvers \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}.
+In addition, several popular problem suites are publicly available for solver validation, such as the Kaluza \cite{kaluza} and Kausler \cite{kausler} suites.
+
+    There are likewise several fuzzers and problem generators currently available, but none of them can generate or transform string and regex problems.
 For example the FuzzSMT\cite{fuzzsmt} tool generates \smt{} problems with bit vectors and arrays, but does not support strings or regexes.

### 2018-01-22 includes/problems.tex
Addressing Federico's feedback. Adding Makefile target to re-gather data.

@@
 
-    We generated several suites of string and regex problems using \fuzzer{}, and they are available at \problemRepo{}.
-The \texttt{generated} suite contains problems that were generated using \generator{}, described below:
+    We generated several suites of string and regex problems using \fuzzer{}.
+These problems are available at \problemRepo{}.
+Below, we describe the \texttt{generated} suite that we generated using \generator{}:
 
@@
 
-        This section describes the bugs in \us{} that were discovered (and subsequently fixed) by testing it with the \fuzzer{} problem suites.
+        This section describes the bugs we discovered in \us{} (that were subsequently fixed) by testing it with the \fuzzer{} problem suites.
 
@@
 
-        While the aforementioned suites are useful in analysing a solver, we also found that randomisation was helpful in exploratory debugging, and we encourage this pattern as well.
+        While the aforementioned suites are useful in analysing a solver, we also used randomised \fuzzer{} runs for exploratory debugging.
 For example the following usage can feed random problems to \cvc{} until it returns an error:
@@
         {\scriptsize\begin{verbatim}
-while stringfuzzg random | cvc4 --lang smt2.5 --tlimit=5000; do sleep 0; done\end{verbatim}}
+while stringfuzzg -r random | tee problem.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do
+    sleep 0
+done\end{verbatim}}
 

### 2018-01-24 includes/abstract.tex
Fleshing out sections and revising a bunch of content further.

--- 2018-01-18 includes/abstract.tex
@@
 
-    In this paper we present \fuzzer{}: an \smtlib{} problem fuzzer and generator for string solvers.
-We provide a rich repository of problems we generated with \fuzzer{} in \smt{} format.
-We also analyse \numSolvers{} mature string solvers: \theSolvers{}.
-We use \fuzzer{} to craft inputs that elicit poor performance in \us{} and \cvc{}, and analyse the causes of the performance degradations.
-We then describe an algorithm to mitigate the performance degradation in \us{}.
-Finally, we describe several bugs in \us{} that were exposed by \fuzzer{}.
+    In this paper we introduce \fuzzer{}: a modular \smt{} problem transformer and generator for string solvers.
+We supply a repository of problems we generated with \fuzzer{} in \smtfull{} format, and demonstrate its usefulness by showing defects it helped find and fix in a mature solver: \us{}.
+We also test the solvers \theSolvers{} with suites of \fuzzer{} problems that elicit poor performance in some of the solvers, but not in others.
+We briefly analyse our experimental results, and identify the causes of the performance degradations in \us{}.
 

### 2018-01-24 includes/experiment.tex
Updating graphs, adding some docs to Makefile, and putting graph captions under graphs..
Fleshing out sections and revising a bunch of content further.

@@
 \section{Experimental Data}
+\label{sec:data}
 
     We generated several problem suites with \fuzzer{} that made one solver perform poorly, but not others.
-The graphs in the figures below show the performance results.
+These suites are \theSuites{}.
+Figure~\ref{fig:cvc-hard} shows the suites that were uniquely difficult for \cvc{}.
+Figure~\ref{fig:z3str3-hard} shows the suites that were uniquely difficult for \us{}.
 All experiments were run in series on the same Linux computer, with a timeout of 15 seconds.
@@
         \begin{subfigure}{.5\textwidth}
-            \caption{Performance on concats-balanced}
-            \label{fig:concats-balanced}
-            \includegraphics[width=\textwidth]{data/graphs/concats-balanced.png}
+            \includegraphics[width=\textwidth]{data/graphs/concats-extracts-small.png}
+            \label{fig:concats-extracts-small}
+            \caption{Performance on concats-extracts-small}
         \end{subfigure}
         \begin{subfigure}{.5\textwidth}
-            \caption{Performance on concats-small}
-            \label{fig:concats-small}
-            \includegraphics[width=\textwidth]{data/graphs/concats-small.png}
+            \includegraphics[width=\textwidth]{data/graphs/different-prefix.png}
+            \label{fig:different-prefix}
+            \caption{Performance on different-prefix}
+        \end{subfigure}
+        \caption{Problems hard for \cvc{}}
+        \label{fig:cvc-hard}
+    \end{figure}
+
+    \begin{figure}[H]
+        \begin{subfigure}{.5\textwidth}
+            \includegraphics[width=\textwidth]{data/graphs/concats-balanced.png}
+            \label{fig:concats-balanced}
+            \caption{Performance on concats-balanced}
         \end{subfigure}
         \begin{subfigure}{.5\textwidth}
-            \caption{Performance on concats-extracts-small}
-            \label{fig:concats-extracts-small}
-            \includegraphics[width=\textwidth]{data/graphs/concats-extracts-small.png}
+            \includegraphics[width=\textwidth]{data/graphs/concats-small.png}
+            \label{fig:concats-small}
+            \caption{Performance on concats-small}
         \end{subfigure}
-        \begin{subfigure}{.5\textwidth}
-            \caption{Performance on different-prefix}
-            \label{fig:different-prefix}
-            \includegraphics[width=\textwidth]{data/graphs/different-prefix.png}
-        \end{subfigure}
-        \caption{Results on selected \fuzzer{} problems}
-        \label{fig:graphs}
+        \caption{Problems hard for \us{}}
+        \label{fig:z3str3-hard}
     \end{figure}
@@
 \section{Analyses}
+\label{sec:analysis}
 
-    In this section, we analyse the experimental results from the previous section.
-Although it is satisfying to find a class of problems that makes only one solver behave a certain way, it is only practically useful when the behaviour's cause is also understood.
+    In this section, we analyse our experimental results.
+We discuss the causes of \us{}'s poor performance on the two problem suites: \textit{concats-balanced} and \textit{concats-big}.
+We were not equipped well enough to debug the behaviours of the other solvers, but we provide our data in hopes that they will be useful to the solvers' authors.
 
-    \todo{Maybe organise these by solver, instead of by problem?}
+    \subsection{\us{} on concats-balanced}
 
-    \subsection{\cHard{}}
+        \todo{Dmitry with help: Explain why \us{} performs poorly on this suite.}
 
-        The \cvc{} trace file suggests that it performs the following operations:
+% X = "solution"
+% X = (((A.B).(C.D)).((E.F).(G.H))).
+%     (((I.J).(K.L)).((M.N).(O.P)))
 
-        \begin{enumerate}
-            \item Loads all facts into its database.
-            \item Flattens binary concatenations into n-ary concatenations.
-            \item Computes equivalence classes for strings and integers.
-        \end{enumerate}
+    \subsection{\us{} on concats-big}
 
-        At this stage it discovers that there is a conflict in one of its equivalence classes, as shown in Figure~\ref{fig:cvc4-conflict}.
-After discovering the conflict, the rest of the trace is filled with apparently the same operation repeated hundreds of thousands of times.
-This operation dominates the content of the trace.
-After this expensive operation is finished, \cvc{} appears to recall the earlier conflict and returns \texttt{unsat}.
+        \todo{Dmitry with help: Explain why \us{} performs poorly on this suite.}
 
-        \begin{figure}[h]
-            {\scriptsize\begin{verbatim}
-CONFLICT: Eq engine conflict : (and
-(= "woof" (str.++ "woof" lsym_5 ... lsym_5))
-(= "" lsym_5)
-(= "" var3) ... (= "" var30)
-(= (str.++ "woof" var3 ... var30) (str.++ "meow" var43 ... var70))
-(= "" var43) ... (= "" var70)
-(= "meow" (str.++ "meow" lsym_5 ... lsym_5)))\end{verbatim}}
-            \caption{Evidence of \cvc{} detecting conflict}
-            \label{fig:cvc4-conflict}
-        \end{figure}
-
-        \us{} behaves differently.
-It follows a similar process as \cvc{}, except it does not flatten concatenations.
-In contrast to \cvc{}, \us{} immediately returns \texttt{unsat} as soon as it verifies consistency of equivalence classes as it constructs them, as shown in Figure~\ref{fig:z3str3-conflict}.
-
-        \begin{figure}[h]
-            {\scriptsize\begin{verbatim}
--------- [str] new_eq_check ../src/smt/theory_str.cpp:1864 ---------
-checking whether (str.++ "woof" var2) and (str.++ "meow" var42) can be equal
-------------------------------------------------
--------- [str] new_eq_check ../src/smt/theory_str.cpp:1867 ---------
-inconsistency detected: (str.++ "woof" var2) cannot be equal to (str.++ "meow" var42)
-------------------------------------------------
--------- [str] assert_axiom ../src/smt/theory_str.cpp:179 ---------
-asserting (not (= (str.++ "woof" var2) (str.++ "meow" var42)))
-------------------------------------------------\end{verbatim}}
-            \caption{Evidence of \us{} detecting conflict}
-            \label{fig:z3str3-conflict}
-        \end{figure}
-
-        We were not equipped well enough to debug this behaviour in \cvc{}, but we intend this result to be useful to its authors in improving it.
-
-    \subsection{\zHard{}}
-
-        Both solvers exhibit similar patterns in their trace files. They differ in their strategies for assigning possible satisfying assignments.
-
-        \todo{Explain why \us{} performs poorly.}
+% X = "solution"
+% X = (A.(B.(C.(D.(E.(F.(G.H)))))))

### 2018-01-24 includes/introduction.tex
Addressing Federico's feedback. Adding Makefile target to re-gather data.
Fleshing out sections and revising a bunch of content further.

@@
 \theSolvers{}\cite{cvc4}\cite{z3str3} are \numSolvers{} such solvers.
-Moreover a standard input language for problem instances, \smt{}\cite{smt}, has been developed and many solvers support it.
+Moreover a standard input language for problem instances, \smtfull{}\cite{smt}, has been developed and widely adopted.
 To validate their solvers, many authors have relied on hand-crafted input suites or real-world examples from industrial applications \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}.
@@
     We introduce a modular fuzzer for string solvers, \fuzzer{}, and describe its utility as an exploratory validation tool.
-We show its effectiveness by presenting defects we were able to find in leading solvers.
+We show its effectiveness by presenting defects and limitations we were able to find in leading solvers.
 
@@
         \begin{enumerate}
-        \item \textbf{The \fuzzer{} tool}: We describe a modular fuzzer which can transform and generate \smt{} string and regex problems.
-We briefly document its components, modular architecture, and usage patterns to demonstrate its usefulness as an exploratory tool for validating not only solver implementations, but also algorithmic assumptions.
-        \item \textbf{A suite of \smt{} problems}: We present a suite of \smt{} string and regex problems we generated with \fuzzer{}.
-We justify the existence of each suite by a motivating example from the development of \us{}.
-We reveal specific defects that this suite helped uncover and fix, as well as specific conjectures that it helped validate or disprove.
-        \item \textbf{Experimental Results}: We present problem classes we found that made one solver perform poorly, but not another.
-We show differences in solver behaviour on the suites \cHard{} and \zHard{}.
+            \item \textbf{The \fuzzer{} tool}: We describe a modular fuzzer which can transform and generate \smtfull{} string and regex problems.
+We briefly document its components and modular architecture.
+We provide some motivating usage patterns to demonstrate its usefulness as an exploratory tool for validating solvers.
+We additionally detail its regex-generating and transforming capabilities.
+            \item \textbf{A repository of \smtfull{} problems}: We present a repository of \smtfull{} string and regex problem suites we generated with \fuzzer{}.
+We demonstrate the usefulness of these suites by revealing specific defects they helped uncover and fix in \us{}.
+            \item \textbf{Experimental Results}: We present experimental runs of \theSolvers{} on the \fuzzer{} suites: \theSuites{}.
+We picked these suites because they uniquely made some solvers perform poorly, but not others.
             \item \textbf{Analysis}: We analyse our experimental results by inspecting the execution traces of the solvers on the given problems.
-Where possible, we explain our observations.
-For \cvc{} we draw superficial conclusions based solely on the execution traces, and invite its authors to join us in analysing them.
-For \us{} we pinpoint algorithmic shortcomings that cause the poor performance.
+For \us{} we pinpoint algorithmic limitations that cause the poor performance.
+For other solvers, we draw superficial conclusions based solely on the execution traces, and invite their authors to conduct further analysis.
         \end{enumerate}

### 2018-01-24 includes/problems.tex
Fleshing out sections and revising a bunch of content further.

@@
 \section{Problem Suites}
+\label{sec:problems}
 
@@
 These problems are available at \problemRepo{}.
-Below, we describe the \texttt{generated} suite that we generated using \generator{}:
+Below, we describe the \texttt{generated} suite that we generated using \generator{}: \\
 
-    \todo{Fill in descriptions.}
-
-    \begin{tabular}{|c|c|}
+    \begin{tabular}{|l|l|}
         \hline
-        \textbf{Name}    & \textbf{Description} \\ \hline
-        Lengths          & \\ \hline
-        Lengths-Concats  & \\ \hline
-        Concats          & \\ \hline
-        Concats-Extracts & \\ \hline
-        Overlaps         & \\ \hline
-        Regex            & \\ \hline
-        Many-Regexes     & \\ \hline
-        Regex-Deep       & \\ \hline
-        Regex-Pair       & \\ \hline
-        Regex-Lengths    & \\ \hline
+        \textbf{Name}    & \textbf{Problems have ...} \\ \hline
+        Concats          & A single, deep tree of concats. \\ \hline
+        Concats-Extracts & A single concat tree, and random character extractions. \\ \hline
+        Lengths          & A single, large length constraint on a variable. \\ \hline
+        Lengths-Concats  & Variables and their concats, each with fixed lengths. \\ \hline
+        Overlaps         & A formula in the form A.X = X.B. \\ \hline
+        Regex            & A test for regex membership of arbitrary complexity. \\ \hline
+        Many-Regexes     & A test for membership in many random regexes. \\ \hline
+        Regex-Deep       & A test for membership in a regex with many nested operators. \\ \hline
+        Regex-Pair       & A test for membership in one regex, but not another. \\ \hline
+        Regex-Lengths    & A test for membership in a regex, and a length constraint. \\ \hline
     \end{tabular}
-    \hfill \\ \\
+    \hfill \\
 
@@
 
-    \todo{Fill in descriptions.}
+    \todo{Federico: fill in descriptions.}
 
-    \begin{tabular}{|c|c|}
+    \begin{tabular}{|l|l|}
         \hline
@@
 
-    \subsection{Results}
+    \subsection{Usefulness to \us{}}
 
@@
 
-        \todo{Describe the length lookup bug and length-testing bug, giving the before/after commits.}
+        The first bug we found caused \us{} to perform poorly when the equivalence class of arithmetic terms is very large (e.g.
+where many strings are equal to the empty string, and thus have length 0).
+The slowdown was caused by a loop over the equivalence class of these terms to search for an integer constant.
+The fix was to check the root of the equivalence class for the integer constant, as Z3 makes "interpreted terms" (i.e.
+constants) the root of equivalence classes whenever possible.
+This bug was last observed in commit 6308636, and was fixed in commit 3865c45.
 
-    \subsection{Patterns}
+        The second bug we found caused \us{} to perform poorly when a variable had a large length constraint.
+The slowdown was caused by the solver performing a linear search for a satisfying length when producing a model for the variable.
+This bug was an inconsistency between the implementation and the behaviour described in the \us{} paper \cite{z3str3}.
+This bug was last observed in commit 66bc68f, and was fixed in commit 7b536e9.
 
-        While the aforementioned suites are useful in analysing a solver, we also used randomised \fuzzer{} runs for exploratory debugging.
-For example the following usage can feed random problems to \cvc{} until it returns an error:
-
-        {\scriptsize\begin{verbatim}
-while stringfuzzg -r random | tee problem.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do
-    sleep 0
-done\end{verbatim}}
-
-        Some \unix{} scripting can yield other interesting results. For example the following script finds a regex problem on which \us{} times out after 5 seconds:
-
-        {\scriptsize\begin{verbatim}while true; do
-    stringfuzzg -r regex -c -a increasing -r 2 -t 5 -d 3 > problem.smt25
-    result=`z3str3 -T:5 problem.smt25`
-    echo $result
-    if [ "$result" == "timeout" ]; then
-        cat hard-problem.smt2
-        break
-    fi
-done\end{verbatim}}
+        \todo{Dmitry: maybe show graphs with before and after?}

### 2018-01-24 includes/stringfuzz.tex
Adding some TODOs.
Fleshing out sections and revising a bunch of content further.

@@
 \section{\fuzzer{}}
+\label{sec:fuzzer}
 
-    This section describes the fuzzer \fuzzer{}, which generates new \smt{} problems and transforms existing ones.
-\fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyse \smt{} string problems.
+    This section describes the fuzzer \fuzzer{}, which generates new \smtfull{} problems and transforms existing ones.
+\fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyse \smtfull{} string problems.
 
@@
 
-    The \fuzzer{} code is organised to be easily extended: all generators and transformers are independent modules.
+    The \fuzzer{} code is organised to be easily extended: all generators and transformers are independent Python modules.
 Its components are also implemented as \unix{} ``filters'', to enable easy integration with other tools (including themselves).
@@
 
-        \item[\texttt{stringfuzzg}] \hfill \\
+        \item[\generator{}] \hfill \\
             This tool generates \smt{} problems. It supports several generators and options that specify its output. The generators it implements are: \\
 
-            \todo{Fill in descriptions.}
-
-            \begin{tabular}{|c|c|}
+            \begin{tabular}{|l|l|}
                 \hline
-                \textbf{Name} & \textbf{Description} \\ \hline
-                concats       & \\ \hline
-                lengths       & \\ \hline
-                overlaps      & \\ \hline
-                regex         & \\ \hline
-                random-text   & \\ \hline
+                \textbf{Name} & \textbf{Generated Problems have ...} \\ \hline
+                concats       & Long concats and optional random extracts. \\ \hline
+                lengths       & Many variables (and their concats) with length constraints. \\ \hline
+                overlaps      & An expression of the form A.X = X.B. \\ \hline
+                equality      & An equality among concats, each with variables or constants. \\ \hline
+                regex         & Regexes of variying complexity. \\ \hline
+                random-text   & Random, likely syntactically invalid text. \\ \hline
+                random-ast    & Totally random, but semantically valid text. \\ \hline
             \end{tabular}
@@
 
-        \item[\texttt{stringfuzzx}] \hfill \\
+        \item[\transformer{}] \hfill \\
+
             This tool transforms \smt{} problems.. It supports several transformers and options that specify its output and input. The transformers it implements are: \\
 
-            \todo{Fill in descriptions.}
+            \todo{Dmitry: maybe add notes about SAT preservation?}
 
-            \begin{tabular}{|c|c|}
+            \begin{tabular}{|l|l|}
                 \hline
-                \textbf{Name} & \textbf{Description} \\ \hline
-                fuzz          & \\ \hline
-                graft         & \\ \hline
-                multiply      & \\ \hline
-                nop           & \\ \hline
-                reverse       & \\ \hline
-                rotate        & \\ \hline
-                translate     & \\ \hline
-                unprintable   & \\ \hline
+                \textbf{Name} & \textbf{The transformer ...} \\ \hline
+                fuzz          & Randomly replaces literals and operators with similar ones. \\ \hline
+                graft         & For each sort, swaps a random non-leaf node with a leaf node. \\ \hline
+                multiply      & Multiplies each number by N, and repeats each character N times. \\ \hline
+                nop           & Does nothing. \\ \hline
+                reverse       & Reverses all string literals and concat arguments. \\ \hline
+                rotate        & Performs a random concat tree rotation. \\ \hline
+                translate     & Maps every character X to a different character Y. \\ \hline
+                unprintable   & Replaces all characters with unprintable ones. \\ \hline
             \end{tabular}
@@
 
-            \todo{Add details about merging strategies.}
+            \todo{Federico: describe \texttt{stringmerge}.}
 
     \end{description}
+
+    \subsection{Regex Fuzzing Capabilities}
+
+        \fuzzer{} can generate and transform problems with regular expression constratints.
+The command \texttt{stringfuzzg regex} invokes the regex problem generator, and has several options to control its output.
+It generates a problem in the form\footnote{Variable declarations omitted for brevity.}:
+
+        \begin{align*}
+            \langle problem \rangle  & ::= \langle membership \rangle \; \langle membership \rangle * \\
+            \langle membership \rangle & ::= \texttt{(assert (str.in.re X}\; R\; \texttt{))}
+        \end{align*}
+
+        where $R \in RegEx$. More simply, the problem is a set of one or more regex constraints on a single variable.
+
+        \todo{Dmitry: further describe the properties of $R$.}
+
+    \subsection{Patterns}
+
+        \fuzzer{} can be used to generate static benchmarks as described in Section~\ref{sec:problems}.
+It cna also be used in a randomised fashion for exploratory debugging.
+As a motivating example, the following usage can feed random problems to \cvc{} until it returns an error:
+
+        {\scriptsize\begin{verbatim}
+while stringfuzzg -r random --num-terms 1000 | tee problem.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do
+    sleep 0
+done\end{verbatim}}
+
+        Some \unix{} scripting can yield other interesting results. For example the following script finds a regex problem on which \us{} times out after 5 seconds:
+
+        {\scriptsize\begin{verbatim}while true; do
+    stringfuzzg -r regex -c -a increasing -r 2 -t 5 -d 3 > problem.smt25
+    result=`z3str3 -T:5 problem.smt25`
+    echo $result
+    if [ "$result" == "timeout" ]; then
+        cat hard-problem.smt2
+        break
+    fi
+done\end{verbatim}}

### 2018-01-24 includes/problems.tex
Fixing typos and descriptions.

@@
 
-    The \texttt{transformerd} suite contains problems generated by using one root problem and transforming it with \transformer{} into many similar problems. They are described below:
+    The \texttt{transformed} suite contains problems generated by using one root problem and transforming it with \transformer{} into many similar problems. They are described below:
 

### 2018-01-24 includes/stringfuzz.tex
Fixing typos and descriptions.

@@
                 equality      & An equality among concats, each with variables or constants. \\ \hline
-                regex         & Regexes of variying complexity. \\ \hline
-                random-text   & Random, likely syntactically invalid text. \\ \hline
-                random-ast    & Totally random, but semantically valid text. \\ \hline
+                regex         & Regexes of varying complexity. \\ \hline
+                random-text   & Random, likely syntactically \textit{in}valid text. \\ \hline
+                random-ast    & Random, but semantically \textit{valid} text. \\ \hline
             \end{tabular}
@@
                 reverse       & Reverses all string literals and concat arguments. \\ \hline
-                rotate        & Performs a random concat tree rotation. \\ \hline
+                rotate        & Performs a random syntax tree rotation on two concats. \\ \hline
                 translate     & Maps every character X to a different character Y. \\ \hline
-                unprintable   & Replaces all characters with unprintable ones. \\ \hline
+                unprintable   & Randomly replaces all characters in literals with unprintable ones. \\ \hline
             \end{tabular}
@@
 
-        \fuzzer{} can generate and transform problems with regular expression constratints.
+        \fuzzer{} can generate and transform problems with regular expression constraints.
 The command \texttt{stringfuzzg regex} invokes the regex problem generator, and has several options to control its output.
@@
         \fuzzer{} can be used to generate static benchmarks as described in Section~\ref{sec:problems}.
-It cna also be used in a randomised fashion for exploratory debugging.
+It can also be used in a randomised fashion for exploratory debugging.
 As a motivating example, the following usage can feed random problems to \cvc{} until it returns an error:

### 2018-01-26 includes/problems.tex
updated description of transformers

@@
 
-    The \texttt{transformed} suite contains problems generated by using one root problem and transforming it with \transformer{} into many similar problems. They are described below:
+    \todo{Federico: fill in descriptions. First draft - Federico}
 
-    \todo{Federico: fill in descriptions.}
+    The \texttt{transformed} suite contains benchmarks derived from existing seed problems by iteratively applying \transformer{}.
+    Every problem in the suite is named according to its seed and the transformations it undertook.
+For example, a hypothetical file named ``seed-fuzz-graft.smt2'' began as a file named ``seed.smt'' and was transformed twice, first by fuzz and then by graft.
+See Table~\ref{tbl:transformed} for an overview description of the suite.
 
-    \begin{tabular}{|l|l|}
+    The suite is divided into two categories. The first category, labeled Amazon, started as two seed files.
+    The first seed, z3-regex-1.smt2, encodes the assertions ``S not in aaabbb*'' and ``S in aaa*bbb*'' for a string constant S,
+    while the second seed, z3-regex-2-negative.smt2, encodes the assertions ``S in aaabbb*'' and ``S not in aaa*bbb*''. 
+    \todo{Can I say that these problems were deemed industrially relevant by Amazon? Probably not, right?} 
+    In total, 516 unique problems were generated from these two seeds.
+
+    The second category, Regex, is seeded by the z3str2 regular expression test suite \cite{} \todo{Is this right?
+If so where we can cite?}.
+This test suite contains 42 problems dealing with a wide variety of regular expressions.
+    Through accumulative transformations, as before, we were able to produce 10,577 unique benchmarks.
+
+    \begin{table}
+    \begin{tabular}{|l|l|r|}
         \hline
-        \textbf{Name} & \textbf{Description} \\ \hline
-        Amazon        & \\ \hline
-        Regex         & \\ \hline
+        \textbf{Name} & \textbf{Seed}                            & \textbf{Qunatity} \\ \hline
+        Amazon        & Two industrial regex membership problems & 516\\ \hline
+        Regex         & Z3str2 regular expression test suite     & 10,577\\ \hline
     \end{tabular}
+    \caption{\transformer{} generated problem sets.}
+    \label{tbl:transformed}
+    \end{table}
 
@@
 
+        \todo{Federico - Can we describe the floating point error we found?}
+
         \todo{Dmitry: maybe show graphs with before and after?}

### 2018-01-26 includes/problems.tex
small fix to transformed suite

@@
     Every problem in the suite is named according to its seed and the transformations it undertook. 
-For example, a hypothetical file named ``seed-fuzz-graft.smt2'' began as a file named ``seed.smt'' and was transformed twice, first by fuzz and then by graft.
-See Table~\ref{tbl:transformed} for an overview description of the suite.
+    For example, a hypothetical file named ``seed-fuzz-graft.smt2'' began as a file named ``seed.smt'' and was transformed twice:
+    first by fuzz, and then by graft.
 
-    The suite is divided into two categories. The first category, labeled Amazon, started as two seed files.
-    The first seed, z3-regex-1.smt2, encodes the assertions ``S not in aaabbb*'' and ``S in aaa*bbb*'' for a string constant S,
-    while the second seed, z3-regex-2-negative.smt2, encodes the assertions ``S in aaabbb*'' and ``S not in aaa*bbb*''. 
-    \todo{Can I say that these problems were deemed industrially relevant by Amazon? Probably not, right?} 
-    In total, 516 unique problems were generated from these two seeds.
-
-    The second category, Regex, is seeded by the z3str2 regular expression test suite \cite{} \todo{Is this right?
-If so where we can cite?}.
-This test suite contains 42 problems dealing with a wide variety of regular expressions.
-    Through accumulative transformations, as before, we were able to produce 10,577 unique benchmarks.
+    The suite is divided into two categories. For an overview see Table~\ref{tbl:transformed}.
 
@@
     \end{table}
+
+    The first category, labeled Amazon, started as two seed files.
+    The first seed, z3-regex-1.smt2, encodes the assertions ``S not in aaabbb*'' and ``S in aaa*bbb*'' for a string constant S,
+    while the second seed, z3-regex-2-negative.smt2, encodes the assertions ``S in aaabbb*'' and ``S not in aaa*bbb*''. 
+    \todo{Can I say something like that these problems were deemed industrially relevant by Amazon? Probably not, right?} 
+    In total, 516 unique problems were generated from these two seeds.
+
+    The second category, Regex, is seeded by the z3str2 regular expression test suite \cite{} 
+    \todo{Is this right? If so where we can cite?}. 
+    This test suite contains 42 problems dealing with a wide variety of regular expressions.
+    Through cumulative transformations, as before, we were able to produce 10,577 unique benchmarks.
 

### 2018-01-26 includes/problems.tex
small updates from Dmitry's comments

@@
         \hline
-        \textbf{Name} & \textbf{Seed}                            & \textbf{Qunatity} \\ \hline
+        \textbf{Name} & \textbf{Seed}                            & \textbf{Quantity} \\ \hline
         Amazon        & Two industrial regex membership problems & 516\\ \hline
@@
     while the second seed, z3-regex-2-negative.smt2, encodes the assertions ``S in aaabbb*'' and ``S not in aaa*bbb*''. 
-    \todo{Can I say something like that these problems were deemed industrially relevant by Amazon? Probably not, right?} 
+    Both problems come from our industrial collaborators. 
     In total, 516 unique problems were generated from these two seeds.
 
-    The second category, Regex, is seeded by the z3str2 regular expression test suite \cite{} 
-    \todo{Is this right? If so where we can cite?}. 
+    The second category, Regex, is seeded by the z3str2 regular expression test suite \cite{z3str2-tests}.
     This test suite contains 42 problems dealing with a wide variety of regular expressions.

### 2018-01-27 includes/problems.tex
Addressing Murphy's feedback.

@@
     We generated several suites of string and regex problems using \fuzzer{}.
-These problems are available at \problemRepo{}.
-Below, we describe the \texttt{generated} suite that we generated using \generator{}: \\
+\footnote{For review anonymity, we removed the link to the problem repository.
+It will be provided separately in the artifact submission track and will appear in the final version of the paper.} Below, we describe the \texttt{generated} suite that we generated using \generator{}: \\
 

### 2018-01-27 includes/stringfuzz.tex
Addressing Murphy's feedback.

@@
 \fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyse \smtfull{} string problems.
-
-    % Its source code repository is available at \sourceRepo{}. It can either be installed from source, or from the Python PIP package repository.
+It can either be installed from source, or from the Python PIP package repository.
+\footnote{For review anonymity, we removed the link to the source code.
+It will be provided separately in the artifact submission track and will appear in the final version of the paper.}
 
@@
 The command \texttt{stringfuzzg regex} invokes the regex problem generator, and has several options to control its output.
-It generates a problem in the form\footnote{Variable declarations omitted for brevity.}:
+It generates a problem of the form\footnote{Variable declarations omitted for brevity.}:
 

### 2018-01-27 includes/problems.tex
Adding more sections. Adding references.

@@
 \footnote{For review anonymity, we removed the link to the problem repository.
-It will be provided separately in the artifact submission track and will appear in the final version of the paper.} Below, we describe the \texttt{generated} suite that we generated using \generator{}: \\
+It will be provided separately in the artifact submission track and will appear in the final version of the paper.} Table~\ref{tbl:generated} describes the \texttt{generated} suite that we generated using \generator{}.
 
+    \begin{table}
+        \centering
         \begin{tabular}{|l|l|}
@@
             \textbf{Name}             & \textbf{Problems have ...} \\ \hline
-        Concats          & A single, deep tree of concats. \\ \hline
-        Concats-Extracts & A single concat tree, and random character extractions. \\ \hline
-        Lengths          & A single, large length constraint on a variable. \\ \hline
-        Lengths-Concats  & Variables and their concats, each with fixed lengths. \\ \hline
-        Overlaps         & A formula in the form A.X = X.B. \\ \hline
-        Regex            & A test for regex membership of arbitrary complexity. \\ \hline
-        Many-Regexes     & A test for membership in many random regexes. \\ \hline
-        Regex-Deep       & A test for membership in a regex with many nested operators. \\ \hline
-        Regex-Pair       & A test for membership in one regex, but not another. \\ \hline
-        Regex-Lengths    & A test for membership in a regex, and a length constraint. \\ \hline
+            \textit{Concats}          & A single, deep tree of concats. \\ \hline
+            \textit{Concats-Extracts} & A single concat tree, and random character extractions. \\ \hline
+            \textit{Lengths}          & A single, large length constraint on a variable. \\ \hline
+            \textit{Lengths-Concats}  & Variables and their concats, each with fixed lengths. \\ \hline
+            \textit{Overlaps}         & A formula of the form A.X = X.B. \\ \hline
+            \textit{Regex}            & A test for regex membership of arbitrary complexity. \\ \hline
+            \textit{Many-Regexes}     & A test for membership in many random regexes. \\ \hline
+            \textit{Regex-Deep}       & A test for membership in a regex with many nested operators. \\ \hline
+            \textit{Regex-Pair}       & A test for membership in one regex, but not another. \\ \hline
+            \textit{Regex-Lengths}    & A test for membership in a regex, and a length constraint. \\ \hline
         \end{tabular}
-    \hfill \\
-
-    \todo{Federico: fill in descriptions. First draft - Federico}
+        \caption{\generator{}-generated problem sets.}
+        \label{tbl:generated}
+    \end{table}
 
@@
 Every problem in the suite is named according to its seed and the transformations it undertook.
-    For example, a hypothetical file named ``seed-fuzz-graft.smt2'' began as a file named ``seed.smt'' and was transformed twice:
-    first by fuzz, and then by graft.
-
-    The suite is divided into two categories. For an overview see Table~\ref{tbl:transformed}.
+For example, a hypothetical file named ``seed-fuzz-graft.smt2'' began as a file named ``seed.smt'' and was transformed twice: first by fuzz, and then by graft.
+The suite is divided into two categories.
+For an overview see Table~\ref{tbl:transformed}.
 
     \begin{table}
+        \centering
         \begin{tabular}{|l|l|r|}
@@
             \textbf{Name}   & \textbf{Seed}                            & \textbf{Quantity} \\ \hline
-        Amazon        & Two industrial regex membership problems & 516\\ \hline
-        Regex         & Z3str2 regular expression test suite     & 10,577\\ \hline
+            \textit{Amazon} & Two industrial regex membership problems & 516\\ \hline
+            \textit{Regex}  & Z3str2 regular expression test suite     & 10,577\\ \hline
         \end{tabular}
-    \caption{\transformer{} generated problem sets.}
+        \caption{\transformer{}-generated problem sets.}
         \label{tbl:transformed}
@@
 
-        The first bug we found caused \us{} to perform poorly when the equivalence class of arithmetic terms is very large (e.g.
-where many strings are equal to the empty string, and thus have length 0).
+        The first bug we found caused \us{} to perform poorly when equivalence classes of arithmetic terms was very large (e.g.
+where many strings were equal to the empty string, and thus had length 0).
+We discovered this bug using the \textit{Concats} problem suite.
 The slowdown was caused by a loop over the equivalence class of these terms to search for an integer constant.
@@
         The second bug we found caused \us{} to perform poorly when a variable had a large length constraint.
+We discovered this bug using the \textit{Lengths} problem suite.
 The slowdown was caused by the solver performing a linear search for a satisfying length when producing a model for the variable.

### 2018-01-27 includes/stringfuzz.tex
Adding more sections. Adding references.

@@
         \item[\generator{}] \hfill \\
-            This tool generates \smt{} problems. It supports several generators and options that specify its output. The generators it implements are: \\
+            This tool generates \smt{} problems. It supports several generators and options that specify its output. Table~\ref{tbl:generators} describes them.
+            \hfill \\
 
+            \begin{table}
+                \centering
                 \begin{tabular}{|l|l|}
@@
                     \textbf{Name}        & \textbf{Generated Problems have ...} \\ \hline
-                concats       & Long concats and optional random extracts. \\ \hline
-                lengths       & Many variables (and their concats) with length constraints. \\ \hline
-                overlaps      & An expression of the form A.X = X.B. \\ \hline
-                equality      & An equality among concats, each with variables or constants. \\ \hline
-                regex         & Regexes of varying complexity. \\ \hline
-                random-text   & Random, likely syntactically \textit{in}valid text. \\ \hline
-                random-ast    & Random, but semantically \textit{valid} text. \\ \hline
+                    \textit{concats}     & Long concats and optional random extracts. \\ \hline
+                    \textit{lengths}     & Many variables (and their concats) with length constraints. \\ \hline
+                    \textit{overlaps}    & An expression of the form A.X = X.B. \\ \hline
+                    \textit{equality}    & An equality among concats, each with variables or constants. \\ \hline
+                    \textit{regex}       & Regexes of varying complexity. \\ \hline
+                    \textit{random-text} & Random, likely syntactically \textit{in}valid text. \\ \hline
+                    \textit{random-ast}  & Random, but semantically \textit{valid} text. \\ \hline
                 \end{tabular}
+                \caption{\generator{} generators}
+                \label{tbl:generators}
+            \end{table}
 
+        \item[\transformer{}] \hfill \\
+            This tool transforms \smt{} problems.
+It supports several transformers and options that specify its output and input.
+Table~\ref{tbl:transformers} describes them.
+The following transformers also preserve problem satisfiability: \textit{translate}, \textit{reverse}.
+\cite{ifaz}
             \hfill \\
 
-        \item[\transformer{}] \hfill \\
-
-            This tool transforms \smt{} problems.. It supports several transformers and options that specify its output and input. The transformers it implements are: \\
-
-            \todo{Dmitry: maybe add notes about SAT preservation?}
-
+            \begin{table}
+                \centering
                 \begin{tabular}{|l|l|}
@@
                     \textbf{Name}        & \textbf{The transformer ...} \\ \hline
-                fuzz          & Randomly replaces literals and operators with similar ones. \\ \hline
-                graft         & For each sort, swaps a random non-leaf node with a leaf node. \\ \hline
-                multiply      & Multiplies each number by N, and repeats each character N times. \\ \hline
-                nop           & Does nothing. \\ \hline
-                reverse       & Reverses all string literals and concat arguments. \\ \hline
-                rotate        & Performs a random syntax tree rotation on two concats. \\ \hline
-                translate     & Maps every character X to a different character Y. \\ \hline
-                unprintable   & Randomly replaces all characters in literals with unprintable ones. \\ \hline
+                    \textit{fuzz}        & Randomly replaces literals and operators with similar ones. \\ \hline
+                    \textit{graft}       & For each sort, swaps a random non-leaf node with a leaf node. \\ \hline
+                    \textit{multiply}    & Multiplies each number by N, and repeats each character N times. \\ \hline
+                    \textit{nop}         & Does nothing. \\ \hline
+                    \textit{reverse}     & Reverses all string literals and concat arguments. \\ \hline
+                    \textit{rotate}      & Performs a random syntax tree rotation on two concats. \\ \hline
+                    \textit{translate}   & Maps every character X to a different character Y. \\ \hline
+                    \textit{unprintable} & Randomly replaces all characters in literals with unprintable ones. \\ \hline
                 \end{tabular}
-
-            \hfill \\
+                \caption{\transformer{} transformers}
+                \label{tbl:transformers}
+            \end{table}
 
@@
             This tool takes as input an \smt{} problem, and outputs its properties, such as: numbers of string variables and literals, max/median syntactic depth of expressions, and max/median length of literals.
-
-            \hfill
+            \hfill \\
 
@@
 It generates a problem of the form\footnote{Variable declarations omitted for brevity.}:
+        \begin{align*}
+            & \texttt{(assert (str.in.re X}\; R_0\; \texttt{))} \\
+            & \texttt{(assert (str.in.re X}\; R_n\; \texttt{))}* \\
+            & \texttt{(assert (<= Min (str.len X)))}? \\
+            & \texttt{(assert (<= (str.len X)) Max)}?
+        \end{align*}
+
+        where $R_i \in RegEx$, and $Min, Max \in Int$.
+More simply, the problem is a set of one or more regex constraints on a single variable, with optional maximum and minimum lengths constraints.
+The regex constraints $R$ are each of the form:
 
         \begin{align*}
-            \langle problem \rangle  & ::= \langle membership \rangle \; \langle membership \rangle * \\
-            \langle membership \rangle & ::= \texttt{(assert (str.in.re X}\; R\; \texttt{))}
+            & \texttt{(re.++}\; T_0\; T_1\; \texttt{...}\; T_n\; \texttt{)}
         \end{align*}
 
-        where $R \in RegEx$. More simply, the problem is a set of one or more regex constraints on a single variable.
+        and each $T_i$ is a recursive term of the form:
 
-        \todo{Dmitry: further describe the properties of $R$.}
+        \begin{align*}
+            & \texttt{(re.*}\; T_{i_j}\; \texttt{) | (re.+}\; T_{i_j}\; \texttt{) | (re.union}\; T_{i_{j_1}}\; T_{i_{j_2}}\; \texttt{)}
+        \end{align*}
+
+        where $j$ a specified depth of recursion.
+Terms at depth 0 are regex constants.
+Informally, this form describes a concatenation of regex terms.
+Each term is a random nested regex operator (chosen from regex Kleene star, repetition, and union), up to a specified depth, terminating in a regex literal.
+Below is example regex (with spacing added for clarity) of depth 2 produced by this scheme:
+
+        \begin{align*}
+            & ((\texttt{a}|\texttt{b})|(\texttt{cc})+)\quad ((\texttt{ddd})*)+\quad ((\texttt{ee})+|(\texttt{fff})*)
+        \end{align*}
+
+        \fuzzer{} can also transform the instances it generates.
+All of the transformers in \transformer{} can operate on regex terms.
+They can multiply and permute regex literals (e.g.
+\textit{reverse}, \textit{multiply}, \textit{translate}), randomly replace regex operators (e.g.
+\textit{fuzz}), and manipulate the syntax tree of a regex problem (e.g.
+\textit{graft}, \textit{rotate}).
 
@@
 
-        \fuzzer{} can be used to generate static benchmarks as described in Section~\ref{sec:problems}.
+        \fuzzer{} can be used to generate problems to be saved as static suites like those in Section~\ref{sec:problems}.
 It can also be used in a randomised fashion for exploratory debugging.
@@
 
-        {\scriptsize\begin{verbatim}
-while stringfuzzg -r random --num-terms 1000 | tee problem.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do
+        {\scriptsize\begin{verbatim}while stringfuzzg -r random --num-terms 1000 | tee problem.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do
     sleep 0

### 2018-01-29 includes/abstract.tex
a pass

--- 2018-01-18 includes/abstract.tex
@@
 
-    In this paper we present \fuzzer{}: an \smtlib{} problem fuzzer and generator for string solvers.
-We provide a rich repository of problems we generated with \fuzzer{} in \smt{} format.
-We also analyse \numSolvers{} mature string solvers: \theSolvers{}.
-We use \fuzzer{} to craft inputs that elicit poor performance in \us{} and \cvc{}, and analyse the causes of the performance degradations.
-We then describe an algorithm to mitigate the performance degradation in \us{}.
-Finally, we describe several bugs in \us{} that were exposed by \fuzzer{}.
+    In this paper, we introduce \fuzzer{}: a modular \smt{} problem transformer and generator for string solvers.
+We supply a repository of problems generated by \fuzzer{} in \smtfull{} format.
+We systemically compare \theSolvers{} on groups of such problems focusing on different combinations of string operators, and identify problems that are particularly challenging for some solvers.
+We briefly explain our observations and showcase how \fuzzer{} helped identify causes of the performance degradations in \us{}.
 

### 2018-01-29 includes/experiment.tex
Removing a section for now.
a pass

@@
 \label{sec:data}
+\vspace{-0.1in}
 
@@
 
-    \begin{figure}[H]
+    \begin{figure}[h]
+        \vspace{-0.2in}
         \begin{subfigure}{.5\textwidth}
             \includegraphics[width=\textwidth]{data/graphs/concats-extracts-small.png}                   
+            \vspace{-0.25in}
+            \caption{Performance on concats-extracts-small} 
             \label{fig:concats-extracts-small}
-            \caption{Performance on concats-extracts-small}
         \end{subfigure}
@@
             \includegraphics[width=\textwidth]{data/graphs/different-prefix.png}            
+            \vspace{-0.25in}
+            \caption{Performance on different-prefix}
             \label{fig:different-prefix}
-            \caption{Performance on different-prefix}
         \end{subfigure}
+        \vspace{-0.1in}
         \caption{Problems hard for \cvc{}}
         \label{fig:cvc-hard}
+        \vspace{-0.3in}
     \end{figure}
 
-    \begin{figure}[H]
+    \begin{figure}[h]
+    \vspace{-0.25in}
         \begin{subfigure}{.5\textwidth}
@@
             \label{fig:concats-balanced}
+            \vspace{-0.25in}
             \caption{Performance on concats-balanced}
@@
             \label{fig:concats-small}
+            \vspace{-0.25in}
             \caption{Performance on concats-small}
         \end{subfigure}
+        \vspace{-0.1in}
         \caption{Problems hard for \us{}}
         \label{fig:z3str3-hard}
+        \vspace{-0.3in}
     \end{figure}
 
-\section{Analyses}
-\label{sec:analysis}
+\section{Usefulness to \us{}: A Case Study}
+\vspace{-0.1in}
 
-    In this section, we analyse our experimental results.
-We discuss the causes of \us{}'s poor performance on the two problem suites: \textit{concats-balanced} and \textit{concats-big}.
-We were not equipped well enough to debug the behaviours of the other solvers, but we provide our data in hopes that they will be useful to the solvers' authors.
+        We describe the defects and missing heuristics exposed by \fuzzer{} to illustrate why \fuzzer{} is a valuable asset in solver developments.
 
-    \subsection{\us{} on concats-balanced}
+\vspace{-0.15in}
+\subsection{Defects discovered and fixed in \us{}}
+\vspace{-0.1in}
 
-        \todo{Dmitry with help: Explain why \us{} performs poorly on this suite.}
+The first issue we found caused \us{} to perform poorly when equivalence classes 
+of arithmetic terms were very large (e.g. the lengths of many strings were equal s
+to 0). This issue was detected by the \texttt{Concats} problem suite. The slowdown 
+was caused by a loop over terms of such equivalence class to search for an 
+integer constant. The fix was to check the root of the equivalence class for the 
+integer constant, as Z3 makes "interpreted terms" (e.g. constants) the root of 
+equivalence classes whenever possible. This issue was last observed in commit 
+\texttt{6308636}, and was fixed in commit \texttt{3865c45}.
+
+The second issue, which was exposed by the \texttt{Lengths} suite, caused \us{} to 
+perform poorly when a variable has a large length constraint. The slowdown was 
+caused by the solver performing a linear search for a satisfying length when 
+producing a model for the variable. This issue was an inconsistency between the 
+implementation and the behavior described in the \us{} paper \cite{z3str3}. 
+This issue was last observed in commit \texttt{66bc68f}, and was fixed in commit 
+\texttt{7b536e9}.
+
+\vspace{-0.15in}    
+\subsection{Solving heuristics}
+\vspace{-0.1in}
+
+Discovering heuristics is crucial for solver efficacy improvements. Take 
+conflicting constraint detection as an example. Solvers will eventually catch 
+the offending terms, if they follow the string constraint solving algorithms and 
+gradually propagate the (dis)equivalences discovered along the way. However, in 
+many scenarios, a solver may be able to detect the conflicts before it tries to 
+figure out the relationships among sub-terms and actually propagates the facts. 
+The benefits are clear. It saves the efforts to reason about sub-terms and 
+propagate the observations. As reported in existing works, heuristics usually 
+lead to significant improvements. However, this is an extremely challenging 
+process as the heuristic are usually learned from examples but it's usually hard 
+to having multiple instances confirming such inefficiencies in the first place.
+
+The instances in the \texttt{concats-big} generated by \fuzzer{} helped us 
+discover a missing heuristic in \us{}. In particular, \us{} didn't make full use 
+of the solving context (e.g. some terms are empty strings) to simplify the 
+concatenations of a long list of string terms before trying to reason about the 
+equivalences among sub-terms. It hence introduced a large number of unnecessary 
+intermediate variables and fact propagations. We partially fixed this issue in 
+our develop branch and observed some improvements.
+
+% In this section, we analyse our experimental results. We discuss the causes of 
+% \us{}'s poor performance on the two problem suites: \textit{concats-balanced} 
+% and \textit{concats-big}. We were not equipped well enough to debug the 
+% behaviours of the other solvers, but we provide our data in hopes that they will 
+% be useful to the solvers' authors.
+
+%     \subsection{\us{} on concats-balanced}
+%         \todo{Dmitry with help: Explain why \us{} performs poorly on this suite.}
 
@@
 
-    \subsection{\us{} on concats-big}
+    % \subsection{\us{} on concats-big}
 
-        \todo{Dmitry with help: Explain why \us{} performs poorly on this suite.}
+    %     \todo{Dmitry with help: Explain why \us{} performs poorly on this suite.}
 

### 2018-01-29 includes/introduction.tex
Adding more sections. Adding references.
a pass

@@
 
-    Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and useful in practice.
-\theSolvers{}\cite{cvc4}\cite{z3str3} are \numSolvers{} such solvers.
-Moreover a standard input language for problem instances, \smtfull{}\cite{smt}, has been developed and widely adopted.
-To validate their solvers, many authors have relied on hand-crafted input suites or real-world examples from industrial applications \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}.
-Indeed several suites of industrial and hand-crafted problems have been compiled \cite{kaluza} \cite{kausler} to both validate solvers and benchmark their performance.
-However, though these suites help debug solvers, they do not age well.
-As solvers continue to grow, fixed benchmarks leave more and more functionality untested.
+    Many SMT solvers supporting the theory of strings (e.g., CVC4 \cite{cvc4},  Z3str2 \cite{z3str2}, Norn \cite{norn} and Z3str3 \cite{z3str3}) have been developed over the past decade.
+To validate and benchmark their solvers, many authors have relied on hand-crafted input suites \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests} or real-world examples from industrial applications \cite{kaluza} \cite{kausler}.
+These test suites have helped developers identify implementation defects and develop more sophistic solving heuristics.
+Although extremely helpful, these suites can only cover a limited range of the problem space because they are either manually created or translated from carefully developed programs.
 
-    We introduce a modular fuzzer for string solvers, \fuzzer{}, and describe its utility as an exploratory validation tool.
-We show its effectiveness by presenting defects and limitations we were able to find in leading solvers.
+    Fuzzing, on the other hand, has already been widely used in similar scenarios to systematically generate more diverse test cases.
+Guided by different rules, it can also be applied to generate different instances that are particularly designed to challenge selected capacities.
+Inspired by traditional fuzzers, we introduce a modular fuzzer for string solvers, \fuzzer{}, and describe its utility as an exploratory validation tool.
+We demonstrate its effectiveness by presenting defects and limitations we were able to identify in leading solvers.
+%     Moreover, a standard input language for problem instances, \smtfull{}\cite{smt}, has been developed and widely adopted.
 
@@
 We briefly document its components and modular architecture.
-We provide some motivating usage patterns to demonstrate its usefulness as an exploratory tool for validating solvers.
+We provide example usages to demonstrate its usefulness as an exploratory tool for validating solvers.
 We additionally detail its regex-generating and transforming capabilities.
-            \item \textbf{A repository of \smtfull{} problems}: We present a repository of \smtfull{} string and regex problem suites we generated with \fuzzer{}.
+            \item \textbf{A repository of \smtfull{} problems}: We present a repository of \smtfull{} string and regex problem suites we generated using \fuzzer{}.
 We demonstrate the usefulness of these suites by revealing specific defects they helped uncover and fix in \us{}.
-            \item \textbf{Experimental Results}: We present experimental runs of \theSolvers{} on the \fuzzer{} suites: \theSuites{}.
-We picked these suites because they uniquely made some solvers perform poorly, but not others.
-            \item \textbf{Analysis}: We analyse our experimental results by inspecting the execution traces of the solvers on the given problems.
-For \us{} we pinpoint algorithmic limitations that cause the poor performance.
+            \item \textbf{Experimental Results}: We compare \theSolvers{} on the \fuzzer{} suites and selectively present the experimental result on \theSuites{}.
+We highlighted these suites because they uniquely made some solvers perform poorly, but not others.
+            \item \textbf{Analysis}: We analyze our experimental results by inspecting the execution traces of the solvers on the given problems.
+For \us{}, we pinpoint algorithmic limitations that cause the poor performance.
 For other solvers, we draw superficial conclusions based solely on the execution traces, and invite their authors to conduct further analysis.

### 2018-01-29 includes/problems.tex
Adding placeholder reference for Ifaz's paper. Removing some TODOs.
a pass

@@
 \label{sec:problems}
+\vspace{-0.1in}
 
-    We generated several suites of string and regex problems using \fuzzer{}.
-\footnote{For review anonymity, we removed the link to the problem repository.
-It will be provided separately in the artifact submission track and will appear in the final version of the paper.} Table~\ref{tbl:generated} describes the \texttt{generated} suite that we generated using \generator{}.
+\subsection{Generated suite}
+\vspace{-0.1in}
+    We generated several suites of string and regex problems using \fuzzer{}\footnote{For review anonymity, we removed the link to the source code.
+It will be provided separately in the artifact submission.}.
+Table~\ref{tbl:generated} describes the suite \texttt{generated} by \generator{}.
 
-    \begin{table}
+\begin{table}[h]
+\vspace{-0.4in}
 \centering
+\caption{\generator{}-generated problem sets.}
+\label{tbl:generated}
+{
+  \footnotesize
+  \bgroup
+  \def\arraystretch{1}
+  \resizebox{0.8\columnwidth}{!}{
         \begin{tabular}{|l|l|}
@@
         \end{tabular}  
-        \caption{\generator{}-generated problem sets.}
-        \label{tbl:generated}
+  }
+  \egroup
+  \vspace{-0.2in}
+}
 \end{table}
 
+%     \begin{table}
+%         \centering
+%         \begin{tabular}{|l|l|}
+%             \hline
+%             \textbf{Name}             & \textbf{Problems have ...} \\ \hline
+%             \textit{Concats}          & A single, deep tree of concats. \\ \hline
+%             \textit{Concats-Extracts} & A single concat tree, and random character extractions. \\ \hline
+%             \textit{Lengths}          & A single, large length constraint on a variable. \\ \hline
+%             \textit{Lengths-Concats}  & Variables and their concats, each with fixed lengths. \\ \hline
+%             \textit{Overlaps}         & A formula of the form A.X = X.B. \\ \hline
+%             \textit{Regex}            & A test for regex membership of arbitrary complexity. \\ \hline
+%             \textit{Many-Regexes}     & A test for membership in many random regexes. \\ \hline
+%             \textit{Regex-Deep}       & A test for membership in a regex with many nested operators. \\ \hline
+%             \textit{Regex-Pair}       & A test for membership in one regex, but not another. \\ \hline
+%             \textit{Regex-Lengths}    & A test for membership in a regex, and a length constraint. \\ \hline
+%         \end{tabular}
+%         \caption{\generator{}-generated problem sets.}
+%         \label{tbl:generated}
+%     \end{table}
+
+\vspace{-0.2in}
+\subsection{Transformed suite}
+\vspace{-0.1in}
     The \texttt{transformed} suite contains benchmarks derived from existing seed problems by iteratively applying \transformer{}.
+Table~\ref{tbl:transformed} shows the overview.
 Every problem in the suite is named according to its seed and the transformations it undertook.
-For example, a hypothetical file named ``seed-fuzz-graft.smt2'' began as a file named ``seed.smt'' and was transformed twice: first by fuzz, and then by graft.
-The suite is divided into two categories.
-For an overview see Table~\ref{tbl:transformed}.
+For example, input \texttt{seed-fuzz-graft.smt2} was transformed by applying \texttt{fuzz} and then \texttt{graft} from \texttt{seed.smt2}.
 
-    \begin{table}
+\begin{table}[h]
+\vspace{-0.35in}
 \centering
+\caption{Transformed problem sets generated by \transformer{}.}
+\label{tbl:transformed}
+{
+  \footnotesize
+  \bgroup
+  \def\arraystretch{1}
+  \resizebox{0.6\columnwidth}{!}{
           \begin{tabular}{|l|l|r|}
@@
         \end{tabular}
-        \caption{\transformer{}-generated problem sets.}
-        \label{tbl:transformed}
+    }
+  \egroup
+  \vspace{-0.2in}
+}
 \end{table}
 
-    The first category, labeled Amazon, started as two seed files.
-    The first seed, z3-regex-1.smt2, encodes the assertions ``S not in aaabbb*'' and ``S in aaa*bbb*'' for a string constant S,
-    while the second seed, z3-regex-2-negative.smt2, encodes the assertions ``S in aaabbb*'' and ``S not in aaa*bbb*''.
-    Both problems come from our industrial collaborators.
-    In total, 516 unique problems were generated from these two seeds.
+%     \begin{table}
+%         \centering
+%         \begin{tabular}{|l|l|r|}
+%             \hline
+%             \textbf{Name}   & \textbf{Seed}                            & \textbf{Quantity} \\ \hline
+%             \textit{Amazon} & Two industrial regex membership problems & 516\\ \hline
+%             \textit{Regex}  & Z3str2 regular expression test suite     & 10,577\\ \hline
+%         \end{tabular}
+%         \caption{\transformer{}-generated problem sets.}
+%         \label{tbl:transformed}
+%     \end{table}
 
-    The second category, Regex, is seeded by the z3str2 regular expression test suite \cite{z3str2-tests}.
+    The Amazon category is obtained from two seeds: (1) \texttt{z3-regex-1.smt2} encodes the assertions \texttt{(S not in aaabbb*)} and \texttt{(S in aaa*bbb*)} for a string constant S; (2) \texttt{z3-regex-2-negative.smt2} includes regex \texttt{(S in aaabbb*)} and \texttt{(S not in aaa*bbb*)}.
+    Both problems come from our industrial collaborators. In total, 516 unique problems were generated from these two seeds.
+
+    The Regex category is seeded by the z3str2 regular expression test suite \cite{z3str2-tests}.
     This test suite contains 42 problems dealing with a wide variety of regular expressions.
-    Through cumulative transformations, as before, we were able to produce 10,577 unique benchmarks.
-
-    \subsection{Usefulness to \us{}}
-
-        This section describes the bugs we discovered in \us{} (that were subsequently fixed) by testing it with the \fuzzer{} problem suites.
-
-        The first bug we found caused \us{} to perform poorly when equivalence classes of arithmetic terms was very large (e.g.
-where many strings were equal to the empty string, and thus had length 0).
-We discovered this bug using the \textit{Concats} problem suite.
-The slowdown was caused by a loop over the equivalence class of these terms to search for an integer constant.
-The fix was to check the root of the equivalence class for the integer constant, as Z3 makes "interpreted terms" (i.e.
-constants) the root of equivalence classes whenever possible.
-This bug was last observed in commit 6308636, and was fixed in commit 3865c45.
-
-        The second bug we found caused \us{} to perform poorly when a variable had a large length constraint.
-We discovered this bug using the \textit{Lengths} problem suite.
-The slowdown was caused by the solver performing a linear search for a satisfying length when producing a model for the variable.
-This bug was an inconsistency between the implementation and the behaviour described in the \us{} paper \cite{z3str3}.
-This bug was last observed in commit 66bc68f, and was fixed in commit 7b536e9.
-
-        \todo{Federico - Can we describe the floating point error we found?}
-
-        \todo{Dmitry: maybe show graphs with before and after?}
+    Through cumulative transformations, we have $10,577$ unique benchmarks.

### 2018-01-29 includes/stringfuzz.tex
Removing stringmerge for now.
a pass

@@
 \label{sec:fuzzer}
+\vspace{-0.1in}
 
-    This section describes the fuzzer \fuzzer{}, which generates new \smtfull{} problems and transforms existing ones.
-\fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyse \smtfull{} string problems.
+%     This section describes the fuzzer \fuzzer{}, which generates new \smtfull{} problems and transforms existing ones. 
+    \fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyze \smtfull{} string problems.
 It can either be installed from source, or from the Python PIP package repository.
-\footnote{For review anonymity, we removed the link to the source code.
-It will be provided separately in the artifact submission track and will appear in the final version of the paper.}
 
-    The \fuzzer{} code is organised to be easily extended: all generators and transformers are independent Python modules.
+%     {\it For review anonymity, we removed the link to the source code. It will be provided separately in the artifact submission.}
+
+    \fuzzer{} is organized to be easily extended: all generators and transformers are independent Python modules.
 Its components are also implemented as \unix{} ``filters'', to enable easy integration with other tools (including themselves).
-For example, the outputs of generators can be piped directly into transformers, and transformers can be chained to produce a tuned stream of challenging inputs to a solver.
+For example, the outputs of generators can be piped into transformers, and transformers can be chained to produce a stream of tuned inputs to a solver.
 
@@
 
-    \begin{description}
+\vspace{-0.15in}
+\subsection{\generator{}}
+% \vspace{-0.1in}
 
-        \item[\generator{}] \hfill \\
-            This tool generates \smt{} problems. It supports several generators and options that specify its output. Table~\ref{tbl:generators} describes them.
-            \hfill \\
+\generator{} generates \smt{} problems. It supports several generators and options that specify its output. Details can be found in Table~\ref{tbl:generators}.
 
-            \begin{table}
+\begin{table}[t]
+\vspace{-0.25in}
 \centering
+\caption{\generator{} generators.}
+\label{tbl:generators}
+{
+  \footnotesize
+  \bgroup
+  \def\arraystretch{1}
+  \resizebox{0.8\columnwidth}{!}{
                   \begin{tabular}{|l|l|}
@@
                 \end{tabular}
-                \caption{\generator{} generators}
-                \label{tbl:generators}
+  }
+  \egroup
+\vspace{-0.2in}
+}
 \end{table}
 
-        \item[\transformer{}] \hfill \\
+\vspace{-0.15in}
+\subsection{\transformer{}}
+% \vspace{-0.1in}
+
 This tool transforms \smt{} problems.
-It supports several transformers and options that specify its output and input.
-Table~\ref{tbl:transformers} describes them.
-The following transformers also preserve problem satisfiability: \textit{translate}, \textit{reverse}.
-\cite{ifaz}
-            \hfill \\
+It supports several transformers and options that specify its output and input, which are explained in Table~\ref{tbl:transformers}.
+Note that transformers \textit{translate} and \textit{reverse} also preserve problem satisfiability \cite{ifaz}.
 
-            \begin{table}
+\begin{table}[t]
+\vspace{-0.25in}
 \centering
+\caption{\transformer{} transformers}
+\label{tbl:transformers}
+{
+  \footnotesize
+  \bgroup
+  \def\arraystretch{1}
+  \resizebox{0.8\columnwidth}{!}{
                 \begin{tabular}{|l|l|}
@@
                 \end{tabular}
-                \caption{\transformer{} transformers}
-                \label{tbl:transformers}
+  }
+  \egroup
+  \vspace{-0.2in}
+}
 \end{table}
 
-        \item[\texttt{stringstats}] \hfill \\
-            This tool takes as input an \smt{} problem, and outputs its properties, such as: numbers of string variables and literals, max/median syntactic depth of expressions, and max/median length of literals.
-            \hfill \\
+\vspace{-0.15in}
+\subsection{\texttt{stringstats}}
 
-        \item[\texttt{stringmerge}] \hfill \\
-            This tool takes as input two \smt{} problems and combines them into one problem.
+This tool takes an \smt{} problem as input and outputs its properties: the number of variables/literals, the max/median syntactic depth of expressions, the max/median literal length, etc.
 
-            \todo{Federico: describe \texttt{stringmerge}.}
+% \texttt{stringstats} is handy when analyzing a problem.
 
-    \end{description}
+%     \begin{description}
 
-    \subsection{Regex Fuzzing Capabilities}
+%         \item[\generator{}] \hfill \\
+%             This tool generates \smt{} problems. It supports several generators and options that specify its output. Table~\ref{tbl:generators} describes them.
+%             \hfill \\
+% 
+%             \begin{table}
+%                 \centering
+%                 \begin{tabular}{|l|l|}
+%                     \hline
+%                     \textbf{Name}        & \textbf{Generated Problems have ...} \\ \hline
+%                     \textit{concats}     & Long concats and optional random extracts. \\ \hline
+%                     \textit{lengths}     & Many variables (and their concats) with length constraints. \\ \hline
+%                     \textit{overlaps}    & An expression of the form A.X = X.B. \\ \hline
+%                     \textit{equality}    & An equality among concats, each with variables or constants. \\ \hline
+%                     \textit{regex}       & Regexes of varying complexity. \\ \hline
+%                     \textit{random-text} & Random, likely syntactically \textit{in}valid text. \\ \hline
+%                     \textit{random-ast}  & Random, but semantically \textit{valid} text. \\ \hline
+%                 \end{tabular}
+%                 \caption{\generator{} generators}
+%                 \label{tbl:generators}
+%             \end{table}
 
+%         \item[\transformer{}] \hfill \\
+%             This tool transforms \smt{} problems.
+It supports several transformers and options that specify its output and input.
+Table~\ref{tbl:transformers} describes them.
+The following transformers also preserve problem satisfiability: \textit{translate}, \textit{reverse}.
+\cite{ifaz}
+%             \hfill \\
+% 
+%             \begin{table}
+%                 \centering
+%                 \begin{tabular}{|l|l|}
+%                     \hline
+%                     \textbf{Name}        & \textbf{The transformer ...} \\ \hline
+%                     \textit{fuzz}        & Randomly replaces literals and operators with similar ones. \\ \hline
+%                     \textit{graft}       & For each sort, swaps a random non-leaf node with a leaf node. \\ \hline
+%                     \textit{multiply}    & Multiplies each number by N, and repeats each character N times. \\ \hline
+%                     \textit{nop}         & Does nothing. \\ \hline
+%                     \textit{reverse}     & Reverses all string literals and concat arguments. \\ \hline
+%                     \textit{rotate}      & Performs a random syntax tree rotation on two concats. \\ \hline
+%                     \textit{translate}   & Maps every character X to a different character Y. \\ \hline
+%                     \textit{unprintable} & Randomly replaces all characters in literals with unprintable ones. \\ \hline
+%                 \end{tabular}
+%                 \caption{\transformer{} transformers}
+%                 \label{tbl:transformers}
+%             \end{table}
+
+%         \item[\texttt{stringstats}] \hfill \\
+%             This tool takes as input an \smt{} problem, and outputs its properties, such as: numbers of string variables and literals, max/median syntactic depth of expressions, and max/median length of literals.
+%             \hfill \\
+
+        % \item[\texttt{stringmerge}] \hfill \\
+        %     This tool takes as input two \smt{} problems and combines them into one problem.
+
+        %     \todo{Federico: describe \texttt{stringmerge}.}
+
+%     \end{description}
+
+    \section{Regex Fuzzing Capabilities}
+    \vspace{-0.1in}
         \fuzzer{} can generate and transform problems with regular expression constraints.
-The command \texttt{stringfuzzg regex} invokes the regex problem generator, and has several options to control its output.
-It generates a problem of the form\footnote{Variable declarations omitted for brevity.}:
+The command \texttt{stringfuzzg regex} invokes the regex problem generator.
+It generates a problem of the form: %\footnote{Variable declarations omitted for brevity.}:
+        \begingroup
+        \footnotesize
         \begin{align*}
@@
         \end{align*}
-
+        \endgroup
         where $R_i \in RegEx$, and $Min, Max \in Int$.
@@
 The regex constraints $R$ are each of the form:
-
+        \begingroup
+        \footnotesize
         \begin{align*}
-            & \texttt{(re.++}\; T_0\; T_1\; \texttt{...}\; T_n\; \texttt{)}
+            & \texttt{(re.++}\; \ T_0\; \  T_1\; \texttt{...}\; T_n\; \texttt{)}
         \end{align*}
-
+        \endgroup
         and each $T_i$ is a recursive term of the form:
-
+        \begingroup
+        \footnotesize
         \begin{align*}
@@
         \end{align*}
-
+        \endgroup
         where $j$ a specified depth of recursion.
@@
 Below is example regex (with spacing added for clarity) of depth 2 produced by this scheme:
-
+        \begingroup
+        \footnotesize
         \begin{align*}
@@
         \end{align*}
+        \endgroup
 
-        \fuzzer{} can also transform the instances it generates.
+        {\it \fuzzer{} can also transform the instances it generates}.
 All of the transformers in \transformer{} can operate on regex terms.
 They can multiply and permute regex literals (e.g.
-\textit{reverse}, \textit{multiply}, \textit{translate}), randomly replace regex operators (e.g.
-\textit{fuzz}), and manipulate the syntax tree of a regex problem (e.g.
-\textit{graft}, \textit{rotate}).
+\texttt{reverse}, \texttt{multiply}, \texttt{translate}), randomly replace regex operators (e.g.
+\texttt{fuzz}), and manipulate the syntax tree (e.g.
+\texttt{graft}, \texttt{rotate}).
 
-    \subsection{Patterns}
+\section{Example Usages}
+\vspace{-0.1in}
 
-        \fuzzer{} can be used to generate problems to be saved as static suites like those in Section~\ref{sec:problems}.
+        \fuzzer{} can be used to generate problems to be saved as static suites.
 It can also be used in a randomised fashion for exploratory debugging.
-As a motivating example, the following usage can feed random problems to \cvc{} until it returns an error:
-
-        {\scriptsize\begin{verbatim}while stringfuzzg -r random --num-terms 1000 | tee problem.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do
+As an example, the following usage can feed random problems to \cvc{} until it returns an error:
+\begin{center}
+\vspace{-0.05in}
+\begin{varwidth}{\linewidth}
+{\scriptsize\begin{verbatim}while stringfuzzg -r random | tee problem.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do
     sleep 0
-done\end{verbatim}}
-
-        Some \unix{} scripting can yield other interesting results. For example the following script finds a regex problem on which \us{} times out after 5 seconds:
-
+done
+\end{verbatim}}
+\end{varwidth}
+\end{center}
+        Some \unix{} scripting can yield other interesting results. For example, the following script finds a regex problem on which \us{} times out after 5 seconds:
+\begin{center}
+\vspace{-0.1in}
+\begin{varwidth}{\linewidth}
         {\scriptsize\begin{verbatim}while true; do
@@
 done\end{verbatim}}
+\end{varwidth}
+\end{center}

### 2018-01-29 includes/abstract.tex
starting pass with abstract. All changes are suggestions.

@@
 \begin{abstract}
-
-    In this paper, we introduce \fuzzer{}: a modular \smt{} problem transformer and generator for string solvers.
-We supply a repository of problems generated by \fuzzer{} in \smtfull{} format.
-We systemically compare \theSolvers{} on groups of such problems focusing on different combinations of string operators, and identify problems that are particularly challenging for some solvers.
-We briefly explain our observations and showcase how \fuzzer{} helped identify causes of the performance degradations in \us{}.
-
+    Performant SMT solvers rely on powerful heuristics and highly optimized implementations
+    that need to be validated and tested. 
+    To do this researchers often depend 
+    on tedious to produce hand-crafted benchmarks, and hard to procure industrial suites.
+    In this paper we offer an alternative to string \smt{} solver developers: 
+    \fuzzer{}, a modular problem transformer and generator.
+    We showcase \fuzzer{} by producing a repository of \smtfull{} format problems;
+    systemically comparing \theSolvers{} on these problems; and 
+    identifying causes of performance degradations in \us{}.
 \end{abstract}

### 2018-01-29 includes/prior.tex
Fixing typos and descriptions.
one pass all the way to the end. Conclusion and related work need work.

@@
 
-    Naturally, many solver developers author their own test suites to validate their solvers \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}.
-In addition, several popular problem suites are publicly available for solver validation, such as the Kaluza \cite{kaluza} and Kausler \cite{kausler} suites.
+    Naturally, many solver developers author their own test suites to validate their solvers 
+    \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}. 
+    In addition, several popular problem suites are publicly available for solver validation, 
+    such as the Kaluza \cite{kaluza} and Kausler \cite{kausler} suites.
 
-    There are likewise several fuzzers and problem generators currently available, but none of them can generate or transform string and regex problems.
-For example the FuzzSMT\cite{fuzzsmt} tool generates \smt{} problems with bit vectors and arrays, but does not support strings or regexes.
-The SMTpp\cite{smtpp} tool preprocesses and simplifies problems, but does not generate new ones or fuzz existing ones.
+    There are likewise several fuzzers and problem generators currently available.
+    However, none of these fuzzers can generate and transform string and regex problems. 
+    \todo{I know we talked about this one before, but I'm confused by it again.}
+    For example the FuzzSMT\cite{fuzzsmt} tool generates \smt{} problems with bit vectors and arrays, 
+    but does not support strings or regexes. 
+    The SMTpp\cite{smtpp} tool pre-processes and simplifies problems, but does not generate new ones or fuzz existing ones.
 

### 2018-01-29 includes/experiment.tex

@@
 
-    We generated several problem suites with \fuzzer{} that made one solver perform poorly, but not others.
-These suites are \theSuites{}.
-Figure~\ref{fig:cvc-hard} shows the suites that were uniquely difficult for \cvc{}.
+    We generated several problem suites with \fuzzer{} that each made a solver perform poorly, but not the others. 
+    These suites are \theSuites{}. For example, Figure~\ref{fig:cvc-hard} shows the suites that were uniquely difficult for \cvc{}. 
     Figure~\ref{fig:z3str3-hard} shows the suites that were uniquely difficult for \us{}. 
-All experiments were run in series on the same Linux computer, with a timeout of 15 seconds.
+    We ran all experiments in series on a COMPUTER DESCRIPTION AND EXACT SPECS!!, with a timeout of 15 seconds.
 
@@
 
-        We describe the defects and missing heuristics exposed by \fuzzer{} to illustrate why \fuzzer{} is a valuable asset in solver developments.
+        We illustrate \fuzzer{}'s utility by describing the defects and vulnerable heuristics it exposed.
 
@@
 The first issue we found caused \us{} to perform poorly when equivalence classes 
-of arithmetic terms were very large (e.g. the lengths of many strings were equal s
-to 0). This issue was detected by the \texttt{Concats} problem suite. The slowdown 
+of arithmetic terms were very large (e.g. the lengths of many strings were equal
+to 0\todo{HUH!?}). This issue was detected by the \texttt{Concats} problem suite. The slowdown 
 was caused by a loop over terms of such equivalence class to search for an 
@@
 integer constant, as Z3 makes "interpreted terms" (e.g. constants) the root of 
-equivalence classes whenever possible. This issue was last observed in commit 
-\texttt{6308636}, and was fixed in commit \texttt{3865c45}.
+equivalence classes whenever possible. This issue was fixed in commit \texttt{3865c45}.
 
@@
 implementation and the behavior described in the \us{} paper \cite{z3str3}. 
-This issue was last observed in commit \texttt{66bc68f}, and was fixed in commit 
+This issue was fixed in commit 
 \texttt{7b536e9}.
@@
 Discovering heuristics is crucial for solver efficacy improvements. Take 
-conflicting constraint detection as an example. Solvers will eventually catch 
+conflicting constraint detection as an example\todo{describe what it is. what are offending terms?}. Solvers will eventually catch 
 the offending terms, if they follow the string constraint solving algorithms and 
@@
 many scenarios, a solver may be able to detect the conflicts before it tries to 
-figure out the relationships among sub-terms and actually propagates the facts. 
-The benefits are clear. It saves the efforts to reason about sub-terms and 
-propagate the observations. As reported in existing works, heuristics usually 
+figure out the relationships among sub-terms and actually propagate the facts. 
+The benefits are clear. It saves the effort to reason about sub-terms and 
+propagate the observations. As reported in existing work, heuristics usually 
 lead to significant improvements. However, this is an extremely challenging 
-process as the heuristic are usually learned from examples but it's usually hard 
-to having multiple instances confirming such inefficiencies in the first place.
+process because it is usually hard to have multiple instances confirming such inefficiencies in the first place.
 
 The instances in the \texttt{concats-big} generated by \fuzzer{} helped us 
-discover a missing heuristic in \us{}. In particular, \us{} didn't make full use 
+discover a vulnerable heuristic in \us{}. In particular, \us{} didn't make full use 
 of the solving context (e.g. some terms are empty strings) to simplify the 

### 2018-01-29 includes/introduction.tex

@@
 
-    Many SMT solvers supporting the theory of strings (e.g., CVC4 \cite{cvc4},  Z3str2 \cite{z3str2}, Norn \cite{norn} and Z3str3 \cite{z3str3}) have been developed over the past decade.
-To validate and benchmark their solvers, many authors have relied on hand-crafted input suites \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests} or real-world examples from industrial applications \cite{kaluza} \cite{kausler}.
+    Many SMT solvers supporting the theory of strings (e.g., CVC4 \cite{cvc4},  Z3str2 \cite{z3str2}, Norn \cite{norn} 
+    and Z3str3 \cite{z3str3}) have been developed over the past decade. 
+    To validate and benchmark their solvers, many developers have relied on hand-crafted suites \cite{cvc4-tests} 
+    \cite{z3str3-tests} \cite{z3str2-tests} or industrial examples \cite{kaluza} \cite{kausler}. 
     These test suites have helped developers identify implementation defects and develop more sophistic solving heuristics. 
-Although extremely helpful, these suites can only cover a limited range of the problem space because they are either manually created or translated from carefully developed programs.
+    However, the suites cover a limited problem space, can be difficult to create, and hard to acquire.
 
-    Fuzzing, on the other hand, has already been widely used in similar scenarios to systematically generate more diverse test cases.
-Guided by different rules, it can also be applied to generate different instances that are particularly designed to challenge selected capacities.
-Inspired by traditional fuzzers, we introduce a modular fuzzer for string solvers, \fuzzer{}, and describe its utility as an exploratory validation tool.
-We demonstrate its effectiveness by presenting defects and limitations we were able to identify in leading solvers.
-%     Moreover, a standard input language for problem instances, \smtfull{}\cite{smt}, has been developed and widely adopted.
-
-    \subsection{Contributions}
-
+    In contrast, fuzzing can systematically generate diverse test cases with little effort. 
+    Guided by different rules, fuzzing can also be applied to generate instances designed to challenge selected capacities. 
+    Inspired by traditional fuzzers, we introduce a fuzzer for string solvers, \fuzzer{}, 
+    and describe its utility as an exploratory validation tool. 
+    We demonstrate its effectiveness by presenting defects and limitations it helped identify in leading solvers.
+    More specifically, we contribute
     \begin{enumerate}
-            \item \textbf{The \fuzzer{} tool}: We describe a modular fuzzer which can transform and generate \smtfull{} string and regex problems.
-We briefly document its components and modular architecture.
-We provide example usages to demonstrate its usefulness as an exploratory tool for validating solvers.
+        \item \textbf{The \fuzzer{} tool}. We describe a modular fuzzer which can transform and generate \smtfull{} string and regex problems. We briefly document its components and architecture. 
+        We provide examples to demonstrate its usefulness as an exploratory tool for validating solvers. 
         We additionally detail its regex-generating and transforming capabilities.
-            \item \textbf{A repository of \smtfull{} problems}: We present a repository of \smtfull{} string and regex problem suites we generated using \fuzzer{}.
-We demonstrate the usefulness of these suites by revealing specific defects they helped uncover and fix in \us{}.
-            \item \textbf{Experimental Results}: We compare \theSolvers{} on the \fuzzer{} suites and selectively present the experimental result on \theSuites{}.
-We highlighted these suites because they uniquely made some solvers perform poorly, but not others.
-            \item \textbf{Analysis}: We analyze our experimental results by inspecting the execution traces of the solvers on the given problems.
-For \us{}, we pinpoint algorithmic limitations that cause the poor performance.
-For other solvers, we draw superficial conclusions based solely on the execution traces, and invite their authors to conduct further analysis.
+        \item \textbf{A repository of \smtfull{} problems}. We present a repository of \smtfull{} string and regex problem suites 
+        generated by \fuzzer{}. We demonstrate the usefulness of these suites by revealing specific defects they helped uncover and fix in \us{}.
+        \item \textbf{Experimental Results and Analysis}. We compare \theSolvers{} on the \fuzzer{} suites and present the experimental results. 
+        We highlight some suites that cause some solvers to perform poorly poorly in comparison to the others,
+        and inspect solver execution traces for some. In the case of \us{}, we
+        pinpoint algorithmic limitations that cause the identified poor performance.
     \end{enumerate}

### 2018-01-29 includes/stringfuzz.tex

@@
 %     This section describes the fuzzer \fuzzer{}, which generates new \smtfull{} problems and transforms existing ones. 
-    \fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyze \smtfull{} string problems.
-It can either be installed from source, or from the Python PIP package repository.
+    \fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyze 
+    \smtfull{} string problems. It can either be installed from source, or from the Python PIP package repository.
 
@@
     Its components are also implemented as \unix{} ``filters'', to enable easy integration with other tools (including themselves). 
-For example, the outputs of generators can be piped into transformers, and transformers can be chained to produce a stream of tuned inputs to a solver.
+    For example, the outputs of generators can be piped into transformers, and transformers can be chained to produce a stream of 
+    tuned inputs to a solver.
 
@@
 
-\generator{} generates \smt{} problems. It supports several generators and options that specify its output. Details can be found in Table~\ref{tbl:generators}.
+\generator{} generates \smt{} problems. It supports several generators and options that specify its output. 
+Details can be found in Table~\ref{tbl:generators}.
 
@@
 
-This tool transforms \smt{} problems.
-It supports several transformers and options that specify its output and input, which are explained in Table~\ref{tbl:transformers}.
-Note that transformers \textit{translate} and \textit{reverse} also preserve problem satisfiability \cite{ifaz}.
+\transformer{} transforms \smt{} problems. Table~\ref{tbl:transformers} lists the several transformers and configurations available.
+Note that transformers \textit{translate} and \textit{reverse} preserve problem satisfiability \cite{ifaz} in specific cases.
 
@@
 
-This tool takes an \smt{} problem as input and outputs its properties: the number of variables/literals, the max/median syntactic depth of expressions, the max/median literal length, etc.
+This tool takes an \smt{} problem as input and outputs a number of properties.
+Properties include the number of variables/literals, the max/median syntactic depth of expressions, and the max/median literal length.
 
@@
         \fuzzer{} can be used to generate problems to be saved as static suites.
-It can also be used in a randomised fashion for exploratory debugging.
+It can also be used in a randomized fashion for exploratory debugging.
 As an example, the following usage can feed random problems to \cvc{} until it returns an error:

### 2018-01-30 includes/experiment.tex
editing first pass

--- 2018-01-24 includes/experiment.tex
@@
 All experiments were run in series on the same Linux computer, with a timeout of 15 seconds.
+\todo{Specify CPU, memory}
 
-    \begin{figure}[H]
+    \begin{figure}[h]
+        \vspace{-0.2in}
         \begin{subfigure}{.5\textwidth}
             \includegraphics[width=\textwidth]{data/graphs/concats-extracts-small.png}                   
+            \vspace{-0.25in}
+            \caption{Performance on concats-extracts-small} 
             \label{fig:concats-extracts-small}
-            \caption{Performance on concats-extracts-small}
         \end{subfigure}
@@
             \label{fig:concats-small}
+            \vspace{-0.25in}
             \caption{Performance on concats-small}
         \end{subfigure}
+        \vspace{-0.1in}
         \caption{Problems hard for \us{}}
         \label{fig:z3str3-hard}
+        \vspace{-0.3in}
     \end{figure}
 
-\section{Analyses}
-\label{sec:analysis}
+\section{Usefulness to \us{}: A Case Study}
+\vspace{-0.1in}
 
-    In this section, we analyse our experimental results.
-We discuss the causes of \us{}'s poor performance on the two problem suites: \textit{concats-balanced} and \textit{concats-big}.
-We were not equipped well enough to debug the behaviours of the other solvers, but we provide our data in hopes that they will be useful to the solvers' authors.
+        We describe the defects and missing heuristics exposed by \fuzzer{} to illustrate why \fuzzer{} is a valuable asset in solver development.
 
-    \subsection{\us{} on concats-balanced}
+\vspace{-0.15in}
+\subsection{Defects discovered and fixed in \us{}}
+\vspace{-0.1in}
 
-        \todo{Dmitry with help: Explain why \us{} performs poorly on this suite.}
+The first issue we found caused \us{} to perform poorly when equivalence classes 
+of arithmetic terms were very large (e.g. the lengths of many strings were equal
+to 0). This issue was detected by the \texttt{Concats} problem suite. The slowdown 
+was caused by a loop over terms in the same equivalence class to search for an 
+integer constant. The fix was to check the root of the equivalence class for the 
+integer constant, as Z3 makes ``interpreted terms'' (e.g. constants) the root of 
+equivalence classes whenever possible. This issue was last observed in commit 
+\texttt{6308636}, and was fixed in commit \texttt{3865c45}.
+
+The second issue, which was exposed by the \texttt{Lengths} suite, caused \us{} to 
+perform poorly when a variable has a large length constraint.
+The slowdown was caused by the solver performing a search for a satisfying length
+even when the input formula explicitly constrained the exact length of a string term.
+The fix was to check whether the integer solver had already assigned a length value
+before searching for length, and skip the search if this was the case.
+This issue was last observed in commit \texttt{66bc68f}, and was fixed in commit 
+\texttt{7b536e9}.    
+%The slowdown was  caused by the solver performing a linear search for a satisfying length when 
+%producing a model for the variable. This issue was an inconsistency between the 
+%implementation and the behavior described in the \us{} paper \cite{z3str3}. 
+%This issue was last observed in commit \texttt{66bc68f}, and was fixed in commit 
+%\texttt{7b536e9}.
+
+\vspace{-0.15in}    
+\subsection{Solving heuristics}
+\vspace{-0.1in}
+
+In order to improve the efficiency of any solver, discovering new heuristics is crucial.
+As an illustrative example, consider detection of conflicting constraints.
+A solver that follows the string constraint solving algorithm and gradually propagates
+the (dis)equalities discovered along the way will eventually detect a conflict.
+However, in many scenarios, a conflict can be discovered ``early'' before trying to
+figure out the relationships among subterms and propagating the facts.
+The benefits of this eager approach are clear: this saves the effort of reasoning about
+subterms and propagating observations, as a conflict will eventually be reached in either case,
+forcing conflict analysis and a backjump.
+As reported in existing works, heuristics of this form usually lead to significant improvements.
+However, the process of discovering such heuristics is extremely challenging,
+as they are usually learned from a class of examples whose commonalities
+are not always obvious or immediately indicative of such inefficiencies.
+
+The instances in the \texttt{concats-big} suite generated by \fuzzer{} helped us 
+discover a missing heuristic in \us{}. In particular, \us{} didn't make full use 
+of the solving context (e.g. some terms are empty strings) to simplify the 
+concatenations of a long list of string terms before trying to reason about the 
+equivalences among subterms. \us{} therefore introduced a large number of unnecessary
+intermediate variables and propagations.
+As an immediate consequence of the \texttt{concats-big} benchmarks, we were able to identify
+the factors common to these instances and rapidly formulate a hypothesis as to why they were
+performing poorly. This allowed us to move forward with the development of new heuristics
+to resolve these issues and achieve better performance.
+
+% In this section, we analyse our experimental results. We discuss the causes of 
+% \us{}'s poor performance on the two problem suites: \textit{concats-balanced} 
+% and \textit{concats-big}. We were not equipped well enough to debug the 
+% behaviours of the other solvers, but we provide our data in hopes that they will 
+% be useful to the solvers' authors.
+
+%     \subsection{\us{} on concats-balanced}
+%         \todo{Dmitry with help: Explain why \us{} performs poorly on this suite.}
 

### 2018-01-30 includes/introduction.tex
editing first pass

--- 2018-01-29 includes/introduction.tex
@@
     Many SMT solvers supporting the theory of strings (e.g., CVC4 \cite{cvc4},  Z3str2 \cite{z3str2}, Norn \cite{norn} and Z3str3 \cite{z3str3}) have been developed over the past decade.
-To validate and benchmark their solvers, many authors have relied on hand-crafted input suites \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests} or real-world examples from industrial applications \cite{kaluza} \cite{kausler}.
-These test suites have helped developers identify implementation defects and develop more sophistic solving heuristics.
+To validate and benchmark their solvers, many authors have relied on hand-crafted input suites~\cite{cvc4-tests,z3str3-tests,z3str2-tests} or real-world examples from industrial applications~\cite{kaluza,kausler}.
+These test suites have helped developers identify implementation defects and develop more sophisticated solving heuristics.
 Although extremely helpful, these suites can only cover a limited range of the problem space because they are either manually created or translated from carefully developed programs.
@@
     Fuzzing, on the other hand, has already been widely used in similar scenarios to systematically generate more diverse test cases.
-Guided by different rules, it can also be applied to generate different instances that are particularly designed to challenge selected capacities.
+Guided by different rules, it can also be applied to generate different instances that are particularly designed to challenge selected parts of the solvers.
 Inspired by traditional fuzzers, we introduce a modular fuzzer for string solvers, \fuzzer{}, and describe its utility as an exploratory validation tool.
@@
 We briefly document its components and modular architecture.
-We provide example usages to demonstrate its usefulness as an exploratory tool for validating solvers.
-We additionally detail its regex-generating and transforming capabilities.
+We provide example use cases to demonstrate its usefulness as an exploratory tool for validating solvers.
+We additionally detail its regex generation and transformation capabilities.
             \item \textbf{A repository of \smtfull{} problems}: We present a repository of \smtfull{} string and regex problem suites we generated using \fuzzer{}.
@@
             \item \textbf{Analysis}: We analyze our experimental results by inspecting the execution traces of the solvers on the given problems.
-For \us{}, we pinpoint algorithmic limitations that cause the poor performance.
+For \us{}, we pinpoint algorithmic limitations that cause poor performance.
 For other solvers, we draw superficial conclusions based solely on the execution traces, and invite their authors to conduct further analysis.

### 2018-01-30 includes/prior.tex
editing first pass

--- 2018-01-22 includes/prior.tex
@@
 
-    Naturally, many solver developers author their own test suites to validate their solvers \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}.
-In addition, several popular problem suites are publicly available for solver validation, such as the Kaluza \cite{kaluza} and Kausler \cite{kausler} suites.
+    Naturally, many solver developers author their own test suites to validate their solvers~\cite{cvc4-tests,z3str3-tests,z3str2-tests}.
+In addition, several popular problem suites are publicly available for solver validation, such as the Kaluza~\cite{kaluza} and Kausler~\cite{kausler} suites.
 
     There are likewise several fuzzers and problem generators currently available, but none of them can generate or transform string and regex problems.
-For example the FuzzSMT\cite{fuzzsmt} tool generates \smt{} problems with bit vectors and arrays, but does not support strings or regexes.
-The SMTpp\cite{smtpp} tool preprocesses and simplifies problems, but does not generate new ones or fuzz existing ones.
+For example, the FuzzSMT~\cite{fuzzsmt} tool generates \smt{} problems with bit-vectors and arrays, but does not support strings or regexes.
+The SMTpp~\cite{smtpp} tool pre-processes and simplifies problems, but does not generate new ones or fuzz existing ones.
 

### 2018-01-30 includes/problems.tex
editing first pass

@@
 
+In this section, we describe the benchmark suites that we generated with \fuzzer{} on which the experimental evaluation was conducted.
+
 \subsection{Generated suite}
 \vspace{-0.1in}
-    We generated several suites of string and regex problems using \fuzzer{}\footnote{For review anonymity, we removed the link to the source code.
-It will be provided separately in the artifact submission.}.
+    We generated several suites of string and regex problems using \fuzzer{}\footnote{For review anonymity, we removed the link to the source code and the generated suites.
+They will be provided separately in the artifact submission.}.
 Table~\ref{tbl:generated} describes the suite \texttt{generated} by \generator{}.
+
+\todo{Specify how many total instances were generated.}
 

### 2018-01-30 includes/stringfuzz.tex
editing first pass

--- 2018-01-29 includes/stringfuzz.tex
@@
 
-    Below are descriptions of the tools that constitute \fuzzer{}:
+    \fuzzer{} is composed of the following tools:
 
 \vspace{-0.15in}
-\subsection{\generator{}}
+\subsubsection{\generator{}:}
 % \vspace{-0.1in}
 
-\generator{} generates \smt{} problems. It supports several generators and options that specify its output. Details can be found in Table~\ref{tbl:generators}.
+This tool generates \smt{} problems. It supports several generators and options that specify its output. Details can be found in Table~\ref{tbl:generators}.
 
@@
 \vspace{-0.15in}
-\subsection{\transformer{}}
+\subsubsection{\transformer{}:}
 % \vspace{-0.1in}
@@
 \vspace{-0.15in}
-\subsection{\texttt{stringstats}}
+\subsubsection{\texttt{stringstats}:}
 
@@
         where $R_i \in RegEx$, and $Min, Max \in Int$.
-More simply, the problem is a set of one or more regex constraints on a single variable, with optional maximum and minimum lengths constraints.
+More simply, the problem is a set of one or more regex constraints on a single variable, with optional maximum and minimum length constraints.
 The regex constraints $R$ are each of the form:
@@
         \endgroup
-        where $j$ a specified depth of recursion.
+        where $j$  is the specified depth of recursion.
 Terms at depth 0 are regex constants.
@@
 Each term is a random nested regex operator (chosen from regex Kleene star, repetition, and union), up to a specified depth, terminating in a regex literal.
-Below is example regex (with spacing added for clarity) of depth 2 produced by this scheme:
+Below are several example regexes (with spacing added for clarity) of depth 2 produced by this scheme:
         \begingroup
@@
 
-        {\it \fuzzer{} can also transform the instances it generates}.
+        \fuzzer{} can also transform the instances it generates.
 All of the transformers in \transformer{} can operate on regex terms.
@@
 
-\section{Example Usages}
+\section{Example Use Cases}
 \vspace{-0.1in}
@@
 It can also be used in a randomised fashion for exploratory debugging.
-As an example, the following usage can feed random problems to \cvc{} until it returns an error:
+As an example, \fuzzer{} can be invoked as follows to feed random problems to \cvc{} until it returns an error:
 \begin{center}
@@
     if [ "$result" == "timeout" ]; then
-        cat hard-problem.smt2
+        cat problem.smt25
         break

### 2018-01-30 includes/introduction.tex
add section labels; remove manual spacing; fix sectioning

@@
         \begin{enumerate}
-            \item \textbf{The \fuzzer{} tool}: We describe a modular fuzzer which can transform and generate \smtfull{} string and regex problems.
+            \item \textbf{The \fuzzer{} tool}: We describe in Section~\ref{sec:fuzzer} a modular fuzzer which can transform and generate \smtfull{} string and regex problems.
 We briefly document its components and modular architecture.
@@
 We additionally detail its regex generation and transformation capabilities.
-            \item \textbf{A repository of \smtfull{} problems}: We present a repository of \smtfull{} string and regex problem suites we generated using \fuzzer{}.
+            \item \textbf{A repository of \smtfull{} problems}: We present a repository of \smtfull{} string and regex problem suites we generated using \fuzzer{} in Section~\ref{sec:problems}.
 We demonstrate the usefulness of these suites by revealing specific defects they helped uncover and fix in \us{}.
-            \item \textbf{Experimental Results}: We compare \theSolvers{} on the \fuzzer{} suites and selectively present the experimental result on \theSuites{}.
+            \item \textbf{Experimental Results}: We compare \theSolvers{} on the \fuzzer{} suites and selectively present the experimental result on \theSuites{} in Section~\ref{sec:data}.
 We highlighted these suites because they uniquely made some solvers perform poorly, but not others.
-            \item \textbf{Analysis}: We analyze our experimental results by inspecting the execution traces of the solvers on the given problems.
+            \item \textbf{Analysis}: We analyze our experimental results in Section~\ref{sec:analysis} by inspecting the execution traces of the solvers on the given problems.
 For \us{}, we pinpoint algorithmic limitations that cause poor performance.

### 2018-01-30 includes/problems.tex
add section labels; remove manual spacing; fix sectioning

@@
 \label{sec:problems}
-\vspace{-0.1in}
 
@@
 \subsection{Generated suite}
-\vspace{-0.1in}
+
     We generated several suites of string and regex problems using \fuzzer{}\footnote{For review anonymity, we removed the link to the source code and the generated suites.
@@
 
-\vspace{-0.2in}
 \subsection{Transformed suite}
-\vspace{-0.1in}
+
     The \texttt{transformed} suite contains benchmarks derived from existing seed problems by iteratively applying \transformer{}.

### 2018-01-30 includes/experiment.tex
add section labels; remove manual spacing; fix sectioning
explain analysis a bit more carefully

@@
 \label{sec:data}
-\vspace{-0.1in}
 
@@
 \section{Usefulness to \us{}: A Case Study}
-\vspace{-0.1in}
+\label{sec:analysis}
 
-        We describe the defects and missing heuristics exposed by \fuzzer{} to illustrate why \fuzzer{} is a valuable asset in solver development.
+        In this section we describe a number of performance-related issues and opportunities for new heuristics
+        which were exposed in \us{} by \fuzzer{} to illustrate the utility and value of the tool in solver development.
 
-\vspace{-0.15in}
 \subsection{Defects discovered and fixed in \us{}}
-\vspace{-0.1in}
 
@@
 
-\vspace{-0.15in}    
 \subsection{Solving heuristics}
-\vspace{-0.1in}
 

### 2018-01-30 includes/introduction.tex
explain analysis a bit more carefully

@@
             \item \textbf{Analysis}: We analyze our experimental results in Section~\ref{sec:analysis} by inspecting the execution traces of the solvers on the given problems.
-For \us{}, we pinpoint algorithmic limitations that cause poor performance.
-For other solvers, we draw superficial conclusions based solely on the execution traces, and invite their authors to conduct further analysis.
+We pinpoint algorithmic limitations in \us{} that cause poor performance, and analyze proposed and implemented enhancements that address the issues which \fuzzer{} helped us to identify.
         \end{enumerate}

### 2018-01-30 includes/abstract.tex
adding comma
editing first pass
cleaned up the paper a lot

--- 2018-01-29 includes/abstract.tex
@@
 \begin{abstract}
-
-    In this paper, we introduce \fuzzer{}: a modular \smt{} problem transformer and generator for string solvers.
-We supply a repository of problems generated by \fuzzer{} in \smtfull{} format.
-We systemically compare \theSolvers{} on groups of such problems focusing on different combinations of string operators, and identify problems that are particularly challenging for some solvers.
-We briefly explain our observations and showcase how \fuzzer{} helped identify causes of the performance degradations in \us{}.
-
+    In this paper, we introduce \fuzzer{}: a modular \smt{} problem
+    transformer and generator for string solvers. We supply a
+    repository of problems generated by \fuzzer{} in \smtfull{}
+    format. We systemically compare \theSolvers{} on groups of such
+    problems focusing on different combinations of string operators,
+    and identify problems that are particularly challenging for some
+    solvers. We briefly explain our observations and showcase how
+    \fuzzer{} helped identify causes of performance degradations in
+    \us{}.
 \end{abstract}

### 2018-01-30 includes/experiment.tex
cleaned up the paper a lot

--- 2018-01-30 includes/experiment.tex
@@
 \label{sec:data}
-\vspace{-0.1in}
 
-    We generated several problem suites with \fuzzer{} that made one solver perform poorly, but not others.
-These suites are \theSuites{}.
-Figure~\ref{fig:cvc-hard} shows the suites that were uniquely difficult for \cvc{}.
-Figure~\ref{fig:z3str3-hard} shows the suites that were uniquely difficult for \us{}.
-All experiments were run in series on the same Linux computer, with a timeout of 15 seconds.
-\todo{Specify CPU, memory}
+We generated several problem suites with \fuzzer{} that made one
+solver perform poorly, but not others. These suites are
+\theSuites{}. Figure~\ref{fig:cvc-hard} shows the suites that were
+uniquely difficult for \cvc{}. Figure~\ref{fig:z3str3-hard} shows the
+suites that were uniquely difficult for \us{}. All experiments were
+run in series on the same Linux computer, with a timeout of 15
+seconds. \todo{Specify CPU, memory}
 
@@
 \section{Usefulness to \us{}: A Case Study}
-\vspace{-0.1in}
+\label{sec:analysis}
 
-        We describe the defects and missing heuristics exposed by \fuzzer{} to illustrate why \fuzzer{} is a valuable asset in solver development.
+We found a number of performance-related issues and opportunities for
+new heuristics in \us{} thanks to \fuzzer{}. For example, the
+instances in the \texttt{concats-big} suite generated by \fuzzer{}
+helped us discover a missing heuristic. In particular, \us{} didn't
+make full use of the solving context (e.g. some terms are empty
+strings) to simplify the concatenations of a long list of string terms
+before trying to reason about the equivalences among subterms. \us{}
+therefore introduced a large number of unnecessary intermediate
+variables and propagations.  As an immediate consequence of the
+testing \us{} on \texttt{concats-big} benchmarks, we were able to
+identify the factors common to these instances and rapidly formulate a
+hypothesis as to why they were performing poorly. This allowed us to
+move forward with the development of new heuristic to resolve this
+issue and achieve better performance.
 
-\vspace{-0.15in}
-\subsection{Defects discovered and fixed in \us{}}
-\vspace{-0.1in}
+%% %VG: this subsection is not needed in the paper    
+%% \noindent{\textbf{Defects discovered and fixed in \us{}:}} The first
+%% issue we found caused \us{} to perform poorly when equivalence classes
+%% of arithmetic terms were very large (e.g. the lengths of many strings
+%% were equal to 0). This issue was detected by the \texttt{Concats}
+%% problem suite. The slowdown was caused by a loop over terms in the
+%% same equivalence class to search for an integer constant. The fix was
+%% to check the root of the equivalence class for the integer constant,
+%% as Z3 makes ``interpreted terms'' (e.g. constants) the root of
+%% equivalence classes whenever possible. The second issue, which was
+%% exposed by the \texttt{Lengths} suite, caused \us{} to perform poorly
+%% when a variable has a large length constraint.  The slowdown was
+%% caused by the solver performing a search for a satisfying length even
+%% when the input formula explicitly constrained the exact length of a
+%% string term.  The fix was to check whether the integer solver had
+%% already assigned a length value before searching for length, and skip
+%% the search if this was the case.
 
-The first issue we found caused \us{} to perform poorly when equivalence classes 
-of arithmetic terms were very large (e.g. the lengths of many strings were equal
-to 0). This issue was detected by the \texttt{Concats} problem suite. The slowdown 
-was caused by a loop over terms in the same equivalence class to search for an 
-integer constant. The fix was to check the root of the equivalence class for the 
-integer constant, as Z3 makes ``interpreted terms'' (e.g. constants) the root of 
-equivalence classes whenever possible. This issue was last observed in commit 
-\texttt{6308636}, and was fixed in commit \texttt{3865c45}.
-
-The second issue, which was exposed by the \texttt{Lengths} suite, caused \us{} to 
-perform poorly when a variable has a large length constraint.
-The slowdown was caused by the solver performing a search for a satisfying length
-even when the input formula explicitly constrained the exact length of a string term.
-The fix was to check whether the integer solver had already assigned a length value
-before searching for length, and skip the search if this was the case.
-This issue was last observed in commit \texttt{66bc68f}, and was fixed in commit 
-\texttt{7b536e9}.    
-%The slowdown was  caused by the solver performing a linear search for a satisfying length when 
-%producing a model for the variable. This issue was an inconsistency between the 
-%implementation and the behavior described in the \us{} paper \cite{z3str3}. 
-%This issue was last observed in commit \texttt{66bc68f}, and was fixed in commit 
-%\texttt{7b536e9}.
-
-\vspace{-0.15in}    
-\subsection{Solving heuristics}
-\vspace{-0.1in}
-
-In order to improve the efficiency of any solver, discovering new heuristics is crucial.
-As an illustrative example, consider detection of conflicting constraints.
-A solver that follows the string constraint solving algorithm and gradually propagates
-the (dis)equalities discovered along the way will eventually detect a conflict.
-However, in many scenarios, a conflict can be discovered ``early'' before trying to
-figure out the relationships among subterms and propagating the facts.
-The benefits of this eager approach are clear: this saves the effort of reasoning about
-subterms and propagating observations, as a conflict will eventually be reached in either case,
-forcing conflict analysis and a backjump.
-As reported in existing works, heuristics of this form usually lead to significant improvements.
-However, the process of discovering such heuristics is extremely challenging,
-as they are usually learned from a class of examples whose commonalities
-are not always obvious or immediately indicative of such inefficiencies.
-
-The instances in the \texttt{concats-big} suite generated by \fuzzer{} helped us 
-discover a missing heuristic in \us{}. In particular, \us{} didn't make full use 
-of the solving context (e.g. some terms are empty strings) to simplify the 
-concatenations of a long list of string terms before trying to reason about the 
-equivalences among subterms. \us{} therefore introduced a large number of unnecessary
-intermediate variables and propagations.
-As an immediate consequence of the \texttt{concats-big} benchmarks, we were able to identify
-the factors common to these instances and rapidly formulate a hypothesis as to why they were
-performing poorly. This allowed us to move forward with the development of new heuristics
-to resolve these issues and achieve better performance.
-
-% In this section, we analyse our experimental results. We discuss the causes of 
-% \us{}'s poor performance on the two problem suites: \textit{concats-balanced} 
-% and \textit{concats-big}. We were not equipped well enough to debug the 
-% behaviours of the other solvers, but we provide our data in hopes that they will 
-% be useful to the solvers' authors.
-
-%     \subsection{\us{} on concats-balanced}
-%         \todo{Dmitry with help: Explain why \us{} performs poorly on this suite.}
-
-% X = "solution"
-% X = (((A.B).(C.D)).((E.F).(G.H))).
-%     (((I.J).(K.L)).((M.N).(O.P)))
-
-    % \subsection{\us{} on concats-big}
-
-    %     \todo{Dmitry with help: Explain why \us{} performs poorly on this suite.}
-
-% X = "solution"
-% X = (A.(B.(C.(D.(E.(F.(G.H)))))))
+%% In order to improve the efficiency of any solver, discovering new
+%% heuristics is crucial.  As an illustrative example, consider the
+%% problem of how the a string solver may detect conflicting
+%% constraints. A string solver that gradually propagates
+%% (dis)equalities discovered along the way will eventually detect a
+%% conflict.  However, in many scenarios, a conflict can be discovered
+%% ``early'' before trying to figure out the relationships among
+%% subterms and propagating the facts.  The benefits of this eager
+%% approach are clear: this saves the effort of reasoning about
+%% subterms and propagating observations, as a conflict will
+%% eventually be reached in either case, forcing conflict analysis and
+%% a backjump.  As reported in existing works, heuristics of this form
+%% usually lead to significant improvements.  However, the process of
+%% discovering such heuristics is extremely challenging, as they are
+%% usually learned from a class of examples whose commonalities are
+%% not always obvious or immediately indicative of such
+%% inefficiencies.

### 2018-01-30 includes/introduction.tex
cleaned up the paper a lot

@@
 
-    Many SMT solvers supporting the theory of strings (e.g., CVC4 \cite{cvc4},  Z3str2 \cite{z3str2}, Norn \cite{norn} and Z3str3 \cite{z3str3}) have been developed over the past decade.
-To validate and benchmark their solvers, many authors have relied on hand-crafted input suites~\cite{cvc4-tests,z3str3-tests,z3str2-tests} or real-world examples from industrial applications~\cite{kaluza,kausler}.
-These test suites have helped developers identify implementation defects and develop more sophisticated solving heuristics.
-Although extremely helpful, these suites can only cover a limited range of the problem space because they are either manually created or translated from carefully developed programs.
+In recent years many algorithms for solving string constraints have
+been developed and implemented as part of SMT solvers such as CVC4
+\cite{cvc4} and Z3 (e.g., Z3str2 \cite{z3str2} and Z3str3
+\cite{z3str3}). To validate and benchmark these solvers, their
+developers have relied on hand-crafted input
+suites~\cite{cvc4-tests,z3str3-tests,z3str2-tests} or real-world
+examples from a limited class of industrial
+applications~\cite{kaluza,kausler}. These test suites have helped
+developers identify implementation defects and develop more
+sophisticated solving heuristics. Although extremely helpful, these
+suites are of limited value since they do not test the vast majority
+of interesting behaviors in solvers. There is an acute need for more
+robst, inexpensive, and automatic way of generating test suites to
+test SMT solvers, that can augment hand-crafted as well as application
+tests.
 
-    Fuzzing, on the other hand, has already been widely used in similar scenarios to systematically generate more diverse test cases.
-Guided by different rules, it can also be applied to generate different instances that are particularly designed to challenge selected parts of the solvers.
-Inspired by traditional fuzzers, we introduce a modular fuzzer for string solvers, \fuzzer{}, and describe its utility as an exploratory validation tool.
-We demonstrate its effectiveness by presenting defects and limitations we were able to identify in leading solvers.
-%     Moreover, a standard input language for problem instances, \smtfull{}\cite{smt}, has been developed and widely adopted.
+Random and mutation fuzzing are widely used test all kinds of software
+including SAT solvers~\cite{}. Inspired by their utility, we introduce
+a fuzzer for string solvers, \fuzzer{}, and describe its value as an
+exploratory validation tool. We demonstrate the efficacy \fuzzer{} by
+presenting defects and limitations it enabled us to identify in
+leading string solvers, which otherwise would have been difficult to
+detect. To the best of our knowledge, \fuzzer{} is the first such tool
+aimed at automatic generation of string constraints. \fuzzer{} allows
+to test string solvers by enabling us to mutate existing classes of
+benchmarks in interesting ways, as well as generate extremal inputs
+(e.g., inputs with very long strings or deep concatenations or
+highly-complex mix of string operations and regular
+expressions). Extremal inputs are particularly useful in empirically
+understanding asymptotic behavior of solvers in a way that no other
+class of instances can.
 
-    \subsection{Contributions}
+\noindent{\textbf{Contributions:}}
 
 \begin{enumerate}
-            \item \textbf{The \fuzzer{} tool}: We describe in Section~\ref{sec:fuzzer} a modular fuzzer which can transform and generate \smtfull{} string and regex problems.
-We briefly document its components and modular architecture.
-We provide example use cases to demonstrate its usefulness as an exploratory tool for validating solvers.
-We additionally detail its regex generation and transformation capabilities.
-            \item \textbf{A repository of \smtfull{} problems}: We present a repository of \smtfull{} string and regex problem suites we generated using \fuzzer{} in Section~\ref{sec:problems}.
-We demonstrate the usefulness of these suites by revealing specific defects they helped uncover and fix in \us{}.
-            \item \textbf{Experimental Results}: We compare \theSolvers{} on the \fuzzer{} suites and selectively present the experimental result on \theSuites{} in Section~\ref{sec:data}.
-We highlighted these suites because they uniquely made some solvers perform poorly, but not others.
-            \item \textbf{Analysis}: We analyze our experimental results in Section~\ref{sec:analysis} by inspecting the execution traces of the solvers on the given problems.
-We pinpoint algorithmic limitations in \us{} that cause poor performance, and analyze proposed and implemented enhancements that address the issues which \fuzzer{} helped us to identify.
+\item \textbf{The \fuzzer{} tool}: We describe in
+  Section~\ref{sec:fuzzer} a modular fuzzer which can transform and
+  randomly generate extremal \smtfull{} string and regex problems. We
+  briefly document its components and modular architecture. We provide
+  example use cases to demonstrate its utility as an exploratory tool
+  for validating solvers.
+
+\item \textbf{A repository of \smtfull{} problems}: We present a
+  repository of \smtfull{} string and regex problem suites we
+  generated using \fuzzer{} in Section~\ref{sec:problems}. We
+  demonstrate the usefulness of these suites by revealing specific
+  defects they helped uncover and fix in \us{}.
+
+\item \textbf{Experimental Results}: We compare \theSolvers{} on the
+  \fuzzer{} suites and selectively present the experimental result on
+  \theSuites{} in Section~\ref{sec:data}. We highlighted these suites
+  because they uniquely made some solvers perform poorly, but not
+  others.
+
+\item \textbf{Analysis}: We analyze our experimental results in
+  Section~\ref{sec:analysis} by inspecting the execution traces of the
+  solvers on the given problems. We pinpoint algorithmic limitations
+  in \us{} that cause poor performance, and analyze proposed and
+  implemented enhancements that address the issues which \fuzzer{}
+  helped us to identify.
 \end{enumerate}

### 2018-01-30 includes/problems.tex
cleaned up the paper a lot

@@
 \label{sec:problems}
+In this section, we describe the benchmark suites that we generated
+with \fuzzer{} on which the experimental evaluation was conducted.
 
-In this section, we describe the benchmark suites that we generated with \fuzzer{} on which the experimental evaluation was conducted.
-
-\subsection{Generated suite}
-
-    We generated several suites of string and regex problems using \fuzzer{}\footnote{For review anonymity, we removed the link to the source code and the generated suites.
-They will be provided separately in the artifact submission.}.
-Table~\ref{tbl:generated} describes the suite \texttt{generated} by \generator{}.
+\noindent{\textbf{Generated Benchmarks:}} We generated several suites
+of string and regex problems using \fuzzer{}\footnote{For review
+  anonymity, we removed the link to the source code and the generated
+  suites. They will be provided separately in the artifact
+  submission.}. Table~\ref{tbl:generated} describes the suite
+\texttt{generated} by \generator{}.
 
@@
 
-\subsection{Transformed suite}
-
-    The \texttt{transformed} suite contains benchmarks derived from existing seed problems by iteratively applying \transformer{}.
-Table~\ref{tbl:transformed} shows the overview.
-Every problem in the suite is named according to its seed and the transformations it undertook.
-For example, input \texttt{seed-fuzz-graft.smt2} was transformed by applying \texttt{fuzz} and then \texttt{graft} from \texttt{seed.smt2}.
+\noindent{\textbf{Transformed Benchmarks:}} The \texttt{transformed}
+suite contains benchmarks derived from existing seed problems by
+iteratively applying \transformer{}. Table~\ref{tbl:transformed} shows
+the overview. Every problem in the suite is named according to its
+seed and the transformations it undertook. For example, input
+\texttt{seed-fuzz-graft.smt2} was transformed by applying
+\texttt{fuzz} and then \texttt{graft} from \texttt{seed.smt2}.
 
@@
 
-    The Amazon category is obtained from two seeds: (1) \texttt{z3-regex-1.smt2} encodes the assertions \texttt{(S not in aaabbb*)} and \texttt{(S in aaa*bbb*)} for a string constant S; (2) \texttt{z3-regex-2-negative.smt2} includes regex \texttt{(S in aaabbb*)} and \texttt{(S not in aaa*bbb*)}.
-    Both problems come from our industrial collaborators. In total, 516 unique problems were generated from these two seeds.
-
-    The Regex category is seeded by the z3str2 regular expression test suite \cite{z3str2-tests}.
-    This test suite contains 42 problems dealing with a wide variety of regular expressions.
-    Through cumulative transformations, we have $10,577$ unique benchmarks.
+The Amazon category is obtained from two seeds: (1)
+\texttt{z3-regex-1.smt2} encodes the assertions \texttt{(S not in
+  aaabbb*)} and \texttt{(S in aaa*bbb*)} for a string constant S; (2)
+\texttt{z3-regex-2-negative.smt2} includes regex \texttt{(S in
+  aaabbb*)} and \texttt{(S not in aaa*bbb*)}.  Both problems come from
+our industrial collaborators. In total, 516 unique problems were
+generated from these two seeds. The Regex category is seeded by the
+z3str2 regular expression test suite \cite{z3str2-tests}.  This test
+suite contains 42 problems dealing with a wide variety of regular
+expressions.  Through cumulative transformations, we have $10,577$
+unique benchmarks.

### 2018-01-30 includes/stringfuzz.tex
add section labels; remove manual spacing; fix sectioning
cleaned up the paper a lot

@@
 \label{sec:fuzzer}
-\vspace{-0.1in}
+\fuzzer{} is implemented as a Python package, and comes with several
+executables to generate, transform, and analyze \smtfull{} string
+problems. It can either be installed from source, or from the Python
+PIP package repository. \fuzzer{} is organized to be easily extended:
+all generators and transformers are independent Python modules. Its
+components are also implemented as \unix{} ``filters'', to enable easy
+integration with other tools (including themselves). For example, the
+outputs of generators can be piped into transformers, and transformers
+can be chained to produce a stream of tuned inputs to a
+solver.
 
-%     This section describes the fuzzer \fuzzer{}, which generates new \smtfull{} problems and transforms existing ones. 
-    \fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyze \smtfull{} string problems.
-It can either be installed from source, or from the Python PIP package repository.
+\noindent{Specifically, \fuzzer{} is composed of the following tools:}
 
-%     {\it For review anonymity, we removed the link to the source code. It will be provided separately in the artifact submission.}
-
-    \fuzzer{} is organized to be easily extended: all generators and transformers are independent Python modules.
-Its components are also implemented as \unix{} ``filters'', to enable easy integration with other tools (including themselves).
-For example, the outputs of generators can be piped into transformers, and transformers can be chained to produce a stream of tuned inputs to a solver.
-
-    \fuzzer{} is composed of the following tools:
-
-\vspace{-0.15in}
-\subsubsection{\generator{}:}
-% \vspace{-0.1in}
-
-This tool generates \smt{} problems. It supports several generators and options that specify its output. Details can be found in Table~\ref{tbl:generators}.
+\noindent{\textbf{\generator{}:}} This tool generates \smt{}
+problems. It supports several generators and options that specify its
+output. Details can be found in Table~\ref{tbl:generators}.
 
 \begin{table}[t]
-\vspace{-0.25in}
+%\vspace{-0.25in}
 \centering
@@
   \egroup
-\vspace{-0.2in}
+%\vspace{-0.2in}
 }
@@
 
-\vspace{-0.15in}
-\subsubsection{\transformer{}:}
-% \vspace{-0.1in}
-
-This tool transforms \smt{} problems.
-It supports several transformers and options that specify its output and input, which are explained in Table~\ref{tbl:transformers}.
-Note that transformers \textit{translate} and \textit{reverse} also preserve problem satisfiability \cite{ifaz}.
+\noindent{\textbf{\transformer{}:}This tool transforms \smt{}
+  problems. It supports several transformers and options that specify
+  its output and input, which are explained in
+  Table~\ref{tbl:transformers}. Note that transformers
+  \textit{translate} and \textit{reverse} also preserve problem
+  satisfiability \cite{ifaz}.
 
 \begin{table}[t]
-\vspace{-0.25in}
+%\vspace{-0.25in}
 \centering
@@
   \egroup
-  \vspace{-0.2in}
+  %\vspace{-0.2in}
 }
@@
 
-\vspace{-0.15in}
-\subsubsection{\texttt{stringstats}:}
+\noindent{\textbf{\texttt{stringstats}:}} This tool takes an \smt{}
+problem as input and outputs its properties: the number of
+variables/literals, the max/median syntactic depth of expressions, the
+max/median literal length, etc.
 
-This tool takes an \smt{} problem as input and outputs its properties: the number of variables/literals, the max/median syntactic depth of expressions, the max/median literal length, etc.
+\noindent{\textbf{Regex Fuzzing Capabilities:}} \fuzzer{} can generate
+and transform problems with regular expression constraints. The
+command \texttt{stringfuzzg regex} invokes the regex problem
+generator. It generates a problem of the form:
+
+\begingroup
+\footnotesize
+\begin{align*}
+  & \texttt{(assert (str.in.re X}\; R_0\; \texttt{))} \\
+  & \texttt{(assert (str.in.re X}\; R_n\; \texttt{))}* \\
+  & \texttt{(assert (<= Min (str.len X)))}? \\
+  & \texttt{(assert (<= (str.len X)) Max)}?
+\end{align*}
+\endgroup
+
+where $R_i \in RegEx$, and $Min, Max \in Int$. More simply, the
+problem is a set of one or more regex constraints on a single
+variable, with optional maximum and minimum length constraints. The
+regex constraints $R$ are each of the form:
+
+\begingroup
+\footnotesize
+\begin{align*}
+  & \texttt{(re.++}\; \ T_0\; \ T_1\; \texttt{...}\; T_n\; \texttt{)}
+\end{align*}
+\endgroup
+and each $T_i$ is a recursive term of the form:
+\begingroup
+\footnotesize
+\begin{align*}
+  & \texttt{(re.*}\; T_{i_j}\; \texttt{) | (re.+}\; T_{i_j}\;
+  \texttt{) | (re.union}\; T_{i_{j_1}}\; T_{i_{j_2}}\; \texttt{)}
+\end{align*}
+\endgroup
+
+where $j$ is the specified depth of recursion. Terms at depth 0 are
+regex constants. Informally, this form describes a concatenation of
+regex terms. Each term is a random nested regex operator (chosen from
+regex Kleene star, repetition, and union), up to a specified depth,
+terminating in a regex literal. Below are several example regexes
+(with spacing added for clarity) of depth 2 produced by this scheme:
+
+\begingroup
+\footnotesize
+\begin{align*}
+  & ((\texttt{a}|\texttt{b})|(\texttt{cc})+)\quad
+  ((\texttt{ddd})*)+\quad ((\texttt{ee})+|(\texttt{fff})*)
+\end{align*}
+\endgroup
+
+\fuzzer{} can also transform the instances it generates. All of the
+transformers in \transformer{} can operate on regex terms. They can
+multiply and permute regex literals (e.g. \texttt{reverse},
+\texttt{multiply}, \texttt{translate}), randomly replace regex
+operators (e.g. \texttt{fuzz}), and manipulate the syntax tree
+(e.g. \texttt{graft}, \texttt{rotate}).
+
+\noindent{\textbf{Example Use Cases:}} \fuzzer{} can be used to
+generate benchmark suites in a batch mode, or can be used in an online
+randomized fashion for exploratory debugging. For example, \fuzzer{}
+can be invoked as follows to feed random problems to \cvc{} until it
+returns an error:
+
+\begin{center}
+%\vspace{-0.05in}
+\begin{varwidth}{\linewidth}
+{\scriptsize\begin{verbatim}while stringfuzzg -r random | tee
+  problem.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do sleep 0 done
+\end{verbatim}}
+\end{varwidth}
+\end{center}
+
+Some \unix{} scripting can yield other interesting results. For
+example, the following script finds a regex problem on which \us{}
+times out after 5 seconds:
+
+\begin{center}
+%\vspace{-0.1in}
+\begin{varwidth}{\linewidth}
+        {\scriptsize\begin{verbatim}while true; do
+    stringfuzzg -r regex -c -a increasing -r 2 -t 5 -d 3 > problem.smt25
+    result=`z3str3 -T:5 problem.smt25`
+    echo $result
+    if [ "$result" == "timeout" ]; then
+        cat problem.smt25
+        break
+    fi
+done\end{verbatim}}
+\end{varwidth}
+\end{center}
 
 % \texttt{stringstats} is handy when analyzing a problem.    
-
 %     \begin{description}
@@
 %     \end{description}
-
-    \section{Regex Fuzzing Capabilities}
-    \vspace{-0.1in}
-        \fuzzer{} can generate and transform problems with regular expression constraints.
-The command \texttt{stringfuzzg regex} invokes the regex problem generator.
-It generates a problem of the form: %\footnote{Variable declarations omitted for brevity.}:
-        \begingroup
-        \footnotesize
-        \begin{align*}
-            & \texttt{(assert (str.in.re X}\; R_0\; \texttt{))} \\
-            & \texttt{(assert (str.in.re X}\; R_n\; \texttt{))}* \\
-            & \texttt{(assert (<= Min (str.len X)))}? \\
-            & \texttt{(assert (<= (str.len X)) Max)}?
-        \end{align*}
-        \endgroup
-        where $R_i \in RegEx$, and $Min, Max \in Int$.
-More simply, the problem is a set of one or more regex constraints on a single variable, with optional maximum and minimum length constraints.
-The regex constraints $R$ are each of the form:
-        \begingroup
-        \footnotesize
-        \begin{align*}
-            & \texttt{(re.++}\; \ T_0\; \  T_1\; \texttt{...}\; T_n\; \texttt{)}
-        \end{align*}
-        \endgroup
-        and each $T_i$ is a recursive term of the form:
-        \begingroup
-        \footnotesize
-        \begin{align*}
-            & \texttt{(re.*}\; T_{i_j}\; \texttt{) | (re.+}\; T_{i_j}\; \texttt{) | (re.union}\; T_{i_{j_1}}\; T_{i_{j_2}}\; \texttt{)}
-        \end{align*}
-        \endgroup
-        where $j$  is the specified depth of recursion.
-Terms at depth 0 are regex constants.
-Informally, this form describes a concatenation of regex terms.
-Each term is a random nested regex operator (chosen from regex Kleene star, repetition, and union), up to a specified depth, terminating in a regex literal.
-Below are several example regexes (with spacing added for clarity) of depth 2 produced by this scheme:
-        \begingroup
-        \footnotesize
-        \begin{align*}
-            & ((\texttt{a}|\texttt{b})|(\texttt{cc})+)\quad ((\texttt{ddd})*)+\quad ((\texttt{ee})+|(\texttt{fff})*)
-        \end{align*}
-        \endgroup
-
-        \fuzzer{} can also transform the instances it generates.
-All of the transformers in \transformer{} can operate on regex terms.
-They can multiply and permute regex literals (e.g.
-\texttt{reverse}, \texttt{multiply}, \texttt{translate}), randomly replace regex operators (e.g.
-\texttt{fuzz}), and manipulate the syntax tree (e.g.
-\texttt{graft}, \texttt{rotate}).
-
-\section{Example Use Cases}
-\vspace{-0.1in}
-
-        \fuzzer{} can be used to generate problems to be saved as static suites.
-It can also be used in a randomised fashion for exploratory debugging.
-As an example, \fuzzer{} can be invoked as follows to feed random problems to \cvc{} until it returns an error:
-\begin{center}
-\vspace{-0.05in}
-\begin{varwidth}{\linewidth}
-{\scriptsize\begin{verbatim}while stringfuzzg -r random | tee problem.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do
-    sleep 0
-done
-\end{verbatim}}
-\end{varwidth}
-\end{center}
-        Some \unix{} scripting can yield other interesting results. For example, the following script finds a regex problem on which \us{} times out after 5 seconds:
-\begin{center}
-\vspace{-0.1in}
-\begin{varwidth}{\linewidth}
-        {\scriptsize\begin{verbatim}while true; do
-    stringfuzzg -r regex -c -a increasing -r 2 -t 5 -d 3 > problem.smt25
-    result=`z3str3 -T:5 problem.smt25`
-    echo $result
-    if [ "$result" == "timeout" ]; then
-        cat problem.smt25
-        break
-    fi
-done\end{verbatim}}
-\end{varwidth}
-\end{center}

### 2018-01-30 includes/introduction.tex
further clean up of the entire paper

@@
 of interesting behaviors in solvers. There is an acute need for more
-robst, inexpensive, and automatic way of generating test suites to
-test SMT solvers, that can augment hand-crafted as well as application
-tests.
+robst, inexpensive, and automatic way of generating benchmarks to test
+the correctness and performance of SMT solvers, that can augment
+hand-crafted as well as tests generated from industrial applications.
 
+%VG: add citation to SAT fuzzer
 Random and mutation fuzzing are widely used test all kinds of software
-including SAT solvers~\cite{}. Inspired by their utility, we introduce
-a fuzzer for string solvers, \fuzzer{}, and describe its value as an
-exploratory validation tool. We demonstrate the efficacy \fuzzer{} by
-presenting defects and limitations it enabled us to identify in
+including SAT solvers. Inspired by their utility, we introduce a
+fuzzer for string solvers, \fuzzer{}, and describe its value as an
+exploratory validation tool. We demonstrate the efficacy of \fuzzer{}
+by presenting defects and limitations it enabled us to identify in
 leading string solvers, which otherwise would have been difficult to
 detect. To the best of our knowledge, \fuzzer{} is the first such tool
-aimed at automatic generation of string constraints. \fuzzer{} allows
-to test string solvers by enabling us to mutate existing classes of
-benchmarks in interesting ways, as well as generate extremal inputs
-(e.g., inputs with very long strings or deep concatenations or
-highly-complex mix of string operations and regular
-expressions). Extremal inputs are particularly useful in empirically
-understanding asymptotic behavior of solvers in a way that no other
-class of instances can.
+aimed at automatic generation of string constraints. \fuzzer{} can be
+used to mutate or transform existing benchmarks, as well
+randomly-generate structured instances that can be scaled with respect
+to a variety of parameters, e.g., length of string constants, depth of
+concats, balanced or unbalanced concats, overlapping word equations,
+systems of word equations with arithmetic over length, nested regular
+expressions, rich combination of regular expressions and string
+constraints, and many more.
 
@@
   Section~\ref{sec:fuzzer} a modular fuzzer which can transform and
-  randomly generate extremal \smtfull{} string and regex problems. We
-  briefly document its components and modular architecture. We provide
-  example use cases to demonstrate its utility as an exploratory tool
-  for validating solvers.
+  randomly generate extremal \smtfull{} string and regular expression
+  (regex) problems~\footnote{We assume basic
+    familiarity with string solvers and their input
+    language.}. Extremal or scaling inputs (e.g., long string
+  constants, deep concatenations) are particularly useful in
+  identifying asymptotic behaviors in solvers. We briefly document its
+  components and modular architecture. We provide example use cases to
+  demonstrate its utility as an exploratory tool for validating
+  solvers.
 

### 2018-01-30 includes/introduction.tex
Trimming trailing whitespace. Fixing grammar.

@@
 suites are of limited value since they do not test the vast majority
-of interesting behaviors in solvers. There is an acute need for more
-robst, inexpensive, and automatic way of generating benchmarks to test
+of interesting behaviors in solvers. There is an acute need for a more
+robust, inexpensive, and automatic way of generating benchmarks to test
 the correctness and performance of SMT solvers, that can augment
@@
 %VG: add citation to SAT fuzzer
-Random and mutation fuzzing are widely used test all kinds of software
+Random and mutation fuzzing are widely used to test all kinds of software
 including SAT solvers. Inspired by their utility, we introduce a
@@
 aimed at automatic generation of string constraints. \fuzzer{} can be
-used to mutate or transform existing benchmarks, as well
-randomly-generate structured instances that can be scaled with respect
-to a variety of parameters, e.g., length of string constants, depth of
-concats, balanced or unbalanced concats, overlapping word equations,
+used to mutate or transform existing benchmarks, as well as
+randomly generate structured instances that can be scaled with respect
+to a variety of parameters. Examples include: length of string constants,
+depth of concats, balanced or unbalanced concats, overlapping word equations,
 systems of word equations with arithmetic over length, nested regular
-expressions, rich combination of regular expressions and string
+expressions, rich combinations of regular expressions and string
 constraints, and many more.
@@
   constants, deep concatenations) are particularly useful in
-  identifying asymptotic behaviors in solvers. We briefly document its
+  identifying asymptotic behaviors in solvers. We briefly document \fuzzer{}'s
   components and modular architecture. We provide example use cases to
@@
   \fuzzer{} suites and selectively present the experimental result on
-  \theSuites{} in Section~\ref{sec:data}. We highlighted these suites
-  because they uniquely made some solvers perform poorly, but not
-  others.
+  the suites \theSuites{} in Section~\ref{sec:data}. We highlighted
+  these suites because they uniquely made some solvers perform poorly,
+  but not others.
 

### 2018-01-31 includes/problems.tex
further clean up of the entire paper
More typos and trailing whitespace.
First pass with Federico.

@@
 \label{sec:problems}
+
 In this section, we describe the benchmark suites that we generated
@@
 
-\noindent{\textbf{Generated Benchmarks:}} We generated several suites
+\subsubsection{Generated Benchmarks}
+
+We generated several suites
 of string and regex problems using \fuzzer{}\footnote{For review
@@
 \texttt{generated} by \generator{}.
-
-\todo{Specify how many total instances were generated.}
-
-\begin{table}[h]
-\vspace{-0.4in}
+\begin{table}[H]
     \centering
@@
     \label{tbl:generated}
-{
-  \footnotesize
-  \bgroup
-  \def\arraystretch{1}
-  \resizebox{0.8\columnwidth}{!}{
     \begin{tabular}{|l|l|}
@@
     \end{tabular}
-  }
-  \egroup
-  \vspace{-0.2in}
-}
 \end{table}
 
-%     \begin{table}
-%         \centering
-%         \begin{tabular}{|l|l|}
-%             \hline
-%             \textbf{Name}             & \textbf{Problems have ...} \\ \hline
-%             \textit{Concats}          & A single, deep tree of concats. \\ \hline
-%             \textit{Concats-Extracts} & A single concat tree, and random character extractions. \\ \hline
-%             \textit{Lengths}          & A single, large length constraint on a variable. \\ \hline
-%             \textit{Lengths-Concats}  & Variables and their concats, each with fixed lengths. \\ \hline
-%             \textit{Overlaps}         & A formula of the form A.X = X.B. \\ \hline
-%             \textit{Regex}            & A test for regex membership of arbitrary complexity. \\ \hline
-%             \textit{Many-Regexes}     & A test for membership in many random regexes. \\ \hline
-%             \textit{Regex-Deep}       & A test for membership in a regex with many nested operators. \\ \hline
-%             \textit{Regex-Pair}       & A test for membership in one regex, but not another. \\ \hline
-%             \textit{Regex-Lengths}    & A test for membership in a regex, and a length constraint. \\ \hline
-%         \end{tabular}
-%         \caption{\generator{}-generated problem sets.}
-%         \label{tbl:generated}
-%     \end{table}
+\subsubsection{Transformed Benchmarks}
 
-\noindent{\textbf{Transformed Benchmarks:}} The \texttt{transformed}
+The \texttt{transformed}
 suite contains benchmarks derived from existing seed problems by
@@
 \texttt{fuzz} and then \texttt{graft} from \texttt{seed.smt2}.
-
-\begin{table}[h]
-\vspace{-0.35in}
+\begin{table}[H]
     \centering
@@
     \label{tbl:transformed}
-{
-  \footnotesize
-  \bgroup
-  \def\arraystretch{1}
-  \resizebox{0.6\columnwidth}{!}{
     \begin{tabular}{|l|l|r|}
@@
     \end{tabular}
-    }
-  \egroup
-  \vspace{-0.2in}
-}
 \end{table}
-
-%     \begin{table}
-%         \centering
-%         \begin{tabular}{|l|l|r|}
-%             \hline
-%             \textbf{Name}   & \textbf{Seed}                            & \textbf{Quantity} \\ \hline
-%             \textit{Amazon} & Two industrial regex membership problems & 516\\ \hline
-%             \textit{Regex}  & Z3str2 regular expression test suite     & 10,577\\ \hline
-%         \end{tabular}
-%         \caption{\transformer{}-generated problem sets.}
-%         \label{tbl:transformed}
-%     \end{table}
 

### 2018-01-31 includes/stringfuzz.tex
further clean up of the entire paper
Trimming trailing whitespace. Fixing grammar.
First pass with Federico.

@@
 \label{sec:fuzzer}
+
 \fuzzer{} is implemented as a Python package, and comes with several
@@
 can be chained to produce a stream of tuned inputs to a
-solver.
+solver. Specifically, \fuzzer{} is composed of the following tools:
+\begin{description}
+    \item[\generator{}] \hfill \\
+        This tool generates \smt{} problems. It supports several generators and
+        options that specify its output. Details can be found in
+        Table~\ref{tbl:generators}.
+    \item[\transformer{}] \hfill \\
+        This tool transforms \smt{}
+        problems. It supports several transformers and options that specify
+        its output and input, which are explained in
+        Table~\ref{tbl:transformers}. Note that transformers
+        \textit{translate} and \textit{reverse} also preserve problem
+        satisfiability \cite{ifaz}.
+    \item[\texttt{stringstats}] \hfill \\
+        This tool takes an \smt{}
+        problem as input and outputs its properties: the number of
+        variables/literals, the max/median syntactic depth of expressions, the
+        max/median literal length, etc.
+\end{description}
 
-\noindent{Specifically, \fuzzer{} is composed of the following tools:}
-
-\noindent{\textbf{\generator{}:}} This tool generates \smt{}
-problems. It supports several generators and options that specify its
-output. Details can be found in Table~\ref{tbl:generators}.
-
-\begin{table}[t]
-%\vspace{-0.25in}
-\centering
+\begin{table}[H]
     \caption{\generator{} generators.}
     \label{tbl:generators}
-{
-  \footnotesize
-  \bgroup
-  \def\arraystretch{1}
-  \resizebox{0.8\columnwidth}{!}{
     \begin{tabular}{|l|l|}
@@
     \end{tabular}
-  }
-  \egroup
-%\vspace{-0.2in}
-}
 \end{table}
 
-\noindent{\textbf{\transformer{}:}This tool transforms \smt{}
-  problems. It supports several transformers and options that specify
-  its output and input, which are explained in
-  Table~\ref{tbl:transformers}. Note that transformers
-  \textit{translate} and \textit{reverse} also preserve problem
-  satisfiability \cite{ifaz}.
-
-\begin{table}[t]
-%\vspace{-0.25in}
-\centering
-\caption{\transformer{} transformers}
+\begin{table}[H]
+    \caption{\transformer{} transformers.}
     \label{tbl:transformers}
-{
-  \footnotesize
-  \bgroup
-  \def\arraystretch{1}
-  \resizebox{0.8\columnwidth}{!}{
     \begin{tabular}{|l|l|}
@@
     \end{tabular}
-  }
-  \egroup
-  %\vspace{-0.2in}
-}
 \end{table}
 
-\noindent{\textbf{\texttt{stringstats}:}} This tool takes an \smt{}
-problem as input and outputs its properties: the number of
-variables/literals, the max/median syntactic depth of expressions, the
-max/median literal length, etc.
+\subsubsection{Regex Fuzzing Capabilities}
 
-\noindent{\textbf{Regex Fuzzing Capabilities:}} \fuzzer{} can generate
+\fuzzer{} can generate
 and transform problems with regular expression constraints. The
@@
 generator. It generates a problem of the form:
-
-\begingroup
-\footnotesize
 \begin{align*}
@@
 \end{align*}
-\endgroup
 
@@
 regex constraints $R$ are each of the form:
-
-\begingroup
-\footnotesize
 \begin{align*}
@@
 \end{align*}
-\endgroup
+
 and each $T_i$ is a recursive term of the form:
-\begingroup
-\footnotesize
 \begin{align*}
@@
 (with spacing added for clarity) of depth 2 produced by this scheme:
-
-\begingroup
-\footnotesize
 \begin{align*}
@@
 
-\noindent{\textbf{Example Use Cases:}} \fuzzer{} can be used to
+\subsubsection{Example Use Cases}
+
+\fuzzer{} can be used to
 generate benchmark suites in a batch mode, or can be used in an online
@@
 returns an error:
+\vspace{-0.15in}
+\begin{figure}[H]
+    \centering
+    \begin{minipage}[b]{0.91\linewidth}
+        \begin{minted}{bash}
+while \
+  stringfuzzg -r random-ast -m \
+  | tee problem.smt25 \
+  | cvc4 --lang smt2.5 --tlimit=5000; do
+    sleep 0
+done
+        \end{minted}
+    \end{minipage}
+\end{figure}
+\vspace{-0.15in}
 
-\begin{center}
-%\vspace{-0.05in}
-\begin{varwidth}{\linewidth}
-{\scriptsize\begin{verbatim}while stringfuzzg -r random | tee
-  problem.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do sleep 0 done
-\end{verbatim}}
-\end{varwidth}
-\end{center}
-
-Some \unix{} scripting can yield other interesting results. For
+Some more \unix{} scripting can yield other interesting results. For
 example, the following script finds a regex problem on which \us{}
 times out after 5 seconds:
-
-\begin{center}
-%\vspace{-0.1in}
-\begin{varwidth}{\linewidth}
-        {\scriptsize\begin{verbatim}while true; do
+\vspace{-0.15in}
+\begin{figure}[H]
+    \centering
+    \begin{minipage}[b]{0.91\linewidth}
+        \begin{minted}{bash}
+while true; do
     stringfuzzg -r regex -c -a increasing -r 2 -t 5 -d 3 > problem.smt25
@@
     fi
-done\end{verbatim}}
-\end{varwidth}
-\end{center}
-
-% \texttt{stringstats} is handy when analyzing a problem.    
-%     \begin{description}
-
-%         \item[\generator{}] \hfill \\
-%             This tool generates \smt{} problems. It supports several generators and options that specify its output. Table~\ref{tbl:generators} describes them.
-%             \hfill \\
-% 
-%             \begin{table}
-%                 \centering
-%                 \begin{tabular}{|l|l|}
-%                     \hline
-%                     \textbf{Name}        & \textbf{Generated Problems have ...} \\ \hline
-%                     \textit{concats}     & Long concats and optional random extracts. \\ \hline
-%                     \textit{lengths}     & Many variables (and their concats) with length constraints. \\ \hline
-%                     \textit{overlaps}    & An expression of the form A.X = X.B. \\ \hline
-%                     \textit{equality}    & An equality among concats, each with variables or constants. \\ \hline
-%                     \textit{regex}       & Regexes of varying complexity. \\ \hline
-%                     \textit{random-text} & Random, likely syntactically \textit{in}valid text. \\ \hline
-%                     \textit{random-ast}  & Random, but semantically \textit{valid} text. \\ \hline
-%                 \end{tabular}
-%                 \caption{\generator{} generators}
-%                 \label{tbl:generators}
-%             \end{table}
-
-%         \item[\transformer{}] \hfill \\
-%             This tool transforms \smt{} problems.
-It supports several transformers and options that specify its output and input.
-Table~\ref{tbl:transformers} describes them.
-The following transformers also preserve problem satisfiability: \textit{translate}, \textit{reverse}.
-\cite{ifaz}
-%             \hfill \\
-% 
-%             \begin{table}
-%                 \centering
-%                 \begin{tabular}{|l|l|}
-%                     \hline
-%                     \textbf{Name}        & \textbf{The transformer ...} \\ \hline
-%                     \textit{fuzz}        & Randomly replaces literals and operators with similar ones. \\ \hline
-%                     \textit{graft}       & For each sort, swaps a random non-leaf node with a leaf node. \\ \hline
-%                     \textit{multiply}    & Multiplies each number by N, and repeats each character N times. \\ \hline
-%                     \textit{nop}         & Does nothing. \\ \hline
-%                     \textit{reverse}     & Reverses all string literals and concat arguments. \\ \hline
-%                     \textit{rotate}      & Performs a random syntax tree rotation on two concats. \\ \hline
-%                     \textit{translate}   & Maps every character X to a different character Y. \\ \hline
-%                     \textit{unprintable} & Randomly replaces all characters in literals with unprintable ones. \\ \hline
-%                 \end{tabular}
-%                 \caption{\transformer{} transformers}
-%                 \label{tbl:transformers}
-%             \end{table}
-
-%         \item[\texttt{stringstats}] \hfill \\
-%             This tool takes as input an \smt{} problem, and outputs its properties, such as: numbers of string variables and literals, max/median syntactic depth of expressions, and max/median length of literals.
-%             \hfill \\
-
-        % \item[\texttt{stringmerge}] \hfill \\
-        %     This tool takes as input two \smt{} problems and combines them into one problem.
-
-        %     \todo{Federico: describe \texttt{stringmerge}.}
-
-%     \end{description}
+done
+        \end{minted}
+    \end{minipage}
+\end{figure}
+\vspace{-0.15in}

### 2018-01-31 includes/abstract.tex
Fixing abstract.

@@
     repository of problems generated by \fuzzer{} in \smtfull{}
-    format. We systemically compare \theSolvers{} on groups of such
-    problems focusing on different combinations of string operators,
-    and identify problems that are particularly challenging for some
-    solvers. We briefly explain our observations and showcase how
+    format. We systematically compare \theSolvers{} on groups of such
+    problems, and identify problems that are particularly challenging for some
+    solvers. We briefly explain our observations and show how
     \fuzzer{} helped identify causes of performance degradations in

### 2018-01-31 includes/introduction.tex
First pass with Federico.
Fixing up more content.

@@
 In recent years many algorithms for solving string constraints have
-been developed and implemented as part of SMT solvers such as CVC4
-\cite{cvc4} and Z3 (e.g., Z3str2 \cite{z3str2} and Z3str3
-\cite{z3str3}). To validate and benchmark these solvers, their
-developers have relied on hand-crafted input
-suites~\cite{cvc4-tests,z3str3-tests,z3str2-tests} or real-world
-examples from a limited class of industrial
+been developed and implemented in SMT solvers such as Norn~\cite{norn},
+CVC4~\cite{cvc4}, and Z3 (e.g., Z3str2~\cite{z3str2} and Z3str3~\cite{z3str3}).
+To validate and benchmark these solvers, their developers have relied on
+hand-crafted input suites~\cite{cvc4-tests,z3str3-tests,z3str2-tests} or
+real-world examples from a limited class of industrial
 applications~\cite{kaluza,kausler}. These test suites have helped
 developers identify implementation defects and develop more
-sophisticated solving heuristics. Although extremely helpful, these
-suites are of limited value since they do not test the vast majority
-of interesting behaviors in solvers. There is an acute need for a more
-robust, inexpensive, and automatic way of generating benchmarks to test
-the correctness and performance of SMT solvers, that can augment
-hand-crafted as well as tests generated from industrial applications.
+sophisticated solving heuristics. Unfortunately, as solvers grow,
+fixed benchmarks leave more functionality untested.
+There is an acute need for a more robust, inexpensive, and automatic way
+of generating benchmarks to test
+the correctness and performance of SMT solvers.
 
 %VG: add citation to SAT fuzzer
-Random and mutation fuzzing are widely used to test all kinds of software
+Fuzzing is often used to test all kinds of software,
 including SAT solvers. Inspired by their utility, we introduce a
 fuzzer for string solvers, \fuzzer{}, and describe its value as an
-exploratory validation tool. We demonstrate the efficacy of \fuzzer{}
-by presenting defects and limitations it enabled us to identify in
-leading string solvers, which otherwise would have been difficult to
-detect. To the best of our knowledge, \fuzzer{} is the first such tool
-aimed at automatic generation of string constraints. \fuzzer{} can be
+exploratory validation tool. We demonstrate its efficacy
+by presenting limitations it helped us find in
+leading string solvers. To the best of our knowledge, \fuzzer{} is the
+first tool aimed at automatic generation of string constraints. \fuzzer{} can be
 used to mutate or transform existing benchmarks, as well as
-randomly generate structured instances that can be scaled with respect
-to a variety of parameters. Examples include: length of string constants,
-depth of concats, balanced or unbalanced concats, overlapping word equations,
-systems of word equations with arithmetic over length, nested regular
-expressions, rich combinations of regular expressions and string
-constraints, and many more.
+randomly generate structured instances. These instances can be scaled with respect
+to a variety of parameters, e.g., length of string constants,
+depth of concats and regeular expressions, number of variables,
+number of length constraints, and many more.
 
-\noindent{\textbf{Contributions:}}
+\subsubsection{Contributions}
 
 \begin{enumerate}
-\item \textbf{The \fuzzer{} tool}: We describe in
-  Section~\ref{sec:fuzzer} a modular fuzzer which can transform and
+\item \textbf{The \fuzzer{} tool}:
+    In section~\ref{sec:fuzzer}, we describe a modular fuzzer that can transform and
     randomly generate extremal \smtfull{} string and regular expression
@@
 
-\item \textbf{A repository of \smtfull{} problems}: We present a
-  repository of \smtfull{} string and regex problem suites we
-  generated using \fuzzer{} in Section~\ref{sec:problems}. We
-  demonstrate the usefulness of these suites by revealing specific
-  defects they helped uncover and fix in \us{}.
+\item \textbf{A repository of \smtfull{} problems}:
+    We present a repository of \smtfull{} string and regex problem suites we
+    generated using \fuzzer{} in Section~\ref{sec:problems}. The repository
+    consists of two categories: \texttt{generated}, with new problems generated
+    by \fuzzer{}, and \texttt{transformed}, with transformed problems generated
+    from a small suite of industrial benchmarks.
 
-\item \textbf{Experimental Results}: We compare \theSolvers{} on the
-  \fuzzer{} suites and selectively present the experimental result on
-  the suites \theSuites{} in Section~\ref{sec:data}. We highlighted
-  these suites because they uniquely made some solvers perform poorly,
-  but not others.
-
-\item \textbf{Analysis}: We analyze our experimental results in
-  Section~\ref{sec:analysis} by inspecting the execution traces of the
-  solvers on the given problems. We pinpoint algorithmic limitations
-  in \us{} that cause poor performance, and analyze proposed and
-  implemented enhancements that address the issues which \fuzzer{}
-  helped us to identify.
+\item \textbf{Experimental Results and Analysis}:
+    We compare the performance of \theSolvers{} on the
+    the \fuzzer{} suites \theSuites{} in section~\ref{sec:data}. We highlight
+    these suites because they make some solvers perform poorly,
+    but not others. In section~\ref{sec:analysis}, we analyze our
+    experimental results, and pinpoint algorithmic limitations
+    in \us{} that cause poor performance. We propose enhancements that
+    address these issues, which \fuzzer{} helped us find.
 \end{enumerate}

### 2018-01-31 includes/problems.tex
Fixing up more content.

@@
 We generated several suites
-of string and regex problems using \fuzzer{}\footnote{For review
-anonymity, we removed the link to the source code and the generated
-suites. They will be provided separately in the artifact
-submission.}. Table~\ref{tbl:generated} describes the suite
+of string and regex problems using \fuzzer{}\footnote{The link to the
+repository will be added after double-blind review.}.
+Table~\ref{tbl:generated} describes the suite
 \texttt{generated} by \generator{}.

### 2018-01-31 includes/stringfuzz.tex
Fixing up more content.

@@
 \fuzzer{} is implemented as a Python package, and comes with several
-executables to generate, transform, and analyze \smtfull{} string
+executables to generate, transform, and analyze \smtfull{} string and regex
 problems. It can either be installed from source, or from the Python
-PIP package repository. \fuzzer{} is organized to be easily extended:
+PIP package repository.\footnote{The link to the
+source code will be added after double-blind review.}
+\fuzzer{} is organized to be easily extended:
 all generators and transformers are independent Python modules. Its
@@
 can be chained to produce a stream of tuned inputs to a
-solver. Specifically, \fuzzer{} is composed of the following tools:
+solver. \fuzzer{} is composed of the following tools:
 \begin{description}
@@
         \textit{translate} and \textit{reverse} also preserve problem
-        satisfiability \cite{ifaz}.
+        satisfiability under certain conditions~\cite{ifaz}.
     \item[\texttt{stringstats}] \hfill \\
@@
     \end{tabular}
-\end{table}
-
-\begin{table}[H]
     \caption{\transformer{} transformers.}
@@
 regex Kleene star, repetition, and union), up to a specified depth,
-terminating in a regex literal. Below are several example regexes
-(with spacing added for clarity) of depth 2 produced by this scheme:
+terminating in a regex literal. Below are three example regexes
+(separated by spaces) of depth 2 produced by this scheme:
 \begin{align*}
-  & ((\texttt{a}|\texttt{b})|(\texttt{cc})+)\quad
-  ((\texttt{ddd})*)+\quad ((\texttt{ee})+|(\texttt{fff})*)
+  & ((\texttt{a}|\texttt{b})|(\texttt{cc})+)\quad\quad
+  ((\texttt{ddd})*)+\quad\quad ((\texttt{ee})+|(\texttt{fff})*)
 \end{align*}

### 2018-01-31 includes/stringfuzz.tex
Removing minted for now.

@@
 returns an error:
-\vspace{-0.15in}
-\begin{figure}[H]
-    \centering
-    \begin{minipage}[b]{0.91\linewidth}
-        \begin{minted}{bash}
+% \vspace{-0.15in}
+% \begin{figure}[H]
+%     \centering
+%     \begin{minipage}[b]{0.91\linewidth}
+%         \begin{minted}{bash}
+{\scriptsize\begin{verbatim}
 while \
@@
     sleep 0
-done
-        \end{minted}
-    \end{minipage}
-\end{figure}
-\vspace{-0.15in}
+done\end{verbatim}}
+%         \end{minted}
+%     \end{minipage}
+% \end{figure}
+% \vspace{-0.15in}
 
@@
 times out after 5 seconds:
-\vspace{-0.15in}
-\begin{figure}[H]
-    \centering
-    \begin{minipage}[b]{0.91\linewidth}
-        \begin{minted}{bash}
-while true; do
+% \vspace{-0.15in}
+% \begin{figure}[H]
+%     \centering
+%     \begin{minipage}[b]{0.91\linewidth}
+%         \begin{minted}{bash}
+{\scriptsize\begin{verbatim}while true; do
     stringfuzzg -r regex -c -a increasing -r 2 -t 5 -d 3 > problem.smt25
@@
     fi
-done
-        \end{minted}
-    \end{minipage}
-\end{figure}
-\vspace{-0.15in}
+done\end{verbatim}}
+%         \end{minted}
+%     \end{minipage}
+% \end{figure}
+% \vspace{-0.15in}

### 2018-01-31 includes/introduction.tex
Fixing contributions and footnotes.

@@
 \item \textbf{The \fuzzer{} tool}:
-    In section~\ref{sec:fuzzer}, we describe a modular fuzzer that can transform and
-    randomly generate extremal \smtfull{} string and regular expression
-    (regex) problems~\footnote{We assume basic
+    In section~\ref{sec:fuzzer}, we describe a modular fuzzer that can
+    transform and randomly generate \smtfull{} string and regular
+    expression (regex) problems.\footnote{We assume basic
     familiarity with string solvers and their input
-    language.}. Extremal or scaling inputs (e.g., long string
+    language.} Scaling inputs (e.g., long string
     constants, deep concatenations) are particularly useful in
-    identifying asymptotic behaviors in solvers. We briefly document \fuzzer{}'s
+    identifying asymptotic behaviors in solvers, and \fuzzer{}.
+    We briefly document \fuzzer{}'s
     components and modular architecture. We provide example use cases to

### 2018-01-31 includes/problems.tex
Centering and putting tables at the top.
Fixing contributions and footnotes.

@@
 We generated several suites
-of string and regex problems using \fuzzer{}\footnote{The link to the
-repository will be added after double-blind review.}.
+of string and regex problems using \fuzzer{}.\footnote{The link to the
+repository will be added after double-blind review.}
 Table~\ref{tbl:generated} describes the suite
 \texttt{generated} by \generator{}.
-\begin{table}[H]
+\begin{table}[t]
     \centering
@@
 \texttt{fuzz} and then \texttt{graft} from \texttt{seed.smt2}.
-\begin{table}[H]
+\begin{table}[t]
     \centering

### 2018-01-31 includes/experiment.tex
More typos and trailing whitespace.
First pass with Federico.
More edits from meeting.

@@
-\section{Experimental Data}
+\section{Experimental Data and Analysis}
 \label{sec:data}
@@
 \begin{figure}[h]
-        \vspace{-0.2in}
     \begin{subfigure}{.5\textwidth}
         \includegraphics[width=\textwidth]{data/graphs/concats-extracts-small.png}
-            \vspace{-0.25in}
         \caption{Performance on concats-extracts-small}
@@
         \includegraphics[width=\textwidth]{data/graphs/different-prefix.png}
-            \vspace{-0.25in}
         \caption{Performance on different-prefix}
@@
     \end{subfigure}
-        \vspace{-0.1in}
     \caption{Problems hard for \cvc{}}
     \label{fig:cvc-hard}
-        \vspace{-0.3in}
-    \end{figure}
 
-    \begin{figure}[h]
-    \vspace{-0.25in}
     \begin{subfigure}{.5\textwidth}
@@
         \label{fig:concats-balanced}
-            \vspace{-0.25in}
         \caption{Performance on concats-balanced}
@@
         \label{fig:concats-small}
-            \vspace{-0.25in}
         \caption{Performance on concats-small}
     \end{subfigure}
-        \vspace{-0.1in}
     \caption{Problems hard for \us{}}
     \label{fig:z3str3-hard}
-        \vspace{-0.3in}
 \end{figure}
 
-\section{Usefulness to \us{}: A Case Study}
-\label{sec:analysis}
+\subsubsection{Usefulness to \us{}: A Case Study}
 
@@
 therefore introduced a large number of unnecessary intermediate
-variables and propagations.  As an immediate consequence of the
+variables and propagations. As an immediate consequence of
 testing \us{} on \texttt{concats-big} benchmarks, we were able to
@@
 hypothesis as to why they were performing poorly. This allowed us to
-move forward with the development of new heuristic to resolve this
+move forward with the development of a new heuristic to resolve this
 issue and achieve better performance.

### 2018-01-31 includes/introduction.tex
More edits from meeting.

@@
     familiarity with string solvers and their input
-    language.} Scaling inputs (e.g., long string
-    constants, deep concatenations) are particularly useful in
-    identifying asymptotic behaviors in solvers, and \fuzzer{}.
-    We briefly document \fuzzer{}'s
+    language.} SScaling inputs (e.g., long string constants,
+    deep concatenations) are particularly useful in identifying asymptotic
+    behaviors in solvers, and \fuzzer{} has many options to generate such
+    scaling inputs. We briefly document \fuzzer{}'s
     components and modular architecture. We provide example use cases to
@@
     solvers.
+
+    % Further, StringFuzz's modular design lets users extend it to generate scaling inputs along any parameter of the   input constraint.
 
@@
     these suites because they make some solvers perform poorly,
-    but not others. In section~\ref{sec:analysis}, we analyze our
+    but not others. We analyze our
     experimental results, and pinpoint algorithmic limitations

### 2018-01-31 includes/experiment.tex
Removed last sentence of 5.
Removing commented-out sections. Fixing up more content.

@@
-\section{Experimental Data and Analysis}
+\section{Experimental Results and Analysis}
 \label{sec:data}
@@
 suites that were uniquely difficult for \us{}. All experiments were
-run in series on the same Linux computer, with a timeout of 15
-seconds. \todo{Specify CPU, memory}
+run in series, with a timeout of 15 seconds, on the same computer running
+Ubuntu Linux 16.04. The computer had 32GB of RAM and an
+Intel\textregistered{} Core\texttrademark{} i7-6700 CPU with clock speed
+of 3.40GHz.
 
@@
 new heuristics in \us{} thanks to \fuzzer{}. For example, the
-instances in the \texttt{concats-big} suite generated by \fuzzer{}
+instances in the \textit{concats-big} suite generated by \fuzzer{}
 helped us discover a missing heuristic. In particular, \us{} didn't
@@
 variables and propagations. As an immediate consequence of
-testing \us{} on \texttt{concats-big} benchmarks, we were able to
+testing \us{} on \textit{concats-big} benchmarks, we were able to
 identify the factors common to these instances and rapidly formulate a
-hypothesis as to why they were performing poorly. This allowed us to
-move forward with the development of a new heuristic to resolve this
-issue and achieve better performance.
-
-%% %VG: this subsection is not needed in the paper
-%% \noindent{\textbf{Defects discovered and fixed in \us{}:}} The first
-%% issue we found caused \us{} to perform poorly when equivalence classes
-%% of arithmetic terms were very large (e.g. the lengths of many strings
-%% were equal to 0). This issue was detected by the \texttt{Concats}
-%% problem suite. The slowdown was caused by a loop over terms in the
-%% same equivalence class to search for an integer constant. The fix was
-%% to check the root of the equivalence class for the integer constant,
-%% as Z3 makes ``interpreted terms'' (e.g. constants) the root of
-%% equivalence classes whenever possible. The second issue, which was
-%% exposed by the \texttt{Lengths} suite, caused \us{} to perform poorly
-%% when a variable has a large length constraint.  The slowdown was
-%% caused by the solver performing a search for a satisfying length even
-%% when the input formula explicitly constrained the exact length of a
-%% string term.  The fix was to check whether the integer solver had
-%% already assigned a length value before searching for length, and skip
-%% the search if this was the case.
-
-%% In order to improve the efficiency of any solver, discovering new
-%% heuristics is crucial.  As an illustrative example, consider the
-%% problem of how the a string solver may detect conflicting
-%% constraints. A string solver that gradually propagates
-%% (dis)equalities discovered along the way will eventually detect a
-%% conflict.  However, in many scenarios, a conflict can be discovered
-%% ``early'' before trying to figure out the relationships among
-%% subterms and propagating the facts.  The benefits of this eager
-%% approach are clear: this saves the effort of reasoning about
-%% subterms and propagating observations, as a conflict will
-%% eventually be reached in either case, forcing conflict analysis and
-%% a backjump.  As reported in existing works, heuristics of this form
-%% usually lead to significant improvements.  However, the process of
-%% discovering such heuristics is extremely challenging, as they are
-%% usually learned from a class of examples whose commonalities are
-%% not always obvious or immediately indicative of such
-%% inefficiencies.
+hypothesis as to why they were performing poorly.

### 2018-01-31 includes/introduction.tex
Removing commented-out sections. Fixing up more content.

@@
 
-%VG: add citation to SAT fuzzer
 Fuzzing is often used to test all kinds of software,
@@
 leading string solvers. To the best of our knowledge, \fuzzer{} is the
-first tool aimed at automatic generation of string constraints. \fuzzer{} can be
-used to mutate or transform existing benchmarks, as well as
-randomly generate structured instances. These instances can be scaled with respect
-to a variety of parameters, e.g., length of string constants,
+first tool aimed at automatic generation of string constraints. \fuzzer{} can
+be used to mutate or transform existing benchmarks, as well as
+randomly generate structured instances. These instances can be scaled with
+respect to a variety of parameters, e.g., length of string constants,
 depth of concats and regeular expressions, number of variables,
@@
 
-    % Further, StringFuzz's modular design lets users extend it to generate scaling inputs along any parameter of the   input constraint.
-
     \item \textbf{A repository of \smtfull{} problems}:
-    We present a repository of \smtfull{} string and regex problem suites we
-    generated using \fuzzer{} in Section~\ref{sec:problems}. The repository
-    consists of two categories: \texttt{generated}, with new problems generated
-    by \fuzzer{}, and \texttt{transformed}, with transformed problems generated
-    from a small suite of industrial benchmarks.
+        We present a repository of \smtfull{} string and regex problem suites
+        we generated using \fuzzer{} in section~\ref{sec:problems}. The
+        repository consists of two categories: \texttt{generated}, with new
+        problems generated by \fuzzer{}, and \texttt{transformed}, with
+        transformed problems generated from a small suite of industrial
+        benchmarks.
 
@@
         We compare the performance of \theSolvers{} on the
-    the \fuzzer{} suites \theSuites{} in section~\ref{sec:data}. We highlight
-    these suites because they make some solvers perform poorly,
+        the \fuzzer{} suites \theSuites{} in section~\ref{sec:data}. We
+        highlight these suites because they make some solvers perform poorly,
         but not others. We analyze our

### 2018-01-31 includes/problems.tex
Removing commented-out sections. Fixing up more content.

@@
 In this section, we describe the benchmark suites that we generated
-with \fuzzer{} on which the experimental evaluation was conducted.
+with \fuzzer{}, and on which we conducted our experimental
+evaluation.\footnote{The link to the repository will be added after
+double-blind review.}
 
-\subsubsection{Generated Benchmarks}
+Table~\ref{tbl:generated} describes the string and regex instances that were
+generated by \generator{}. Table~\ref{tbl:transformed} lists benchmarks
+derived from existing seed instances by iteratively applying \transformer{}.
+Every transformed instance is named according to its
+seed and the transformations it undertook. For example, input
+\texttt{z3-regex-1-fuzz-graft.smt2} was transformed by applying
+\textit{fuzz} and then \textit{graft} to \texttt{z3-regex-1.smt2}.
 
-We generated several suites
-of string and regex problems using \fuzzer{}.\footnote{The link to the
-repository will be added after double-blind review.}
-Table~\ref{tbl:generated} describes the suite
-\texttt{generated} by \generator{}.
+The \textit{Amazon} category contains 472 instances, derived from two seeds
+supplied by our industrial collaborators. The \textit{Regex} category is
+seeded by the z3str2 regular expression test suite~\cite{z3str2-tests}. This
+test suite contains 42 instances dealing with a wide variety of regular
+expressions. Through cumulative transformations, we expanded it to 7,551
+instances. Finally, the \textit{Sanitizer} category is obtained from
+five industrial e-mail address and IPv4 sanitizers.
+
 \begin{table}[t]
@@
         \hline
-        \textbf{Name}             & \textbf{Problems have ...} \\ \hline
+        \textbf{Name}             & \textbf{Instances have ...} \\ \hline
         \textit{Concats}          & A single, deep tree of concats. \\ \hline
@@
 
-\subsubsection{Transformed Benchmarks}
-
-The \texttt{transformed}
-suite contains benchmarks derived from existing seed problems by
-iteratively applying \transformer{}. Table~\ref{tbl:transformed} shows
-the overview. Every problem in the suite is named according to its
-seed and the transformations it undertook. For example, input
-\texttt{seed-fuzz-graft.smt2} was transformed by applying
-\texttt{fuzz} and then \texttt{graft} from \texttt{seed.smt2}.
 \begin{table}[t]
@@
         \textbf{Name}      & \textbf{Seed}                            & \textbf{Quantity} \\ \hline
-        \textit{Amazon} & Two industrial regex membership problems & 516\\ \hline
-        \textit{Regex}  & Z3str2 regular expression test suite     & 10,577\\ \hline
+        \textit{Amazon}    & Two industrial regex membership problems & 472 \\ \hline
+        \textit{Regex}     & Z3str2 regular expression test suite     & 7,551 \\ \hline
+        \textit{Sanitizer} & 5 e-mail and IPv4 sanitiser examples     & 1,170 \\ \hline
     \end{tabular}
 \end{table}
-
-The Amazon category is obtained from two seeds: (1)
-\texttt{z3-regex-1.smt2} encodes the assertions \texttt{(S not in
-  aaabbb*)} and \texttt{(S in aaa*bbb*)} for a string constant S; (2)
-\texttt{z3-regex-2-negative.smt2} includes regex \texttt{(S in
-  aaabbb*)} and \texttt{(S not in aaa*bbb*)}.  Both problems come from
-our industrial collaborators. In total, 516 unique problems were
-generated from these two seeds. The Regex category is seeded by the
-z3str2 regular expression test suite \cite{z3str2-tests}.  This test
-suite contains 42 problems dealing with a wide variety of regular
-expressions.  Through cumulative transformations, we have $10,577$
-unique benchmarks.

### 2018-01-31 includes/stringfuzz.tex
Centering and putting tables at the top.
More edits from meeting.
Removing commented-out sections. Fixing up more content.

@@
         options that specify its output. Details can be found in
-        Table~\ref{tbl:generators}.
+        table~\ref{tbl:generators}.
     \item[\transformer{}] \hfill \\
@@
         its output and input, which are explained in
-        Table~\ref{tbl:transformers}. Note that transformers
-        \textit{translate} and \textit{reverse} also preserve problem
+        table~\ref{tbl:transformers}. Note that transformers
+        \textit{translate} and \textit{reverse} also preserve
         satisfiability under certain conditions~\cite{ifaz}.
@@
 
-\begin{table}[H]
+\begin{table}[t]
+    \centering
     \caption{\generator{} generators.}
@@
 transformers in \transformer{} can operate on regex terms. They can
-multiply and permute regex literals (e.g. \texttt{reverse},
-\texttt{multiply}, \texttt{translate}), randomly replace regex
-operators (e.g. \texttt{fuzz}), and manipulate the syntax tree
-(e.g. \texttt{graft}, \texttt{rotate}).
+multiply and permute regex literals (e.g. \textit{reverse},
+\textit{multiply}, \textit{translate}), randomly replace regex
+operators (e.g. \textit{fuzz}), and manipulate the syntax tree
+(e.g. \textit{graft}, \textit{rotate}).
 
@@
 {\scriptsize\begin{verbatim}
-while \
-  stringfuzzg -r random-ast -m \
-  | tee problem.smt25 \
-  | cvc4 --lang smt2.5 --tlimit=5000; do
+while stringfuzzg -r random-ast -m | tee problem.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do
     sleep 0

### 2018-01-31 includes/abstract.tex
Increasing consistency. Renaming problems.tex to suites.tex. Using the word 'instance' instead of the word 'problem'.

@@
 \begin{abstract}
-    In this paper, we introduce \fuzzer{}: a modular \smt{} problem
+    In this paper, we introduce \fuzzer{}: a modular \smt{} problem instance
     transformer and generator for string solvers. We supply a
-    repository of problems generated by \fuzzer{} in \smtfull{}
+    repository of instances generated by \fuzzer{} in \smtfull{}
     format. We systematically compare \theSolvers{} on groups of such
-    problems, and identify problems that are particularly challenging for some
-    solvers. We briefly explain our observations and show how
+    instances, and identify instances that are particularly challenging for
+    some solvers. We briefly explain our observations and show how
     \fuzzer{} helped identify causes of performance degradations in

### 2018-01-31 includes/experiment.tex
Increasing consistency. Renaming problems.tex to suites.tex. Using the word 'instance' instead of the word 'problem'.

@@
 
-We generated several problem suites with \fuzzer{} that made one
+We generated several problem instance suites with \fuzzer{} that made one
 solver perform poorly, but not others. These suites are
@@
     \end{subfigure}
-    \caption{Problems hard for \cvc{}}
+    \caption{Instances hard for \cvc{}}
     \label{fig:cvc-hard}
@@
     \end{subfigure}
-    \caption{Problems hard for \us{}}
+    \caption{Instances hard for \us{}}
     \label{fig:z3str3-hard}
@@
 
-We found a number of performance-related issues and opportunities for
+\fuzzer{}'s ability to produce scaling instances (e.g., long string constants,
+concats of increasing depth, etc.) helped uncover several
+implementation issues and performance limitations in \us{}. Scaling inputs
+can reveal issues that would be out of scope for unit tests or
+industrial benchmarks because they elicit asymptotic behaviour. Three different
+performance and implementation bugs were identified and fixed in \us{}
+as a result of testing with the \fuzzer{} suites
+\textit{Lengths} and \textit{Concats}.
+
+We also found a number of performance-related issues and opportunities for
 new heuristics in \us{} thanks to \fuzzer{}. For example, the
-instances in the \textit{concats-big} suite generated by \fuzzer{}
+instances in the \textit{Concats} suite generated by \fuzzer{}
 helped us discover a missing heuristic. In particular, \us{} didn't
@@
 variables and propagations. As an immediate consequence of
-testing \us{} on \textit{concats-big} benchmarks, we were able to
+testing \us{} on \textit{Concats} benchmarks, we were able to
 identify the factors common to these instances and rapidly formulate a

### 2018-01-31 includes/introduction.tex
Increasing consistency. Renaming problems.tex to suites.tex. Using the word 'instance' instead of the word 'problem'.

@@
         transform and randomly generate \smtfull{} string and regular
-        expression (regex) problems.\footnote{We assume basic
+        expression (regex) instances.\footnote{We assume basic
         familiarity with string solvers and their input
-        language.} SScaling inputs (e.g., long string constants,
+        language.} Scaling inputs (e.g., long string constants,
         deep concatenations) are particularly useful in identifying asymptotic
@@
 
-    \item \textbf{A repository of \smtfull{} problems}:
+    \item \textbf{A repository of \smtfull{} instances}:
         We present a repository of \smtfull{} string and regex problem suites
-        we generated using \fuzzer{} in section~\ref{sec:problems}. The
+        we generated using \fuzzer{} in section~\ref{sec:suites}. The
         repository consists of two categories: \texttt{generated}, with new
-        problems generated by \fuzzer{}, and \texttt{transformed}, with
-        transformed problems generated from a small suite of industrial
+        instances generated by \fuzzer{}, and \texttt{transformed}, with
+        transformed instances generated from a small suite of industrial
         benchmarks.

### 2018-01-31 includes/prior.tex
cleaned up the paper a lot
First pass with Federico.
Increasing consistency. Renaming problems.tex to suites.tex. Using the word 'instance' instead of the word 'problem'.

@@
 
-    Naturally, many solver developers author their own test suites to validate their solvers~\cite{cvc4-tests,z3str3-tests,z3str2-tests}.
-In addition, several popular problem suites are publicly available for solver validation, such as the Kaluza~\cite{kaluza} and Kausler~\cite{kausler} suites.
-
-    There are likewise several fuzzers and problem generators currently available, but none of them can generate or transform string and regex problems.
-For example, the FuzzSMT~\cite{fuzzsmt} tool generates \smt{} problems with bit-vectors and arrays, but does not support strings or regexes.
-The SMTpp~\cite{smtpp} tool pre-processes and simplifies problems, but does not generate new ones or fuzz existing ones.
-
-% FuzzSMT: http://fmv.jku.at/papers/BrummayerBiere-SMT09.pdf
-% SMTpp: http://www.verit-solver.org/papers/smt2015.pdf
+Many solver developers author their own test suites to
+validate their solvers~\cite{cvc4-tests,z3str3-tests,z3str2-tests}. In
+addition, several popular instance suites are publicly available for
+solver testing and benchmarking, such as the Kaluza~\cite{kaluza} and
+Kausler~\cite{kausler} suites. There are likewise several fuzzers and
+instance generators currently available, but none of them can generate
+or transform string and regex instances. For example, the
+FuzzSMT~\cite{fuzzsmt} tool generates \smt{} instances with bit-vectors
+and arrays, but does not support strings or regexes. The
+SMTpp~\cite{smtpp} tool pre-processes and simplifies instances, but
+does not generate new ones or fuzz existing ones.

### 2018-01-31 includes/stringfuzz.tex
Increasing consistency. Renaming problems.tex to suites.tex. Using the word 'instance' instead of the word 'problem'.

@@
         table~\ref{tbl:transformers}. Note that transformers
-        \textit{translate} and \textit{reverse} also preserve
+        \textit{Translate} and \textit{Reverse} also preserve
         satisfiability under certain conditions~\cite{ifaz}.
@@
         \textbf{Name}        & \textbf{Generated Problems have ...} \\ \hline
-        \textit{concats}     & Long concats and optional random extracts. \\ \hline
-        \textit{lengths}     & Many variables (and their concats) with length constraints. \\ \hline
-        \textit{overlaps}    & An expression of the form A.X = X.B. \\ \hline
-        \textit{equality}    & An equality among concats, each with variables or constants. \\ \hline
-        \textit{regex}       & Regexes of varying complexity. \\ \hline
-        \textit{random-text} & Random, likely syntactically \textit{in}valid text. \\ \hline
-        \textit{random-ast}  & Random, but semantically \textit{valid} text. \\ \hline
+        \textit{Concats}     & Long concats and optional random extracts. \\ \hline
+        \textit{Lengths}     & Many variables (and their concats) with length constraints. \\ \hline
+        \textit{Overlaps}    & An expression of the form A.X = X.B. \\ \hline
+        \textit{Equality}    & An equality among concats, each with variables or constants. \\ \hline
+        \textit{Regex}       & Regexes of varying complexity. \\ \hline
+        \textit{Random-Text} & Random, likely syntactically \textit{in}valid text. \\ \hline
+        \textit{Random-AST}  & Random, but semantically \textit{valid} text. \\ \hline
     \end{tabular}
@@
         \textbf{Name}        & \textbf{The transformer ...} \\ \hline
-        \textit{fuzz}        & Randomly replaces literals and operators with similar ones. \\ \hline
-        \textit{graft}       & For each sort, swaps a random non-leaf node with a leaf node. \\ \hline
-        \textit{multiply}    & Multiplies each number by N, and repeats each character N times. \\ \hline
-        \textit{nop}         & Does nothing. \\ \hline
-        \textit{reverse}     & Reverses all string literals and concat arguments. \\ \hline
-        \textit{rotate}      & Performs a random syntax tree rotation on two concats. \\ \hline
-        \textit{translate}   & Maps every character X to a different character Y. \\ \hline
-        \textit{unprintable} & Randomly replaces all characters in literals with unprintable ones. \\ \hline
+        \textit{Fuzz}        & Randomly replaces literals and operators with similar ones. \\ \hline
+        \textit{Graft}       & For each sort, swaps a random non-leaf node with a leaf node. \\ \hline
+        \textit{Multiply}    & Multiplies each number by N, and repeats each character N times. \\ \hline
+        \textit{Nop}         & Doesn't transform (but can translate \smtfull{}). \\ \hline
+        \textit{Reverse}     & Reverses all string literals and concat arguments. \\ \hline
+        \textit{Rotate}      & Performs a random syntax tree rotation on two concats. \\ \hline
+        \textit{Translate}   & Maps every character X to a different character Y. \\ \hline
+        \textit{Unprintable} & Randomly replaces all characters in literals with unprintable ones. \\ \hline
     \end{tabular}
@@
 transformers in \transformer{} can operate on regex terms. They can
-multiply and permute regex literals (e.g. \textit{reverse},
-\textit{multiply}, \textit{translate}), randomly replace regex
-operators (e.g. \textit{fuzz}), and manipulate the syntax tree
-(e.g. \textit{graft}, \textit{rotate}).
+multiply and permute regex literals (e.g. \textit{Reverse},
+\textit{Multiply}, \textit{Translate}), randomly replace regex
+operators (e.g. \textit{Fuzz}), and manipulate the syntax tree
+(e.g. \textit{Graft}, \textit{Rotate}).
 

### 2018-01-31 includes/introduction.tex
More renaming.

@@
     \item \textbf{A repository of \smtfull{} instances}:
-        We present a repository of \smtfull{} string and regex problem suites
+        We present a repository of \smtfull{} string and regex instance suites
         we generated using \fuzzer{} in section~\ref{sec:suites}. The

### 2018-01-31 includes/stringfuzz.tex
More renaming.

@@
 executables to generate, transform, and analyze \smtfull{} string and regex
-problems. It can either be installed from source, or from the Python
+instances. It can either be installed from source, or from the Python
 PIP package repository.\footnote{The link to the
@@
     \item[\generator{}] \hfill \\
-        This tool generates \smt{} problems. It supports several generators and
+        This tool generates \smt{} instances. It supports several generators and
         options that specify its output. Details can be found in
@@
         This tool transforms \smt{}
-        problems. It supports several transformers and options that specify
+        instances. It supports several transformers and options that specify
         its output and input, which are explained in
@@
         This tool takes an \smt{}
-        problem as input and outputs its properties: the number of
+        instance as input and outputs its properties: the number of
         variables/literals, the max/median syntactic depth of expressions, the
@@
         \hline
-        \textbf{Name}        & \textbf{Generated Problems have ...} \\ \hline
+        \textbf{Name}        & \textbf{Generated instances have ...} \\ \hline
         \textit{Concats}     & Long concats and optional random extracts. \\ \hline
@@
 \fuzzer{} can generate
-and transform problems with regular expression constraints. The
-command \texttt{stringfuzzg regex} invokes the regex problem
-generator. It generates a problem of the form:
+and transform instances with regular expression constraints. The
+command \texttt{stringfuzzg regex} invokes the regex instance
+generator. It generates a instance of the form:
 \begin{align*}
@@
 where $R_i \in RegEx$, and $Min, Max \in Int$. More simply, the
-problem is a set of one or more regex constraints on a single
+instance is a set of one or more regex constraints on a single
 variable, with optional maximum and minimum length constraints. The
@@
 randomized fashion for exploratory debugging. For example, \fuzzer{}
-can be invoked as follows to feed random problems to \cvc{} until it
+can be invoked as follows to feed random instances to \cvc{} until it
 returns an error:
@@
 {\scriptsize\begin{verbatim}
-while stringfuzzg -r random-ast -m | tee problem.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do
+while stringfuzzg -r random-ast -m | tee instance.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do
     sleep 0
@@
 Some more \unix{} scripting can yield other interesting results. For
-example, the following script finds a regex problem on which \us{}
+example, the following script finds a regex instance on which \us{}
 times out after 5 seconds:
@@
 {\scriptsize\begin{verbatim}while true; do
-    stringfuzzg -r regex -c -a increasing -r 2 -t 5 -d 3 > problem.smt25
-    result=`z3str3 -T:5 problem.smt25`
+    stringfuzzg -r regex -c -a increasing -r 2 -t 5 -d 3 > instance.smt25
+    result=`z3str3 -T:5 instance.smt25`
     echo $result
     if [ "$result" == "timeout" ]; then
-        cat problem.smt25
+        cat instance.smt25
         break

### 2018-01-31 includes/suites.tex
Increasing consistency. Renaming problems.tex to suites.tex. Using the word 'instance' instead of the word 'problem'.
More renaming.

--- 2018-01-31 includes/problems.tex
@@
-\section{Problem Suites}
-\label{sec:problems}
+\section{Instance Suites}
+\label{sec:suites}
 
@@
 \texttt{z3-regex-1-fuzz-graft.smt2} was transformed by applying
-\textit{fuzz} and then \textit{graft} to \texttt{z3-regex-1.smt2}.
+\textit{Fuzz} and then \textit{Graft} to \texttt{z3-regex-1.smt2}.
 
@@
     \centering
-    \caption{\generator{}-generated problem sets.}
+    \caption{\generator{}-generated instances.}
     \label{tbl:generated}
@@
         \textbf{Name}             & \textbf{Instances have ...} \\ \hline
-        \textit{Concats}          & A single, deep tree of concats. \\ \hline
+        \textit{Concats}          & A right-heavy, deep tree of concats. \\ \hline
+        \textit{Concats-Balanced} & A balanced, deep tree of concats. \\ \hline
         \textit{Concats-Extracts} & A single concat tree, and random character extractions. \\ \hline
@@
     \centering
-    \caption{Transformed problem sets generated by \transformer{}.}
+    \caption{Transformed instances generated by \transformer{}.}
     \label{tbl:transformed}
@@
         \textbf{Name}      & \textbf{Seed}                             & \textbf{Quantity} \\ \hline
-        \textit{Amazon}    & Two industrial regex membership problems & 472 \\ \hline
+        \textit{Amazon}    & Two industrial regex membership instances & 472 \\ \hline
         \textit{Regex}     & Z3str2 regular expression test suite      & 7,551 \\ \hline

### 2018-01-31 includes/experiment.tex
Adding more data to tables. Formatting tables for easier editing. Adding two more test problems.

@@
         \includegraphics[width=\textwidth]{data/graphs/concats-extracts-small.png}
-        \caption{Performance on concats-extracts-small}
+        \caption{Performance on \textit{Concats-Extracts-Small}}
         \label{fig:concats-extracts-small}
@@
         \includegraphics[width=\textwidth]{data/graphs/different-prefix.png}
-        \caption{Performance on different-prefix}
+        \caption{Performance on \textit{Different-Prefix}}
         \label{fig:different-prefix}
@@
 
+    \vspace{0.15in}
+
     \begin{subfigure}{.5\textwidth}
@@
         \label{fig:concats-balanced}
-        \caption{Performance on concats-balanced}
+        \caption{Performance on \textit{Concats-Balanced}}
     \end{subfigure}
@@
         \label{fig:concats-small}
-        \caption{Performance on concats-small}
+        \caption{Performance on \textit{Concats-Small}}
     \end{subfigure}
@@
 
-\fuzzer{}'s ability to produce scaling instances (e.g., long string constants,
-concats of increasing depth, etc.) helped uncover several
+\fuzzer{}'s ability to produce scaling instances helped uncover several
 implementation issues and performance limitations in \us{}. Scaling inputs

### 2018-01-31 includes/stringfuzz.tex
Adding more data to tables. Formatting tables for easier editing. Adding two more test problems.

@@
 \label{sec:fuzzer}
+
+\subsubsection{Implementation and Architecture}
 
@@
 \fuzzer{} is organized to be easily extended:
-all generators and transformers are independent Python modules. Its
-components are also implemented as \unix{} ``filters'', to enable easy
+all generators and transformers are independent Python modules. To demonstrate
+its modularity, we note that the implementations of transformers in \fuzzer{}
+contain an average of \linesPerX{} lines of code, whereas the whole fuzzer
+contains \linesInFuzzer{} lines.
+
+Its components are also implemented as \unix{} ``filters'', to enable easy
 integration with other tools (including themselves). For example, the
@@
         \hline
-        \textbf{Name}        & \textbf{Generated instances have ...} \\ \hline
-        \textit{Concats}     & Long concats and optional random extracts. \\ \hline
-        \textit{Lengths}     & Many variables (and their concats) with length constraints. \\ \hline
-        \textit{Overlaps}    & An expression of the form A.X = X.B. \\ \hline
-        \textit{Equality}    & An equality among concats, each with variables or constants. \\ \hline
-        \textit{Regex}       & Regexes of varying complexity. \\ \hline
-        \textit{Random-Text} & Random, likely syntactically \textit{in}valid text. \\ \hline
-        \textit{Random-AST}  & Random, but semantically \textit{valid} text. \\ \hline
+        \textbf{Name}
+            & \textbf{Generated instances have ...}
+            \\ \hline
+        \textit{Concats}
+            & Long concats and optional random extracts.
+            \\ \hline
+        \textit{Lengths}
+            & Many variables (and their concats) with length constraints.
+            \\ \hline
+        \textit{Overlaps}
+            & An expression of the form A.X = X.B.
+            \\ \hline
+        \textit{Equality}
+            & An equality among concats, each with variables or constants.
+            \\ \hline
+        \textit{Regex}
+            & Regexes of varying complexity.
+            \\ \hline
+        \textit{Random-Text}
+            & Random, likely syntactically \textit{in}valid text.
+            \\ \hline
+        \textit{Random-AST}
+            & Random, but semantically \textit{valid} text.
+            \\ \hline
     \end{tabular}
+
     \caption{\transformer{} transformers.}
@@
         \hline
-        \textbf{Name}        & \textbf{The transformer ...} \\ \hline
-        \textit{Fuzz}        & Randomly replaces literals and operators with similar ones. \\ \hline
-        \textit{Graft}       & For each sort, swaps a random non-leaf node with a leaf node. \\ \hline
-        \textit{Multiply}    & Multiplies each number by N, and repeats each character N times. \\ \hline
-        \textit{Nop}         & Doesn't transform (but can translate \smtfull{}). \\ \hline
-        \textit{Reverse}     & Reverses all string literals and concat arguments. \\ \hline
-        \textit{Rotate}      & Performs a random syntax tree rotation on two concats. \\ \hline
-        \textit{Translate}   & Maps every character X to a different character Y. \\ \hline
-        \textit{Unprintable} & Randomly replaces all characters in literals with unprintable ones. \\ \hline
+        \textbf{Name}
+            & \textbf{The transformer ...}
+            \\ \hline
+        \textit{Fuzz}
+            & Randomly replaces literals and operators with similar ones.
+            \\ \hline
+        \textit{Graft}
+            & For each sort, swaps a random non-leaf node with a leaf node.
+            \\ \hline
+        \textit{Multiply}
+            & Multiplies each number by N, and repeats each character N times.
+            \\ \hline
+        \textit{Nop}
+            & Doesn't transform (but can translate \smtfull{}).
+            \\ \hline
+        \textit{Reverse}
+            & Reverses all string literals and concat arguments.
+            \\ \hline
+        \textit{Rotate}
+            & Performs a random syntax tree rotation on two concats.
+            \\ \hline
+        \textit{Translate}
+            & Maps every character X to a different character Y.
+            \\ \hline
+        \textit{Unprintable}
+            & Randomly replaces all characters in literals with unprintable ones.
+            \\ \hline
     \end{tabular}
@@
 
-\subsubsection{Example Use Cases}
+\subsubsection{Example Use Case}
 
-\fuzzer{} can be used to
-generate benchmark suites in a batch mode, or can be used in an online
-randomized fashion for exploratory debugging. For example, \fuzzer{}
-can be invoked as follows to feed random instances to \cvc{} until it
+\fuzzer{} can be used to generate benchmark suites in a batch mode, but also
+in an online randomized fashion for exploratory debugging. For example,
+\fuzzer{} can be invoked as follows to feed random instances to \cvc{} until it
 returns an error:
-% \vspace{-0.15in}
-% \begin{figure}[H]
-%     \centering
-%     \begin{minipage}[b]{0.91\linewidth}
-%         \begin{minted}{bash}
 {\scriptsize\begin{verbatim}
@@
 done\end{verbatim}}
-%         \end{minted}
-%     \end{minipage}
-% \end{figure}
-% \vspace{-0.15in}
 
-Some more \unix{} scripting can yield other interesting results. For
-example, the following script finds a regex instance on which \us{}
-times out after 5 seconds:
-% \vspace{-0.15in}
-% \begin{figure}[H]
-%     \centering
-%     \begin{minipage}[b]{0.91\linewidth}
-%         \begin{minted}{bash}
-{\scriptsize\begin{verbatim}while true; do
-    stringfuzzg -r regex -c -a increasing -r 2 -t 5 -d 3 > instance.smt25
-    result=`z3str3 -T:5 instance.smt25`
-    echo $result
-    if [ "$result" == "timeout" ]; then
-        cat instance.smt25
-        break
-    fi
-done\end{verbatim}}
-%         \end{minted}
-%     \end{minipage}
-% \end{figure}
-% \vspace{-0.15in}
+Simply by running the above script, we managed to induce segmentation faults
+in \cvc{} and \us{}.

### 2018-01-31 includes/abstract.tex
Adding citation for FuzzSAT. Fixing up more content.

@@
     format. We systematically compare \theSolvers{} on groups of such
-    instances, and identify instances that are particularly challenging for
+    instances, and identify the ones that are particularly challenging for
     some solvers. We briefly explain our observations and show how
-    \fuzzer{} helped identify causes of performance degradations in
+    \fuzzer{} helped find causes of performance degradations in
     \us{}.

### 2018-01-31 includes/experiment.tex
Adding citation for FuzzSAT. Fixing up more content.

@@
 performance and implementation bugs were identified and fixed in \us{}
-as a result of testing with the \fuzzer{} suites
+as a result of testing with the \fuzzer{} scaling suites
 \textit{Lengths} and \textit{Concats}.
@@
 new heuristics in \us{} thanks to \fuzzer{}. For example, the
-instances in the \textit{Concats} suite generated by \fuzzer{}
-helped us discover a missing heuristic. In particular, \us{} didn't
+instances in the \textit{Concats} suite helped us discover a
+potential new heuristic. In particular, \us{} didn't
 make full use of the solving context (e.g. some terms are empty
@@
 therefore introduced a large number of unnecessary intermediate
-variables and propagations. As an immediate consequence of
-testing \us{} on \textit{Concats} benchmarks, we were able to
-identify the factors common to these instances and rapidly formulate a
-hypothesis as to why they were performing poorly.
+variables and propagations. As a consequence of
+testing \us{} with the \textit{Concats} suite, we were able to
+identify the factors common to its instances, examine \us{}'s execution
+traces on them, and rapidly formulate a hypothesis as to why \us{}
+was performing poorly.

### 2018-01-31 includes/introduction.tex
Adding citation for FuzzSAT. Fixing up more content.

@@
 
-In recent years many algorithms for solving string constraints have
+In recent years, many algorithms for solving string constraints have
 been developed and implemented in SMT solvers such as Norn~\cite{norn},
@@
 hand-crafted input suites~\cite{cvc4-tests,z3str3-tests,z3str2-tests} or
-real-world examples from a limited class of industrial
+real-world examples from a limited set of industrial
 applications~\cite{kaluza,kausler}. These test suites have helped
@@
 Fuzzing is often used to test all kinds of software,
-including SAT solvers. Inspired by their utility, we introduce a
-fuzzer for string solvers, \fuzzer{}, and describe its value as an
-exploratory validation tool. We demonstrate its efficacy
+including SAT solvers~\cite{fuzzsat}. Inspired by the utility of fuzzers,
+we introduce a fuzzer for string solvers, \fuzzer{}, and describe its value
+as an exploratory testing tool. We demonstrate its efficacy
 by presenting limitations it helped us find in
@@
         In section~\ref{sec:fuzzer}, we describe a modular fuzzer that can
-        transform and randomly generate \smtfull{} string and regular
+        transform and generate \smtfull{} string and regular
         expression (regex) instances.\footnote{We assume basic
@@
         deep concatenations) are particularly useful in identifying asymptotic
-        behaviors in solvers, and \fuzzer{} has many options to generate such
-        scaling inputs. We briefly document \fuzzer{}'s
-        components and modular architecture. We provide example use cases to
-        demonstrate its utility as an exploratory tool for validating
-        solvers.
+        behaviors in solvers, and \fuzzer{} has many options to generate them.
+        We briefly document \fuzzer{}'s components and modular architecture.
+        We provide example use cases to demonstrate its utility as an
+        exploratory solver testing tool.
 
@@
         experimental results, and pinpoint algorithmic limitations
-        in \us{} that cause poor performance. We propose enhancements that
-        address these issues, which \fuzzer{} helped us find.
+        in \us{} that cause poor performance.
 \end{enumerate}

### 2018-01-31 includes/prior.tex
Adding citation for FuzzSAT. Fixing up more content.

@@
 
-Many solver developers author their own test suites to
-validate their solvers~\cite{cvc4-tests,z3str3-tests,z3str2-tests}. In
-addition, several popular instance suites are publicly available for
+Many solver developers create their own test suites to
+validate their solvers~\cite{cvc4-tests,z3str3-tests,z3str2-tests}. Several
+popular instance suites are also publicly available for
 solver testing and benchmarking, such as the Kaluza~\cite{kaluza} and

### 2018-01-31 includes/stringfuzz.tex
Adding citation for FuzzSAT. Fixing up more content.

@@
 its modularity, we note that the implementations of transformers in \fuzzer{}
-contain an average of \linesPerX{} lines of code, whereas the whole fuzzer
-contains \linesInFuzzer{} lines.
-
-Its components are also implemented as \unix{} ``filters'', to enable easy
+contain \linesPerX{} lines of code on average, whereas the whole fuzzer
+contains \linesInFuzzer{} lines. Its components are also
+implemented as \unix{} ``filters'', to enable easy
 integration with other tools (including themselves). For example, the
@@
 \begin{align*}
-  & \texttt{(re.++}\; \ T_0\; \ T_1\; \texttt{...}\; T_n\; \texttt{)}
+  & \texttt{(re.++}\; T_0\; \texttt{(re.++}\; T_1\;
+  \texttt{...}\; \texttt{(re.++}\; T_{n-1}\; T_n\; \texttt{))}
 \end{align*}
@@
 regex constants. Informally, this form describes a concatenation of
-regex terms. Each term is a random nested regex operator (chosen from
+regex terms, where each term is a random nested regex operator (chosen from
 regex Kleene star, repetition, and union), up to a specified depth,
@@
 {\scriptsize\begin{verbatim}
-while stringfuzzg -r random-ast -m | tee instance.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do
+while stringfuzzg -r random-ast -m \
+    | tee instance.smt25 | cvc4 --lang smt2.5 --tlimit=5000 --strings-exp; do
     sleep 0
 done\end{verbatim}}
-
-Simply by running the above script, we managed to induce segmentation faults
-in \cvc{} and \us{}.

### 2018-01-31 includes/abstract.tex
Pass of paper

@@
     In this paper, we introduce \fuzzer{}: a modular \smt{} problem instance
-    transformer and generator for string solvers. We supply a
+    transformer and generator. We supply a
     repository of instances generated by \fuzzer{} in \smtfull{}
     format. We systematically compare \theSolvers{} on groups of such
-    instances, and identify the ones that are particularly challenging for
+    instances, and identify those that are particularly challenging for
     some solvers. We briefly explain our observations and show how
-    \fuzzer{} helped find causes of performance degradations in
+    \fuzzer{} helped discover causes of performance degradations in
     \us{}.

### 2018-01-31 includes/experiment.tex
Pass of paper

@@
 solver perform poorly, but not others. These suites are
-\theSuites{}. Figure~\ref{fig:cvc-hard} shows the suites that were
-uniquely difficult for \cvc{}. Figure~\ref{fig:z3str3-hard} shows the
+\theSuites{}. Fig.~\ref{fig:cvc-hard} shows the suites that were
+uniquely difficult for \cvc{}. Fig.~\ref{fig:z3str3-hard} shows the
 suites that were uniquely difficult for \us{}. All experiments were
-run in series, with a timeout of 15 seconds, on the same computer running
-Ubuntu Linux 16.04. The computer had 32GB of RAM and an
-Intel\textregistered{} Core\texttrademark{} i7-6700 CPU with clock speed
-of 3.40GHz.
+conducted in series, each with a timeout of 15 seconds,
+on an Ubuntu Linux 16.04 computer with 32GB of RAM and an
+Intel\textregistered{} Core\texttrademark{} i7-6700 CPU (3.40GHz).
 
@@
 implementation issues and performance limitations in \us{}. Scaling inputs
-can reveal issues that would be out of scope for unit tests or
-industrial benchmarks because they elicit asymptotic behaviour. Three different
+can reveal issues that would normally be out of scope for unit tests or
+industrial benchmarks. Three different
 performance and implementation bugs were identified and fixed in \us{}
@@
 
-We also found a number of performance-related issues and opportunities for
-new heuristics in \us{} thanks to \fuzzer{}. For example, the
-instances in the \textit{Concats} suite helped us discover a
-potential new heuristic. In particular, \us{} didn't
+\fuzzer also helped identify a number of performance-related issues and opportunities for
+new heuristics in \us{}. For example, by examining \us{}'s execution traces on the
+instances in the \textit{Concats} suite we discovered a
+potential new heuristic. In particular, \us{} does not
 make full use of the solving context (e.g. some terms are empty
 strings) to simplify the concatenations of a long list of string terms
-before trying to reason about the equivalences among subterms. \us{}
-therefore introduced a large number of unnecessary intermediate
-variables and propagations. As a consequence of
-testing \us{} with the \textit{Concats} suite, we were able to
-identify the factors common to its instances, examine \us{}'s execution
-traces on them, and rapidly formulate a hypothesis as to why \us{}
-was performing poorly.
+before trying to reason about the equivalences among sub-terms. \us{}
+therefore introduces a large number of unnecessary intermediate
+variables and propagations.

### 2018-01-31 includes/introduction.tex
Pass of paper

@@
 developers identify implementation defects and develop more
-sophisticated solving heuristics. Unfortunately, as solvers grow,
-fixed benchmarks leave more functionality untested.
-There is an acute need for a more robust, inexpensive, and automatic way
+sophisticated solving heuristics. Unfortunately, as solvers grow
+fixed benchmarks remain stagnant, leaving increasing functionality untested.
+As such, there is an acute need for a more robust, inexpensive, and automatic way
 of generating benchmarks to test
@@
 
-Fuzzing is often used to test all kinds of software,
-including SAT solvers~\cite{fuzzsat}. Inspired by the utility of fuzzers,
-we introduce a fuzzer for string solvers, \fuzzer{}, and describe its value
+Fuzzing has been used to test all kinds of software
+including SAT solvers~\cite{fuzzsat}. Inspired by these fuzzers,
+we introduce \fuzzer{} and describe its value
 as an exploratory testing tool. We demonstrate its efficacy
-by presenting limitations it helped us find in
+by presenting limitations it helped discover in
 leading string solvers. To the best of our knowledge, \fuzzer{} is the
-first tool aimed at automatic generation of string constraints. \fuzzer{} can
+only tool aimed at automatic generation of string constraints. \fuzzer{} can
 be used to mutate or transform existing benchmarks, as well as
@@
 respect to a variety of parameters, e.g., length of string constants,
-depth of concats and regeular expressions, number of variables,
+depth of concatenations (concats) and regular expressions, number of variables,
 number of length constraints, and many more.
@@
     \item \textbf{The \fuzzer{} tool}:
-        In section~\ref{sec:fuzzer}, we describe a modular fuzzer that can
+        In Sect.~\ref{sec:fuzzer}, we describe a modular fuzzer that can
         transform and generate \smtfull{} string and regular
@@
         We present a repository of \smtfull{} string and regex instance suites
-        we generated using \fuzzer{} in section~\ref{sec:suites}. The
-        repository consists of two categories: \texttt{generated}, with new
-        instances generated by \fuzzer{}, and \texttt{transformed}, with
+        that we generated using \fuzzer{} in Sect.~\ref{sec:suites}. This
+        repository consists of two categories: one with new
+        instances generated by \fuzzer{} (\texttt{generated}); and another with
         transformed instances generated from a small suite of industrial
-        benchmarks.
+        benchmarks (\texttt{transformed}).
 
@@
         We compare the performance of \theSolvers{} on the
-        the \fuzzer{} suites \theSuites{} in section~\ref{sec:data}. We
+        the \fuzzer{} suites \theSuites{} in Sect.~\ref{sec:data}. We
         highlight these suites because they make some solvers perform poorly,

### 2018-01-31 includes/stringfuzz.tex
Pass of paper

@@
 executables to generate, transform, and analyze \smtfull{} string and regex
-instances. It can either be installed from source, or from the Python
-PIP package repository.\footnote{The link to the
-source code will be added after double-blind review.}
-\fuzzer{} is organized to be easily extended:
-all generators and transformers are independent Python modules. To demonstrate
-its modularity, we note that the implementations of transformers in \fuzzer{}
-contain \linesPerX{} lines of code on average, whereas the whole fuzzer
-contains \linesInFuzzer{} lines. Its components are also
-implemented as \unix{} ``filters'', to enable easy
+instances. Its components are implemented as \unix{} ``filters'' to enable easy
 integration with other tools (including themselves). For example, the
@@
 solver. \fuzzer{} is composed of the following tools:
+
 \begin{description}
@@
     options that specify its output. Details can be found in
-        table~\ref{tbl:generators}.
+    Table~\ref{tbl:generators}.
     \item[\transformer{}] \hfill \\
@@
     its output and input, which are explained in
-        table~\ref{tbl:transformers}. Note that transformers
+    Table~\ref{tbl:transformers}. Note that transformers
     \textit{Translate} and \textit{Reverse} also preserve
@@
 
+We organized \fuzzer{} to be easily extended. As evidence of our success we note
+that while the whole project 
+contains \linesInFuzzer{} lines of code, it takes an average of 
+\linesPerX{} lines of code to create a transformer. \fuzzer{} can either be 
+installed from source, or from the Python PIP package
+repository.\footnote{The link to the source code will be added after double-blind review.}
+
 \begin{table}[t]
     \centering
-    \caption{\generator{} generators.}
+    \caption{\generator{} built-in generators.}
     \label{tbl:generators}
@@
         \textbf{Name}
-            & \textbf{Generated instances have ...}
+        & \textbf{Generate instances that have ...}
         \\ \hline
@@
 
-    \caption{\transformer{} transformers.}
+    \caption{\transformer{} built-in transformers.}
     \label{tbl:transformers}
-    \begin{tabular}{|l|l|}
+    \begin{tabular}{|l|l|l|}
         \hline
@@
         & \textbf{The transformer ...}
+        & \textbf{Guarantee}\footnote{See Appendix for proofs and restrictions.}
         \\ \hline
@@
         & Randomly replaces literals and operators with similar ones.
+        & Well-formed
         \\ \hline
@@
         & For each sort, swaps a random non-leaf node with a leaf node.
+        & Well-formed
         \\ \hline
@@
         & Multiplies each number by N, and repeats each character N times.
+        & Sat-sat
         \\ \hline
         \textit{Nop}
-            & Doesn't transform (but can translate \smtfull{}).
+        & Does not transform (can translate between \smtfull{}).
+        & Equisat
         \\ \hline
@@
         & Reverses all string literals and concat arguments.
+        & Equisat
         \\ \hline
         \textit{Rotate}
-            & Performs a random syntax tree rotation on two concats.
+        & Performs a syntax tree rotation on compatible operators.
+        & Well-formed
         \\ \hline
         \textit{Translate}
-            & Maps every character X to a different character Y.
+        & Permutes the alphabet.
+        & Equisat
         \\ \hline
@@
         & Randomly replaces all characters in literals with unprintable ones.
+        & Equisat
         \\ \hline
@@
 \fuzzer{} can generate
-and transform instances with regular expression constraints. The
+and transform instances with regular expression constraints. For example, the
 command \texttt{stringfuzzg regex} invokes the regex instance
-generator. It generates a instance of the form:
+generator and produces an instance of the form:
 \begin{align*}
@@
 regex Kleene star, repetition, and union), up to a specified depth,
-terminating in a regex literal. Below are three example regexes
+terminating in a regex literal. Below are three example regex instances
 (separated by spaces) of depth 2 produced by this scheme:
@@
 
-\fuzzer{} can also transform the instances it generates. All of the
-transformers in \transformer{} can operate on regex terms. They can
-multiply and permute regex literals (e.g. \textit{Reverse},
-\textit{Multiply}, \textit{Translate}), randomly replace regex
-operators (e.g. \textit{Fuzz}), and manipulate the syntax tree
-(e.g. \textit{Graft}, \textit{Rotate}).
+\fuzzer{} can also transform problem instances.
+This is done by manipulating parsed syntax trees.
+By default most of the built-in transformers 
+only guarantee well-formedness, however,
+some can even guarantee equisatisfiability. Table~\ref{tbl:transformers} 
+lists the built-in transformers and these guarantees.
 
 \subsubsection{Example Use Case}
-
-\fuzzer{} can be used to generate benchmark suites in a batch mode, but also
-in an online randomized fashion for exploratory debugging. For example,
-\fuzzer{} can be invoked as follows to feed random instances to \cvc{} until it
-returns an error:
+In Sect.~\ref{sec:suites} we use \fuzzer{} to generate benchmark suites in a batch mode.
+We can also use \fuzzer{} for on-line exploratory debugging. 
+For example, the script below repeatedly feeds random \fuzzer{} 
+instances to \cvc{} until the solver produces an error:
 {\scriptsize\begin{verbatim}

### 2018-01-31 includes/suites.tex
Adding more data to tables. Formatting tables for easier editing. Adding two more test problems.
Adding citation for FuzzSAT. Fixing up more content.
Pass of paper

@@
 
-In this section, we describe the benchmark suites that we generated
+In this section, we describe the benchmark suites we generated
 with \fuzzer{}, and on which we conducted our experimental
@@
 
-The \textit{Amazon} category contains 472 instances, derived from two seeds
+The \textit{Amazon} category contains 472 instances derived from two seeds
 supplied by our industrial collaborators. The \textit{Regex} category is
-seeded by the z3str2 regular expression test suite~\cite{z3str2-tests}. This
+seeded by the \usOld{} regular expression test suite~\cite{z3str2-tests}. This
 test suite contains 42 instances dealing with a wide variety of regular
-expressions. Through cumulative transformations, we expanded it to 7,551
+expressions. Through cumulative transformations we expanded the 42 seeds to 7,551 unique
 instances. Finally, the \textit{Sanitizer} category is obtained from
@@
     \label{tbl:generated}
-    \begin{tabular}{|l|l|}
+    \begin{tabular}{|l|l|l|}
         \hline
-        \textbf{Name}             & \textbf{Instances have ...} \\ \hline
-        \textit{Concats}          & A right-heavy, deep tree of concats. \\ \hline
-        \textit{Concats-Balanced} & A balanced, deep tree of concats. \\ \hline
-        \textit{Concats-Extracts} & A single concat tree, and random character extractions. \\ \hline
-        \textit{Lengths}          & A single, large length constraint on a variable. \\ \hline
-        \textit{Lengths-Concats}  & Variables and their concats, each with fixed lengths. \\ \hline
-        \textit{Overlaps}         & A formula of the form A.X = X.B. \\ \hline
-        \textit{Regex}            & A test for regex membership of arbitrary complexity. \\ \hline
-        \textit{Many-Regexes}     & A test for membership in many random regexes. \\ \hline
-        \textit{Regex-Deep}       & A test for membership in a regex with many nested operators. \\ \hline
-        \textit{Regex-Pair}       & A test for membership in one regex, but not another. \\ \hline
-        \textit{Regex-Lengths}    & A test for membership in a regex, and a length constraint. \\ \hline
+        \textbf{Name}
+            & \textbf{Instances have ...}
+            & \textbf{Quantity}
+            \\ \hline
+        \textit{Concats}
+            & A right-heavy, deep tree of concats.
+            & 600
+            \\ \hline
+        \textit{Concats-Balanced}
+            & A balanced, deep tree of concats.
+            & 100
+            \\ \hline
+        \textit{Concats-Extracts}
+            & A single concat tree, and random character extractions.
+            & 600
+            \\ \hline
+        \textit{Lengths}
+            & A single, large length constraint on a variable.
+            & 1,000
+            \\ \hline
+        \textit{Lengths-Concats}
+            & Variables and their concats, each with fixed lengths.
+            & 500
+            \\ \hline
+        \textit{Overlaps}
+            & A formula of the form A.X = X.B.
+            & 100
+            \\ \hline
+        \textit{Regex}
+            & A test for regex membership of arbitrary complexity.
+            & 1,200
+            \\ \hline
+        \textit{Many-Regexes}
+            & A test for membership in many random regexes.
+            & 600
+            \\ \hline
+        \textit{Regex-Deep}
+            & A test for membership in a regex with many nested operators.
+            & 450
+            \\ \hline
+        \textit{Regex-Pair}
+            & A test for membership in one regex, but not another.
+            & 600
+            \\ \hline
+        \textit{Regex-Lengths}
+            & A test for membership in a regex, and a length constraint.
+            & 600
+            \\ \hline
+        \textit{Different-Prefix}
+            & An equality between two deep concats with different prefixes.
+            & 300
+            \\ \hline
     \end{tabular}
@@
         \textbf{Name}      & \textbf{Seed}                              & \textbf{Quantity} \\ \hline
-        \textit{Amazon}    & Two industrial regex membership instances & 472 \\ \hline
-        \textit{Regex}     & Z3str2 regular expression test suite      & 7,551 \\ \hline
-        \textit{Sanitizer} & 5 e-mail and IPv4 sanitiser examples      & 1,170 \\ \hline
+        \textit{Amazon}    & Two industrial regex membership instances. & 472 \\ \hline
+        \textit{Regex}     & Z3str2 regular expression test suite.      & 7,551 \\ \hline
+        \textit{Sanitizer} & 5 e-mail and IPv4 sanitiser examples.      & 1,170 \\ \hline
     \end{tabular}

### 2018-01-31 includes/appendix.tex
Finished Appendix Introduction.

\section{Appendix}

In this section, we will prove some of the guarantees that transformations
provide in \fuzzer{}.

We assume that the reader is familiar with SMT-LIB syntax. The transformations
work over boolean, integer, string literals and expressions, and regular
expressions.

We will make the folowing simplifications for our proofs:
\begin{itemize}
  \item
    Since many of the operators can be expressed in terms of other, our
    proofs will only consider a subset of the operators. In particular we will
    drop the following:
    \begin{itemize}
      \item \texttt{|} (boolean or)
      \item \texttt{=} for boolean expressions
      \item \texttt{<=}, \texttt{>}, \texttt{>=}
      \item \texttt{str.prefix}, \texttt{str.suffix}, \texttt{str.at}
      \item \texttt{str.contains}
      \item \texttt{re.range}
    \end{itemize}

  \item
    In the above, we assume that \texttt{str.at} is expressible using
    \texttt{substring} although the semantics slightly different when the index
    is out of bounds.

  \item
    We will assume that our program instances are a single assertion. Multiple
    assertions can be expressed by combining them using \texttt{and}.
\end{itemize}

\begin{definition}
  A \emph{model} is a mapping from boolean, integer, and string variables to
literals of the corresponding type.
\end{definition}

\begin{definition}
  A \emph{program} $P$ satisfies a model $m$ if $P$ evaluates to \texttt{true}
under the model $m$. The function $\eval (P)$ evaluates a program instance
under a model; the specific model used is left implicit.
\end{definition}

The proofs all follow a very similar structure. For each transformation
\texttt{Trans}, we show that a problem instance $P$ is satisfiable by a model $m$
if and only if $\texttt{Trans}(P)$ is satisfiable by $\texttt{Trans}(m)$, where
$\texttt{Trans}(M)$ is the transformation applied to all the constants in the
model $m$. In other words, we show that $\eval (P) = \eval (\texttt{Trans}(P))$.
This is proven using a straightforward induction on the structure of problem
instances.

\texttt{Multiply} has a weaker guarantee; it takes satisfiable problems to
satisfiable problems. For instance, $y<x<y+1$ is UNSAT, but multiplying by 2
transforms the problem into $y<x<y+2$ which is SAT. For \texttt{Multiply}, we
prove that if $\eval (P)$ is \texttt{true}, then, $\eval \texttt{Multiply}(P)$
is also \texttt{true}.

\subsection{Translate}
We now prove that translate transforms programs into equisatisfiable programs.

### 2018-01-31 includes/stringfuzz.tex
Reverting some changes addressed in review. Made tables look scientific. Made sure tables were no longer than line width. Added footnotes rather than column for Ifaz transformations.

@@
 solver. \fuzzer{} is composed of the following tools:
-
 \begin{description}
@@
 \end{description}
-
 We organized \fuzzer{} to be easily extended. As evidence of our success we note
@@
 \begin{table}[t]
+    \caption{\fuzzer{} built-in (a) generators and (b) transformers.}
+    \begin{subtable}{1\textwidth}
         \centering
@@
         \label{tbl:generators}
-    \begin{tabular}{|l|l|}
-        \hline
+        \begin{tabular}{ l l }
+            \toprule
             \textbf{Name}
-        & \textbf{Generate instances that have ...}
-        \\ \hline
+            & \textbf{Generates instances that have ...} \\
+            \midrule
             \textit{Concats}
-        & Long concats and optional random extracts.
-        \\ \hline
+            & Long concats and optional random extracts. \\
             \textit{Lengths}
-        & Many variables (and their concats) with length constraints.
-        \\ \hline
+            & Many variables (and their concats) with length constraints. \\
             \textit{Overlaps}
-        & An expression of the form A.X = X.B.
-        \\ \hline
+            & An expression of the form A.X = X.B. \\
             \textit{Equality}
-        & An equality among concats, each with variables or constants.
-        \\ \hline
+            & An equality among concats, each with variables or constants. \\
             \textit{Regex}
-        & Regexes of varying complexity.
-        \\ \hline
+            & Regexes of varying complexity. \\
             \textit{Random-Text}
-        & Random, likely syntactically \textit{in}valid text.
-        \\ \hline
+            & Random, likely syntactically \textit{in}valid text. \\
             \textit{Random-AST}
-        & Random, but semantically \textit{valid} text.
-        \\ \hline
+            & Random, but semantically \textit{valid} text. \\
+            \bottomrule
         \end{tabular}
-
+    \end{subtable}
+    \begin{subtable}{1\textwidth}
+        \centering
         \caption{\transformer{} built-in transformers.}
         \label{tbl:transformers}
-    \begin{tabular}{|l|l|l|}
-        \hline
+        \begin{tabular}{l l}
+            \toprule
             \textbf{Name}
-        & \textbf{The transformer ...}
-        & \textbf{Guarantee}\footnote{See Appendix for proofs and restrictions.}
-        \\ \hline
+            & \textbf{The transformer ...} \\
+            \midrule
             \textit{Fuzz}
-        & Randomly replaces literals and operators with similar ones.
-        & Well-formed
-        \\ \hline
+            & Replaces literals and operators with similar ones.\\
             \textit{Graft}
-        & For each sort, swaps a random non-leaf node with a leaf node.
-        & Well-formed
-        \\ \hline
-        \textit{Multiply}
-        & Multiplies each number by N, and repeats each character N times.
-        & Sat-sat
-        \\ \hline
+            & Randomly swaps non-leaf nodes with leaf nodes.\\
+            \textit{Multiply}\footnote{Satisfiable inputs 
+            will produce satisfiable outputs (see Appendix).}
+            & Multiplies integers and repeats strings by N.\\
             \textit{Nop}
-        & Does not transform (can translate between \smtfull{}).
-        & Equisat
-        \\ \hline
-        \textit{Reverse}
-        & Reverses all string literals and concat arguments.
-        & Equisat
-        \\ \hline
+            & Does nothing (can translate between \smtfull{}).\\
+            \textit{Reverse}\footnote{Input and output 
+            instances will be equisatisfiable (see Appendix).}
+            & Reverses all string literals and concat arguments.\\
             \textit{Rotate}
-        & Performs a syntax tree rotation on compatible operators.
-        & Well-formed
-        \\ \hline
-        \textit{Translate}
-        & Permutes the alphabet.
-        & Equisat
-        \\ \hline
+            & Rotates compatible nodes in syntax tree.\\
+            \textit{Translate}\footnotemark[4]
+            & Permutes the alphabet.\\
             \textit{Unprintable}
-        & Randomly replaces all characters in literals with unprintable ones.
-        & Equisat
-        \\ \hline
+            & Replaces characters in literals with unprintable ones.\\
+            \bottomrule
         \end{tabular}
+    \end{subtable}
 \end{table}
@@
 \subsubsection{Regex Fuzzing Capabilities}
-
 \fuzzer{} can generate
@@
 some can even guarantee equisatisfiability. Table~\ref{tbl:transformers} 
-lists the built-in transformers and these guarantees.
+lists the built-in transformers and notes these guarantees.
 

### 2018-01-31 includes/suites.tex
Reverting some changes addressed in review. Made tables look scientific. Made sure tables were no longer than line width. Added footnotes rather than column for Ifaz transformations.

@@
 \begin{table}[t]
+    \caption{Repository of \smtfull{} instances}
+    \begin{subtable}{1\textwidth}
         \centering
@@
         \label{tbl:generated}
-    \begin{tabular}{|l|l|l|}
-        \hline
+        \begin{tabular}{llr}
+            \toprule
             \textbf{Name}
-            & \textbf{Instances have ...}
+                & \textbf{Instances have a ...}
                 & \textbf{Quantity}
-            \\ \hline
+            \\
+            \midrule 
             \textit{Concats}
-            & A right-heavy, deep tree of concats.
-            & 600
-            \\ \hline
+                & Right-heavy, deep tree of concats.
+                & 600 \\
             \textit{Concats-Balanced}
-            & A balanced, deep tree of concats.
-            & 100
-            \\ \hline
+                & Balanced, deep tree of concats.
+                & 100 \\
             \textit{Concats-Extracts}
-            & A single concat tree, and random character extractions.
-            & 600
-            \\ \hline
+                & Single concat tree, with character extractions.
+                & 600 \\
             \textit{Lengths}
-            & A single, large length constraint on a variable.
-            & 1,000
-            \\ \hline
+                & Single, large length constraint on a variable.
+                & 1,000 \\
             \textit{Lengths-Concats}
-            & Variables and their concats, each with fixed lengths.
-            & 500
-            \\ \hline
+                & Tree of fixed-length concats of variables.
+                & 500 \\
             \textit{Overlaps}
-            & A formula of the form A.X = X.B.
-            & 100
-            \\ \hline
+                & Formula of the form A.X = X.B.
+                & 100 \\
             \textit{Regex}
-            & A test for regex membership of arbitrary complexity.
-            & 1,200
-            \\ \hline
+                & Complex regex membership test.
+                & 1,200 \\
             \textit{Many-Regexes}
-            & A test for membership in many random regexes.
-            & 600
-            \\ \hline
+                & Multiple random regex membership tests.
+                & 600 \\
             \textit{Regex-Deep}
-            & A test for membership in a regex with many nested operators.
-            & 450
-            \\ \hline
+                & Regex membership test with many nested operators.
+                & 450 \\
             \textit{Regex-Pair}
-            & A test for membership in one regex, but not another.
-            & 600
-            \\ \hline
+                & Test for membership in one regex, but not another.
+                & 600 \\
             \textit{Regex-Lengths}
-            & A test for membership in a regex, and a length constraint.
-            & 600
-            \\ \hline
+                & Regex membership test, and a length constraint.
+                & 600 \\
             \textit{Different-Prefix}
-            & An equality between two deep concats with different prefixes.
-            & 300
-            \\ \hline
+                & Equality of two deep concats with different prefixes.
+                & 300 \\
+            \bottomrule
         \end{tabular}
-\end{table}
+    \end{subtable}
 
-\begin{table}[t]
+    \begin{subtable}{1\textwidth}
         \centering
@@
         \label{tbl:transformed}
-    \begin{tabular}{|l|l|r|}
-        \hline
-        \textbf{Name}      & \textbf{Seed}                              & \textbf{Quantity} \\ \hline
-        \textit{Amazon}    & Two industrial regex membership instances. & 472 \\ \hline
-        \textit{Regex}     & Z3str2 regular expression test suite.      & 7,551 \\ \hline
-        \textit{Sanitizer} & 5 e-mail and IPv4 sanitiser examples.      & 1,170 \\ \hline
+        \begin{tabular}{llr}
+            \toprule
+            \textbf{Name}      & \textbf{Seed}                              & \textbf{Quantity} \\
+            \midrule
+            \textit{Amazon}    & Two industrial regex membership instances. & 472 \\
+            \textit{Regex}     & Z3str2 regular expression test suite.      & 7,551 \\
+            \textit{Sanitizer} & 5 e-mail and IPv4 sanitiser examples.      & 1,170 \\
+            \bottomrule
         \end{tabular}
+    \end{subtable}
 \end{table}

### 2018-02-01 includes/appendix.tex
Fixed logical issues.

@@
       \item \texttt{<=}, \texttt{>}, \texttt{>=}
-      \item \texttt{str.prefix}, \texttt{str.suffix}, \texttt{str.at}
+      \item \texttt{str.prefixof}, \texttt{str.suffixof}, \texttt{str.at}
       \item \texttt{str.contains}
@@
 The proofs all follow a very similar structure. For each transformation
-\texttt{Trans}, we show that a problem instance $P$ is satisfiable by a model $m$
-if and only if $\texttt{Trans}(P)$ is satisfiable by $\texttt{Trans}(m)$, where
-$\texttt{Trans}(M)$ is the transformation applied to all the constants in the
-model $m$. In other words, we show that $\eval (P) = \eval (\texttt{Trans}(P))$.
-This is proven using a straightforward induction on the structure of problem
-instances.
+\textit{Trans}, we show that a problem instance $P$ is satisfiable by a model $m$
+if and only if $\textit{Trans}(P)$ is satisfiable by $\textit{Trans}(m)$, where
+$\textit{Trans}(M)$ is the transformation applied to all the constants in the
+model $m$.
 
-\texttt{Multiply} has a weaker guarantee; it takes satisfiable problems to
-satisfiable problems. For instance, $y<x<y+1$ is UNSAT, but multiplying by 2
-transforms the problem into $y<x<y+2$ which is SAT. For \texttt{Multiply}, we
-prove that if $\eval (P)$ is \texttt{true}, then, $\eval \texttt{Multiply}(P)$
-is also \texttt{true}.
+To show the above, we show that for all expressions $e$, $\textit{Trans}(\eval
+(e)) = \eval (\textit{Trans}(e))$. This is proven using a straightforward
+induction on the structure of expressions. Since the transformations fix
+boolean constants, we have, $\textit{Trans}(\eval (P)) = \eval (P)$, and hence
+if the original problem is satisfiable then the transformed problem is also
+satisfiable.
+
+For transformations that have an inverse, such as \textit{Translate}
+and \textit{Reverse} this also shows that if the transformed problem is
+satisfiable, then the original problem is satisfiable. This proves that these
+transformations are equisat transformations. \textit{Multiply} does not have an
+inverse and hence it only guarantees to take satisfiable problems to satisfiable
+problems. This can be seen in the problem instance $y<x<y+1$ which is UNSAT, but
+multiplying by 2 transforms the problem into $y<x<y+2$ which is SAT.
 

### 2018-02-01 includes/appendix.tex
Finished Translate

@@
 
-In this section, we will prove some of the guarantees that transformations
-provide in \fuzzer{}.
+In this section, we will discuss how we proved equisatisfiability guarantees
+that transformations provide in \fuzzer{}.
 
@@
     \begin{itemize}
-      \item \texttt{|} (boolean or)
+      \item \texttt{||} (boolean or)
       \item \texttt{=} for boolean expressions
@@
       \item \texttt{str.contains}
-      \item \texttt{re.range}
+      \item \texttt{re.range}, \texttt{re.+}, \texttt{re.allchar}, \texttt{re.all}
     \end{itemize}
@@
 under the model $m$. The function $\eval (P)$ evaluates a program instance
-under a model; the specific model used is left implicit.
+under a model; the specific model used is left implicit as it is clear from
+context.
 \end{definition}
@@
 \subsection{Translate}
-We now prove that translate transforms programs into equisatisfiable programs.
+We now prove that translate transforms programs into equisatisfiable
+programs. From above, we only need to show that for every expression $e$,
+$\textit{Translate}(\eval (e)) = \eval (\textit{Translate}(e))$. For now, we
+assume that \textit{Translate} fixes the digit characters pointwise and we prove
+the stronger fact that $\textit{Translate}$ also fixes the digits pointwise in
+any string expression.
+
+It is clear that for literals $l$, $\textit{Translate}(\eval (l)) = \eval
+(\textit{Translate}(l))$. Then, assuming that the it holds for smaller
+expressions, we show that it holds larger expressions $e$ created using the
+constructs \texttt{and}, \texttt{=} (for strings and integers), \texttt{+},
+\texttt{-}, \texttt{*}, \texttt{str.len}, \texttt{str.indexof}, \texttt{str.++},
+and \texttt{str.substr}.
+
+For \texttt{str.in.re} we had to show that a string literals $s$, is a member of
+a regular expression $r$ if and only if $\textit{Translate}(s)$ is a member of
+$\textit{Translate}{r}$ by induction on regular expressions. For the inductive
+cases of \texttt{str.to.int}, and \texttt{str.from.int} we needed to use the
+fact that the digits were fixed pointwise.
+
+The restriction that \texttt{Translate} must fix the digit characters can be
+relaxed if we are translaing problem instances that do not use
+\texttt{str.to.int} or \texttt{str.from.int}.

### 2018-02-01 includes/appendix.tex
Finished Reverse.

@@
 
-The restriction that \texttt{Translate} must fix the digit characters can be
-relaxed if we are translaing problem instances that do not use
-\texttt{str.to.int} or \texttt{str.from.int}.
+The restriction that \textit{Translate} must fix the digit characters can be
+relaxed if we are translating problem instances that do not use
+\texttt{str.to.int} or \texttt{str.from.int}. Without these operators we can
+show $\textit{Translate}(\eval (e)) = \eval (\textit{Translate}(e))$ directly by
+induction without having to worry about fixing digits pointwise.
+
+\subsection{Reverse}
+\textit{Reverse} does not transform programs that use \texttt{str.replace},
+\texttt{str.indexof}, \texttt{str.to.int}, and \texttt{str.from.int}. These
+operators do not have a well-defined notion of a reverse. The required lemma is
+proved by induction on the rest of the operators similar to proof for
+\textit{Translate}.
+
+We end our discussion on \textit{Reverse} by nothing that although it disallowed
+\texttt{str.replace} only because it didn't have a natural notion of a reverse
+in the theory we were working with. If we expand our theory to also include an
+operator that replaces the last instance, we can transform problems that include
+\texttt{str.replace}.

### 2018-02-01 includes/appendix.tex
Finished Multiply.

@@
 \texttt{str.replace}.
+
+\subsection{Multiply}
+\textit{Multiply} does not transform programs that use \texttt{*},
+\texttt{str.indexof}, \texttt{str.to.int}, and \texttt{str.from.int}. These
+operators do not have a well-defined notion of a multiply. The required lemma is
+proved by induction on the rest of the operators similar to the above proofs.
+
+We disallow \texttt{*} for \textit{Multiply} because of problems instances such
+as \texttt{(= 10 (* 2 5))}. A naive \textit{Multiply} by $3$ would transform
+this satisfiable problem into the unsatisfiable \texttt{(= 30 (* 6 15))}.

### 2018-02-01 includes/stringfuzz.tex

@@
             \textit{Multiply}\footnote{Satisfiable inputs 
-            will produce satisfiable outputs (see Appendix).}
+            will produce satisfiable outputs (see Appendix for proof).}
             & Multiplies integers and repeats strings by N.\\
@@
             \textit{Reverse}\footnote{Input and output 
-            instances will be equisatisfiable (see Appendix).}
+            instances will be equisatisfiable (see Appendix for proof).}
             & Reverses all string literals and concat arguments.\\

### 2018-02-01 includes/experiment.tex
Adding new graphs. Fixing a few small issues.

@@
 Intel\textregistered{} Core\texttrademark{} i7-6700 CPU (3.40GHz).
-
 \begin{figure}[h]
@@
     \label{fig:cvc-hard}
-
-    \vspace{0.15in}
-
+    \bigskip
     \begin{subfigure}{.5\textwidth}
@@
     \begin{subfigure}{.5\textwidth}
-        \includegraphics[width=\textwidth]{data/graphs/concats-small.png}
-        \label{fig:concats-small}
-        \caption{Performance on \textit{Concats-Small}}
+        \includegraphics[width=\textwidth]{data/graphs/concats-big.png}
+        \label{fig:concats-big}
+        \caption{Performance on \textit{Concats-Big}}
     \end{subfigure}
@@
 
-\fuzzer also helped identify a number of performance-related issues and opportunities for
-new heuristics in \us{}. For example, by examining \us{}'s execution traces on the
+\fuzzer{} also helped identify a number of performance-related issues and
+opportunities for new heuristics in \us{}. For example, by examining \us{}'s
+execution traces on the
 instances in the \textit{Concats} suite we discovered a

### 2018-02-01 includes/appendix.tex

@@
 
-We will make the folowing simplifications for our proofs:
-\begin{itemize}
+To shorten our proofs, we will make the following simplifications:
+\begin{enumerate}
   \item
@@
       \item \texttt{<=}, \texttt{>}, \texttt{>=}
-      \item \texttt{str.prefixof}, \texttt{str.suffixof}, \texttt{str.at}
-      \item \texttt{str.contains}
+      \item \texttt{str.prefixof}, \texttt{str.suffixof}, \texttt{str.at}, \texttt{str.contains}
       \item \texttt{re.range}, \texttt{re.+}, \texttt{re.allchar}, \texttt{re.all}
@@
     In the above, we assume that \texttt{str.at} is expressible using
-    \texttt{substring} although the semantics slightly different when the index
-    is out of bounds.
+    \texttt{substring} although the semantics slightly differ when the index is
+    out of bounds.
 
@@
     assertions can be expressed by combining them using \texttt{and}.
-\end{itemize}
+\end{enumerate}
 
@@
 if and only if $\textit{Trans}(P)$ is satisfiable by $\textit{Trans}(m)$, where
-$\textit{Trans}(M)$ is the transformation applied to all the constants in the
+$\textit{Trans}(m)$ is the transformation applied to all the constants in the
 model $m$.
@@
 
-For transformations that have an inverse, such as \textit{Translate}
-and \textit{Reverse} this also shows that if the transformed problem is
-satisfiable, then the original problem is satisfiable. This proves that these
-transformations are equisat transformations. \textit{Multiply} does not have an
-inverse and hence it only guarantees to take satisfiable problems to satisfiable
-problems. This can be seen in the problem instance $y<x<y+1$ which is UNSAT, but
-multiplying by 2 transforms the problem into $y<x<y+2$ which is SAT.
+For transformations that have an inverse, such as \textit{Translate} and
+\textit{Reverse} this also shows that if the transformed problem is satisfiable,
+then the original problem is satisfiable, proving that they are equisat
+transformations. \textit{Multiply} does not have an inverse and hence it only
+guarantees to take satisfiable problems to satisfiable problems. This can be
+seen in the problem instance $y<x<y+1$ which is UNSAT, but multiplying by 2
+transforms the problem into $y<x<y+2$ which is SAT.
 
 \subsection{Translate}
-We now prove that translate transforms programs into equisatisfiable
+We now prove that \textit{Translate} transforms programs into equisatisfiable
 programs. From above, we only need to show that for every expression $e$,
@@
 We end our discussion on \textit{Reverse} by nothing that although it disallowed
-\texttt{str.replace} only because it didn't have a natural notion of a reverse
-in the theory we were working with. If we expand our theory to also include an
-operator that replaces the last instance, we can transform problems that include
-\texttt{str.replace}.
+\texttt{str.replace}, it only did so because it didn't have a natural notion of
+a reverse in the theory we were working with. If we expand our theory to also
+include an operator that replaces the last instance, we can transform problems
+that use \texttt{str.replace}.
 

### 2018-02-01 includes/suites.tex
adding total number
Adding new graphs. Fixing a few small issues.
Merging paragraphs.

@@
 evaluation.\footnote{The link to the repository will be added after
-double-blind review.}
-
-Table~\ref{tbl:generated} describes the string and regex instances that were
+double-blind review.} Table~\ref{tbl:generated} describes the string
+and regex instances that were
 generated by \generator{}. Table~\ref{tbl:transformed} lists benchmarks
@@
 \begin{table}[t]
-    \caption{Repository of \smtfull{} instances}
+    \caption{Repository of 15,843 \smtfull{} instances.}
     \begin{subtable}{1\textwidth}
@@
         \centering
-        \caption{Transformed instances generated by \transformer{}.}
+        \caption{\transformer{}-generated instances.}
         \label{tbl:transformed}
@@
             \textit{Regex}     & Z3str2 regular expression test suite.      & 7,551 \\
-            \textit{Sanitizer} & 5 e-mail and IPv4 sanitiser examples.      & 1,170 \\
+            \textit{Sanitizer} & Five e-mail and IPv4 sanitiser examples.   & 1,170 \\
             \bottomrule

### 2018-02-01 includes/introduction.tex
Reverting some changes addressed in review. Made tables look scientific. Made sure tables were no longer than line width. Added footnotes rather than column for Ifaz transformations.
Typo.

@@
 Fuzzing has been used to test all kinds of software
-including SAT solvers~\cite{fuzzsat}. Inspired by these fuzzers,
+including SAT solvers~\cite{fuzzsat}. Inspired by the utility of fuzzers,
 we introduce \fuzzer{} and describe its value
@@
         We compare the performance of \theSolvers{} on the
-        the \fuzzer{} suites \theSuites{} in Sect.~\ref{sec:data}. We
+        \fuzzer{} suites \theSuites{} in Sect.~\ref{sec:data}. We
         highlight these suites because they make some solvers perform poorly,

### 2018-02-01 includes/introduction.tex
Fixing sticking-out words.

@@
 respect to a variety of parameters, e.g., length of string constants,
-depth of concatenations (concats) and regular expressions, number of variables,
-number of length constraints, and many more.
+depth of concatenations (concats) and regular expressions (regexes),
+number of variables, number of length constraints, and many more.
 
@@
         In Sect.~\ref{sec:fuzzer}, we describe a modular fuzzer that can
-        transform and generate \smtfull{} string and regular
-        expression (regex) instances.\footnote{We assume basic
+        transform and generate \smtfull{} string and regex
+        instances.\footnote{We assume basic
         familiarity with string solvers and their input

### 2018-02-01 includes/appendix.tex
appendix

@@
 
-In this section, we will discuss how we proved equisatisfiability guarantees
-that transformations provide in \fuzzer{}.
-
-We assume that the reader is familiar with SMT-LIB syntax. The transformations
-work over boolean, integer, string literals and expressions, and regular
+In this section, we discuss how we proved equisatisfiability
+guarantees that transformations provide in \fuzzer{}. We assume that
+the reader is familiar with SMT-LIB syntax. The transformations work
+over boolean, integer, string literals and expressions, and regular
 expressions.
 
-To shorten our proofs, we will make the following simplifications:
+To shorten our proofs, we make the following simplifications:
 \begin{enumerate}
   \item
-    Since many of the operators can be expressed in terms of other, our
-    proofs will only consider a subset of the operators. In particular we will
-    drop the following:
+    Since many of the operators can be expressed in terms of others,
+    our proofs will only consider a subset of the operators. In
+    particular we drop the following:
     \begin{itemize}
@@
     out of bounds.
-
-  \item
-    We will assume that our program instances are a single assertion. Multiple
-    assertions can be expressed by combining them using \texttt{and}.
 \end{enumerate}
@@
   A \emph{model} is a mapping from boolean, integer, and string variables to
-literals of the corresponding type.
+elements in the domain of universe of the corresponding type.
 \end{definition}
@@
 \begin{definition}
-  A \emph{program} $P$ satisfies a model $m$ if $P$ evaluates to \texttt{true}
-under the model $m$. The function $\eval (P)$ evaluates a program instance
-under a model; the specific model used is left implicit as it is clear from
-context.
+  A \emph{formula} $P$ satisfies a model $m$ if $P$ evaluates to
+  \texttt{true} under the model $m$. The function $\eval (P)$
+  evaluates a formula under a model; the specific model used is left
+  implicit as it is clear from context.
 \end{definition}
 
-The proofs all follow a very similar structure. For each transformation
-\textit{Trans}, we show that a problem instance $P$ is satisfiable by a model $m$
-if and only if $\textit{Trans}(P)$ is satisfiable by $\textit{Trans}(m)$, where
-$\textit{Trans}(m)$ is the transformation applied to all the constants in the
-model $m$.
+The proofs all follow a very similar structure. For each
+transformation \textit{Trans}, we show that a formula $P$ is
+satisfiable by a model $m$ if and only if $\textit{Trans}(P)$ is
+satisfiable by $\textit{Trans}(m)$, where $\textit{Trans}(m)$ is the
+transformation applied to all the constants in the model $m$. (The
+exception here is the \textit{Multiply} operator as discussed below.)
 
-To show the above, we show that for all expressions $e$, $\textit{Trans}(\eval
-(e)) = \eval (\textit{Trans}(e))$. This is proven using a straightforward
-induction on the structure of expressions. Since the transformations fix
-boolean constants, we have, $\textit{Trans}(\eval (P)) = \eval (P)$, and hence
-if the original problem is satisfiable then the transformed problem is also
-satisfiable.
+To show the above, we show that for all expressions $e$,
+$\textit{Trans}(\eval (e)) = \eval (\textit{Trans}(e))$. This is
+proven using a straightforward induction on the structure of
+expressions. Since the transformations fix boolean constants, we have,
+$\textit{Trans}(\eval (P)) = \eval (P)$, and hence if the original
+problem is satisfiable so is the transformed problem.
 
-For transformations that have an inverse, such as \textit{Translate} and
-\textit{Reverse} this also shows that if the transformed problem is satisfiable,
-then the original problem is satisfiable, proving that they are equisat
-transformations. \textit{Multiply} does not have an inverse and hence it only
-guarantees to take satisfiable problems to satisfiable problems. This can be
-seen in the problem instance $y<x<y+1$ which is UNSAT, but multiplying by 2
+For transformations that have an inverse, such as \textit{Translate}
+and \textit{Reverse} this also shows that if the transformed problem
+is satisfiable, then the original problem is satisfiable, proving that
+they are equisat transformations. \textit{Multiply} (as defined here)
+does not have an inverse and hence it only guarantees to take
+satisfiable problems to satisfiable problems. This can be seen in the
+problem instance $y<x<y+1$ which is UNSAT, but multiplying by 2
 transforms the problem into $y<x<y+2$ which is SAT.
@@
 \subsection{Translate}
-We now prove that \textit{Translate} transforms programs into equisatisfiable
-programs. From above, we only need to show that for every expression $e$,
-$\textit{Translate}(\eval (e)) = \eval (\textit{Translate}(e))$. For now, we
-assume that \textit{Translate} fixes the digit characters pointwise and we prove
-the stronger fact that $\textit{Translate}$ also fixes the digits pointwise in
-any string expression.
+We now prove that \textit{Translate} transforms constraints into
+equisatisfiable constraints. From above, we only need to show that for
+every expression $e$, $\textit{Translate}(\eval (e)) = \eval
+(\textit{Translate}(e))$. For now, we assume that \textit{Translate}
+fixes the digits pointwise and we prove the stronger fact that
+$\textit{Translate}$ also fixes characters pointwise in any string
+expression. (I.e., $\textit{Translate}$ are bijections and further
+that digits are not mapped to any other character.)
 
-It is clear that for literals $l$, $\textit{Translate}(\eval (l)) = \eval
-(\textit{Translate}(l))$. Then, assuming that the it holds for smaller
-expressions, we show that it holds larger expressions $e$ created using the
-constructs \texttt{and}, \texttt{=} (for strings and integers), \texttt{+},
-\texttt{-}, \texttt{*}, \texttt{str.len}, \texttt{str.indexof}, \texttt{str.++},
-and \texttt{str.substr}.
+It is clear that for literals $l$, $\textit{Translate}(\eval (l)) =
+\eval (\textit{Translate}(l))$. Then, assuming that the it holds for
+smaller expressions, we show that it holds larger expressions $e$
+created using the constructs \texttt{and}, \texttt{=} (for strings and
+integers), \texttt{+}, \texttt{-}, \texttt{*}, \texttt{str.len},
+\texttt{str.indexof}, \texttt{str.++}, and \texttt{str.substr}.
 
-For \texttt{str.in.re} we had to show that a string literals $s$, is a member of
-a regular expression $r$ if and only if $\textit{Translate}(s)$ is a member of
-$\textit{Translate}{r}$ by induction on regular expressions. For the inductive
-cases of \texttt{str.to.int}, and \texttt{str.from.int} we needed to use the
+For \texttt{str.in.re} we had to show that a string literals $s$, is a
+member of a regular expression $r$ if and only if
+$\textit{Translate}(s)$ is a member of $\textit{Translate}{r}$ by
+induction on regular expressions. For the inductive cases of
+\texttt{str.to.int}, and \texttt{str.from.int} we needed to use the
 fact that the digits were fixed pointwise.
 
-The restriction that \textit{Translate} must fix the digit characters can be
-relaxed if we are translating problem instances that do not use
-\texttt{str.to.int} or \texttt{str.from.int}. Without these operators we can
-show $\textit{Translate}(\eval (e)) = \eval (\textit{Translate}(e))$ directly by
-induction without having to worry about fixing digits pointwise.
+The restriction that \textit{Translate} must fix the digit characters
+can be relaxed if we are translating problem instances that do not use
+\texttt{str.to.int} or \texttt{str.from.int}. Without these operators
+we can show $\textit{Translate}(\eval (e)) = \eval
+(\textit{Translate}(e))$ directly by induction without having to worry
+about fixing digits pointwise.
 
 \subsection{Reverse}
-\textit{Reverse} does not transform programs that use \texttt{str.replace},
-\texttt{str.indexof}, \texttt{str.to.int}, and \texttt{str.from.int}. These
-operators do not have a well-defined notion of a reverse. The required lemma is
-proved by induction on the rest of the operators similar to proof for
-\textit{Translate}.
+\textit{Reverse} does not transform constraints that use
+\texttt{str.replace}, \texttt{str.indexof}, \texttt{str.to.int}, and
+\texttt{str.from.int}. These operators do not have a well-defined
+notion of a reverse. The required lemma is proved by induction on the
+rest of the operators similar to proof for \textit{Translate}.
 
-We end our discussion on \textit{Reverse} by nothing that although it disallowed
-\texttt{str.replace}, it only did so because it didn't have a natural notion of
-a reverse in the theory we were working with. If we expand our theory to also
-include an operator that replaces the last instance, we can transform problems
-that use \texttt{str.replace}.
+We end our discussion on \textit{Reverse} by noting that although it
+disallowed \texttt{str.replace}, it only did so because it didn't have
+a natural notion of a reverse in the theory we were working with.
+%% If we expand our theory to also include an operator that replaces
+%% the last instance, we can transform problems that use
+%% \texttt{str.replace}.
 
 \subsection{Multiply}
-\textit{Multiply} does not transform programs that use \texttt{*},
-\texttt{str.indexof}, \texttt{str.to.int}, and \texttt{str.from.int}. These
-operators do not have a well-defined notion of a multiply. The required lemma is
-proved by induction on the rest of the operators similar to the above proofs.
+\textit{Multiply} does not transform constraints that use \texttt{*},
+\texttt{str.indexof}, \texttt{str.to.int}, and
+\texttt{str.from.int}. These operators do not have a well-defined
+notion of a multiply. The required lemma is proved by induction on the
+rest of the operators similar to the above proofs.
 
-We disallow \texttt{*} for \textit{Multiply} because of problems instances such
-as \texttt{(= 10 (* 2 5))}. A naive \textit{Multiply} by $3$ would transform
-this satisfiable problem into the unsatisfiable \texttt{(= 30 (* 6 15))}.
+We disallow \texttt{*} for \textit{Multiply} because of problems
+instances such as \texttt{(= 10 (* 2 5))}. A naive \textit{Multiply}
+by $3$ would transform this satisfiable problem into the unsatisfiable
+\texttt{(= 30 (* 6 15))}.

### 2018-02-01 includes/appendix.tex
appendix

@@
 
-In this section, we discuss how we proved equisatisfiability
-guarantees that transformations provide in \fuzzer{}. We assume that
-the reader is familiar with SMT-LIB syntax. The transformations work
-over boolean, integer, string literals and expressions, and regular
-expressions.
+In this section, we informally discuss how we established
+equisatisfiability guarantees that transformations provide in
+\fuzzer{}. We assume that the reader is familiar with SMT-LIB
+syntax. The transformations work over boolean, integer, string
+literals and expressions, and regular expressions.
 
@@
 equisatisfiable constraints. From above, we only need to show that for
-every expression $e$, $\textit{Translate}(\eval (e)) = \eval
-(\textit{Translate}(e))$. For now, we assume that \textit{Translate}
-fixes the digits pointwise and we prove the stronger fact that
-$\textit{Translate}$ also fixes characters pointwise in any string
-expression. (I.e., $\textit{Translate}$ are bijections and further
-that digits are not mapped to any other character.)
+every expression $e$, the following is true: $\textit{Translate}(\eval
+(e))$ = $\eval (\textit{Translate}(e))$. For now, we assume that
+\textit{Translate} fixes the digits pointwise and we prove the
+stronger fact that $\textit{Translate}$ also fixes characters
+pointwise in any string expression. (I.e., $\textit{Translate}$ are
+bijections and further that digits are not mapped to any other
+character.)
 
@@
 \texttt{str.to.int} or \texttt{str.from.int}. Without these operators
-we can show $\textit{Translate}(\eval (e)) = \eval
+we can show $\textit{Translate}(\eval (e))$ = $\eval
 (\textit{Translate}(e))$ directly by induction without having to worry

### 2018-02-01 includes/stringfuzz.tex
Fixing jarring command.
fix to grammar
Removing reference to ifaz's tech report.

--- 2018-01-31 includes/stringfuzz.tex
@@
     \textit{Translate} and \textit{Reverse} also preserve
-    satisfiability under certain conditions~\cite{ifaz}.
+    satisfiability under certain conditions.
     \item[\texttt{stringstats}] \hfill \\
@@
 
-\subsubsection{Regex Fuzzing Capabilities}
+\subsubsection{Regex Generating Capabilities}
 \fuzzer{} can generate
-and transform instances with regular expression constraints. For example, the
-command \texttt{stringfuzzg regex} invokes the regex instance
+and transform instances with regular expression constraints. For example,
+\texttt{stringfuzzg regex} invokes the regex
 generator and produces an instance of the form:
@@
 
+\subsubsection{Equisatisfiable String Transformations}
 \fuzzer{} can also transform problem instances.

### 2018-02-01 includes/appendix.tex
appendix
Appendix: || changed to or
Typos.

@@
 In this section, we informally discuss how we established
-equisatisfiability guarantees that transformations provide in
+equisatisfiability guarantees regarding the transformations provided in
 \fuzzer{}. We assume that the reader is familiar with SMT-LIB
@@
     \begin{itemize}
-      \item \texttt{||} (boolean or)
+      \item \texttt{or} (boolean or)
       \item \texttt{=} for boolean expressions
@@
   A \emph{model} is a mapping from boolean, integer, and string variables to
-elements in the domain of universe of the corresponding type.
+elements in the domain of the universe of the corresponding type.
 \end{definition}

### 2018-02-01 includes/appendix.tex
Typos

@@
 stronger fact that $\textit{Translate}$ also fixes characters
-pointwise in any string expression. (I.e., $\textit{Translate}$ are
-bijections and further that digits are not mapped to any other
-character.)
+pointwise in any string expression. (i.e., in bijections of character
+sets used by $\textit{Translate}$ the digits are not mapped to any
+other character.)
 
@@
 member of a regular expression $r$ if and only if
-$\textit{Translate}(s)$ is a member of $\textit{Translate}{r}$ by
+$\textit{Translate}(s)$ is a member of $\textit{Translate}(r)$ by
 induction on regular expressions. For the inductive cases of

### 2018-02-01 includes/introduction.tex
typo
introduction

@@
 In recent years, many algorithms for solving string constraints have
-been developed and implemented in SMT solvers such as Norn~\cite{norn},
-CVC4~\cite{cvc4}, and Z3 (e.g., Z3str2~\cite{z3str2} and Z3str3~\cite{z3str3}).
-To validate and benchmark these solvers, their developers have relied on
-hand-crafted input suites~\cite{cvc4-tests,z3str3-tests,z3str2-tests} or
-real-world examples from a limited set of industrial
+been developed and implemented in SMT solvers such as
+Norn~\cite{norn}, CVC4~\cite{cvc4}, and Z3 (e.g., Z3str2~\cite{z3str2}
+and Z3str3~\cite{z3str3}).  To validate and benchmark these solvers,
+their developers have relied on hand-crafted input
+suites~\cite{cvc4-tests,z3str3-tests,z3str2-tests} or real-world
+examples from a limited set of industrial
 applications~\cite{kaluza,kausler}. These test suites have helped
 developers identify implementation defects and develop more
-sophisticated solving heuristics. Unfortunately, as solvers grow
-fixed benchmarks remain stagnant, leaving increasing functionality untested.
-As such, there is an acute need for a more robust, inexpensive, and automatic way
-of generating benchmarks to test
-the correctness and performance of SMT solvers.
+sophisticated solving heuristics. Unfortunately, as more features are
+added to solvers, these benchmarks often remain stagnant, leaving
+increasing functionality untested.  As such, there is an acute need
+for a more robust, inexpensive, and automatic way of generating
+benchmarks to test the correctness and performance of SMT solvers.
 
-Fuzzing has been used to test all kinds of software
-including SAT solvers~\cite{fuzzsat}. Inspired by the utility of fuzzers,
-we introduce \fuzzer{} and describe its value
-as an exploratory testing tool. We demonstrate its efficacy
-by presenting limitations it helped discover in
-leading string solvers. To the best of our knowledge, \fuzzer{} is the
-only tool aimed at automatic generation of string constraints. \fuzzer{} can
-be used to mutate or transform existing benchmarks, as well as
-randomly generate structured instances. These instances can be scaled with
-respect to a variety of parameters, e.g., length of string constants,
-depth of concatenations (concats) and regular expressions (regexes),
-number of variables, number of length constraints, and many more.
+Fuzzing has been used to test all kinds of software including SAT
+solvers~\cite{fuzzsat}. Inspired by the utility of fuzzers, we
+introduce \fuzzer{} and describe its value as an exploratory testing
+tool. We demonstrate its efficacy by presenting limitations it helped
+discover in leading string solvers. To the best of our knowledge,
+\fuzzer{} is the only tool aimed at automatic generation of string
+constraints. \fuzzer{} can be used to mutate or transform existing
+benchmarks, as well as randomly generate structured instances. These
+instances can be scaled with respect to a variety of parameters, e.g.,
+length of string constants, depth of concatenations (concats) and
+regular expressions (regexes), number of variables, number of length
+constraints, and many more.
 

### 2018-02-01 includes/appendix.tex
Typos in appendix.
appendix

@@
 In this section, we informally discuss how we established
-equisatisfiability guarantees regarding the transformations provided in
-\fuzzer{}. We assume that the reader is familiar with SMT-LIB
-syntax. The transformations work over boolean, integer, string
-literals and expressions, and regular expressions.
+equisatisfiability guarantees regarding the transformations provided
+in \fuzzer{}.  The transformations work over boolean, integer, string
+literals and expressions, and regular expressions. To shorten our
+proofs, we make the following simplifications:
 
-To shorten our proofs, we make the following simplifications:
 \begin{enumerate}
@@
     our proofs will only consider a subset of the operators. In
-    particular we drop the following:
+    particular we drop the following from consideration:
     \begin{itemize}

### 2018-02-01 artifact/bin/csv2json.py
Adding code for the artifact.

@@ -1,0 +1,59 @@
+#!/usr/bin/env python3
+
+import sys
+import json
+import csv
+import argparse
+
+DESCRIPTION = '''
+Read CSV file on stdin and print it as JSON on stdout.
+
+example:
+  x,y      [
+  0,0  ->    {"y": 0, "x": 0},
+  1,2        {"y": 2, "x": 1}
+           ]
+'''
+
+def str2value(v):
+    try:
+        return int(v)
+    except ValueError as e:
+        pass
+    try:
+        return float(v)
+    except ValueError as e:
+        pass
+    return v
+
+def make_dict(keys, values):
+    values = map(str2value, values)
+    return dict(zip(keys, values))
+
+def main():
+
+    # create arg parser
+    parser = argparse.ArgumentParser(
+        description     = DESCRIPTION,
+        formatter_class = argparse.RawTextHelpFormatter
+    )
+
+    # parse args
+    args = parser.parse_args()
+
+    # create CSV reader for all lines
+    # NOTE:
+    #      csv.reader returns a generator of rows, which are string tuples
+    rows = csv.reader(sys.stdin, delimiter=',', quotechar='\'')
+
+    # interpret the first tuple as the header
+    header = next(rows)
+
+    # create a list of dicts by mapping the header to each row
+    dicts = [make_dict(header, row) for row in rows]
+
+    # dump the list as json
+    print(json.dumps(dicts))
+
+if __name__ == '__main__':
+    main()

### 2018-02-01 artifact/bin/json2cactus.py

@@ -1,0 +1,282 @@
+#!/usr/bin/env python3
+
+import sys
+import os
+import tempfile
+import json
+import argparse
+import copy
+import re
+
+from collections import OrderedDict
+
+# constants
+LABEL_FONTSIZE    = 10
+TITLE_FONTSIZE    = 14
+SUBTITLE_FONTSIZE = 10
+AXIS_MIN          = 0
+
+NO_TITLE_BY_DEFAULT = False
+
+X_LABEL = 'problems solved'
+Y_LABEL = 'time (s)'
+
+DESCRIPTION = '''
+Make a cactus plot from given datasets and print it in PNG format on stdout.
+
+notes:
+  no check is made to see if the datasets have the same problems
+  the datasets are not required to be of the same size
+
+dataset format:
+  [
+      {
+          "problem": "/path/to/problem",
+          "result":  "sat"|"unsat"|"unknown"|"timeout"|"error",
+          "solver":  "solver name",
+          "elapsed": 1.0 // time it took, as a float
+      },
+      ...
+  ]
+'''
+
+SYMBOLS = [
+    6, # <
+    7, # ^
+    4, # >
+    5, # v
+    8, # x
+]
+
+COLOURS = [
+    'blue',
+    'green',
+    'orange',
+    'red',
+    'cyan',
+    'magenta',
+    'yellow',
+    'black',
+    'lightblue',
+    'gray',
+]
+
+MARKERS = list(zip(SYMBOLS + SYMBOLS, COLOURS))
+
+SOLVER_MARKER_MAP = {
+    r'cvc4':   (6, 'blue'),
+    r'z3str3': (7, 'green'),
+    r'z3str2': (4, 'orange'),
+}
+
+# globals
+args_timeout = 0.0
+
+# helpers
+def next_marker():
+    return MARKERS.pop(0)
+
+def get_marker(given_name):
+    for reserved_name_pattern, marker in SOLVER_MARKER_MAP.items():
+        if re.match(reserved_name_pattern, given_name):
+            SOLVER_MARKER_MAP.pop(reserved_name_pattern)
+            return marker
+    return next_marker()
+
+def plottable(row):
+    return (
+        row['result'] == 'sat' or
+        row['result'] == 'unsat' or
+        row['result'] == 'unknown' or
+        row['result'] == 'timeout'
+    )
+
+def unknown2timeout(row):
+
+    # interpret 'unknown' rows as if they were 'timeout' rows
+    if row['result'] == 'unknown':
+
[…]

### 2018-02-01 artifact/bin/json2compare.py

@@ -1,0 +1,216 @@
+#!/usr/bin/env python3
+
+import sys
+import os
+import tempfile
+import json
+import argparse
+
+# constants
+LABEL_FONTSIZE     = 10
+TITLE_FONTSIZE     = 14
+SUBTITLE_FONTSIZE  = 10
+DEFAULT_AXIS_LIMIT = 10
+AXIS_MIN           = 0
+
+NO_TITLE_BY_DEFAULT = False
+
+DESCRIPTION = '''
+Make a comparison plot from two datasets and print it in PNG format on stdout.
+
+dataset format:
+  [
+      {
+          "problem": "/path/to/problem",
+          "result":  "sat"|"unsat"|"unknown"|"timeout"|"error",
+          "solver":  "solver name",
+          "elapsed": 1.0 // time it took, as a float
+      },
+      ...
+  ]
+'''
+
+MARKERS = [
+    4,
+    5,
+    6,
+    7,
+    8
+]
+
+# helpers
+def plottable(row):
+    return (
+        row['result'] == 'sat' or
+        row['result'] == 'unsat' or
+        row['result'] == 'timeout'
+    )
+
+def get_solver_name(dataset):
+    return dataset[0]['solver']
+
+def get_i(data, i):
+    return [d[i] for d in data]
+
+def data2png(x, x_name, y, y_name, title):
+
+    # configure plot library to use SVG
+    import matplotlib
+    matplotlib.use('svg')
+    import matplotlib.pyplot as pyplot
+
+    # set title
+    if title is not None:
+        pyplot.suptitle(title + '\n', fontsize=TITLE_FONTSIZE)
+
+    # combine data
+    points     = []
+    num_better = 0
+    num_worse  = 0
+    for x_row, y_row in zip(x, y):
+
+        x_value = x_row['elapsed']
+        y_value = y_row['elapsed']
+
+        # only look at plottable runs
+        if plottable(x_row) and plottable(y_row):
+
+            # record performance
+            if x_value <= y_value:
+                num_better += 1
+            else:
+                num_worse += 1
+
+            # save the point
+            points.append((x_row['elapsed'], y_row['elapsed']))
+
+    # get total number of runs and build subtitle
+    num_total = num_better + num_worse
+    if num_total > 0:
+
+        # measure performance
+        subtitle = '''{x} was better {b}/{t} times ({bp:.2f} %), worse {w}/{t} times ({wp:.2f} %)'''.format(
+            x  = x_name,
+            b  = num_better,
[…]

### 2018-02-01 artifact/bin/json2csv.py

@@ -1,0 +1,47 @@
+#!/usr/bin/env python3
+
+import sys
+import json
+import argparse
+
+DESCRIPTION = '''
+Read JSON object list on stdin and print it as CSV on stdout.
+
+notes:
+  the first object's keys are used for the CSV header
+
+example:
+  [                        x,y
+    {"y": 0, "x": 0},  ->  0,0
+    {"y": 2, "x": 1}       1,2
+  ]
+'''
+
+def main():
+
+    # create arg parser
+    parser = argparse.ArgumentParser(
+        description     = DESCRIPTION,
+        formatter_class = argparse.RawTextHelpFormatter
+    )
+
+    # parse args
+    args = parser.parse_args()
+
+    # read in JSON list
+    dicts = json.loads(sys.stdin.read())
+
+    # get objects keys
+    # NOTE:
+    #      it's assumed that all objects have the same keys
+    keys = sorted(dicts[0].keys())
+
+    # print keys as CSV header
+    print(','.join(keys))
+
+    # print each object's values as CSV rows
+    for d in dicts:
+        print(','.join(map(str, [d[k] for k in keys])))
+
+if __name__ == '__main__':
+    main()

### 2018-02-01 artifact/bin/make_instances.py

@@ -1,0 +1,198 @@
+import random
+import sys
+import os
+
+from stringfuzz.constants import SMT_20_STRING, SMT_25_STRING
+from stringfuzz.generators import concats, overlaps, lengths, regex, equality
+from stringfuzz.generator import generate_file
+from stringfuzz.smt import smt_string_logic
+
+RANDOM_SEED = 0
+
+def make_suite(root, name, generator, start, num_levels, increment, per_level, **kwargs):
+    suite_dir_path = os.path.join(root, name)
+    print(suite_dir_path)
+
+    # create the directory
+    try:
+        os.makedirs(suite_dir_path)
+
+    # if it exists, ignore the error
+    except OSError as e:
+        pass
+
+    # generate all the problems
+    x = start
+    for i in range(num_levels):
+
+        # generate as many problems at each level as necessary
+        for y in range(per_level):
+
+            # get file paths
+            file_name = '{name}-{x:0>5}-{y}'.format(name=name, x=x, y=y)
+            smt25_file_path = os.path.join(suite_dir_path, file_name) + '.smt25'
+            smt20_file_path = os.path.join(suite_dir_path, file_name) + '.smt20'
+
+            # format args
+            for key, value in kwargs.items():
+                if isinstance(value, str) and '{x}' in value:
+                    kwargs[key] = int(value.format(x=x))
+
+            # generate problem
+            ast = generator(**kwargs)
+            ast = [smt_string_logic()] + ast
+
+            # write it out in two languages
+            generate_file(ast, SMT_25_STRING, smt25_file_path)
+            generate_file(ast, SMT_20_STRING, smt20_file_path)
+
+        # increment arg
+        x += increment
+
+def main():
+    root_dir = sys.argv[1]
+
+    # seed RNG
+    random.seed(RANDOM_SEED)
+
+    # create problem suites
+    make_suite(root_dir, 'lengths-short', lengths, 1, 50, 5, 2,
+        max_length        = '{x}',
+        min_length        = 0,
+        num_concats       = 0,
+        num_vars          = 30,
+        random_relations  = False
+    )
+    make_suite(root_dir, 'lengths-long', lengths, 1, 50, 100, 2,
+        max_length        = '{x}',
+        min_length        = 0,
+        num_concats       = 0,
+        num_vars          = 30,
+        random_relations  = False
+    )
+    make_suite(root_dir, 'lengths-concats', lengths, 1, 50, 1, 2,
[…]

### 2018-02-01 artifact/bin/timesolver.py

@@ -1,0 +1,230 @@
+#!/usr/bin/env python3
+
+import os
+import sys
+import json
+import subprocess
+import signal
+import datetime
+import argparse
+
+from collections import namedtuple
+
+# constants
+SAT_RESULT     = 'sat'
+UNSAT_RESULT   = 'unsat'
+UNKNOWN_RESULT = 'unknown'
+TIMEOUT_RESULT = 'timeout'
+ERROR_RESULT   = 'error'
+
+DEFAULT_TIMEOUT = 15.0
+
+CSV  = 'csv'
+JSON = 'json'
+
+OUTPUT_FORMATS = [CSV, JSON]
+
+# data
+Result = namedtuple('Result', ('solver', 'problem', 'elapsed', 'result', 'command'))
+
+# helpers
+def output2result(output):
+    # NOTE:
+    #      it's important to check for unsat first, since sat
+    #      is a substring of unsat
+    if 'UNSAT' in output or 'unsat' in output:
+        return UNSAT_RESULT
+    if 'SAT' in output or 'sat' in output:
+        return SAT_RESULT
+    if 'UNKNOWN' in output or 'unknown' in output:
+        return UNKNOWN_RESULT
+
+    print('couldn\'t parse output: \'' + output + '\'', file=sys.stderr)
+    return ERROR_RESULT
+
+def run_problem(solver, invocation, problem, timeout, verbose, debug):
+
+    # pass the problem to the command
+    command = invocation + problem
+
+    # print command that will be run
+    if verbose is True or debug is True:
+        print('RUNNING:', repr(command), file=sys.stderr)
+
+    # get start time
+    start = datetime.datetime.now().timestamp()
+
+    # run command
+    process = subprocess.Popen(
+        command,
+        shell      = True,
+        stdout     = subprocess.PIPE,
+        stderr     = subprocess.PIPE,
+        preexec_fn = os.setsid
+    )
+
+    # wait for it to complete
+    try:
+        process.wait(timeout=timeout)
+
+    # if it times out ...
+    except subprocess.TimeoutExpired as e:
+
+        # kill it
+        print('TIMED OUT:', repr(command), '... killing', process.pid, file=sys.stderr)
+        os.killpg(os.getpgid(process.pid), signal.SIGINT)
+
+        # set timeout result
+        elapsed = timeout
+        result  = TIMEOUT_RESULT
+
+    # if it completes in time ...
+    else:
+
+        # measure run time
[…]

### 2018-03-31 cav2018/rebuttal.txt
Adding review and rebuttal to repo.

Review1

Q1: ”Were you able to find any bugs in existing solvers with your tool? [...] Is the tool more suitable for performance analysis, rather than correctness testing?”

A1: StringFuzz can be used for both, but is more suitable for performance analysis. We used it as such when working with Z3str3, Z3str2 and CVC4. For example it helped find actual implementation bugs (e.g. commits 6308636 to 3865c45, and 66bc68f to 7b536e9) in previous versions of Z3str3, and also helped find performance issues in Z3str3 and CVC4.

Q2: “I am not sure how useful the modified industrial sets are... Is it intended for correctness testing or performance tuning? Solvers are expected to take advantage of structural properties [...] Destroying such properties might lead the solvers astray, but I am not sure if one can learn anything from such experiments...”

A2: Modified industrial instances were useful for performance analysis. Fuzzing them with StringFuzz allowed us to maintain instance structure in some respects, but also make the instance extremal in others. For example in Amazon instances we replaced literals with unprintable characters, and scaled the lengths of literals, without changing any other aspect of the instance.

Review2

Q1: “[...] I would expect some form of evolutionary algorithms [...]”

A1: Thank you for this suggestion! In fact, we’re already working on augmenting StringFuzz with an evolutionary approach.

Q2: “Further, the description of some of the generators and transformers is very brief [...]”

A2: This was intentional, to save space. We provide in-depth generator descriptions/examples on the StringFuzz website[1].

Q3: “[...] both the entire framework as well as the generators and transforms seem to be still relatively simple.”

A3: We respectfully disagree with this point. Some of the transformations are satisfiability-preserving and are fairly complex.

Q4: “Page 3, [...] (a) there should be no indentation there, (b) RegEx is not defined.”

A4: We will fix the indentation and define RegEx.

Q5: “Page 4, [...] (a) two cases of wrong indentation, (b) not clear enough: in particular, can concatenation appear lower in the terms too?”

A5: Indeed, concatenation can only appear on the top level. We will clarify this, and also fix the indentation.

Review3

Q1: “It would be nice to consider extending the fuzzing to cover other theories as well, such as bit-vectors.”

A1: We agree, and are currently extending the fuzzer to support the entire SMT-LIB 2.6 standard.

Review4

Q1: ”Section 3 describes a suite of over 10000 string benchmarks. Section 4 promises an experimental evaluation, but presents results on only a tiny fraction of these benchmarks, including none of the industrial benchmarks. There is no explanation as to why so few results are reported. I think that the paper is pretty weak without a full set of experimental results on the new benchmarks”

A1: We indeed performed experiments on all the suites. We presented the suites that showed interesting behaviour, and for brevity omitted the ones that showed all solvers performing similarly. We currently present all the data and graphs on our website[2]. We will add them to the Appendix.

Q2: “do the tools generally agree on an input syntax?”

A2: They generally agree, but we had to account for two versions of the string syntax. StringFuzz supports both using the --language-in and --language-out flags.

Q3: “The subsection on Regex generating capabilities is rather informal and quite unclear.  Are you mixing SMT-LIB syntax with regular expression syntax at the meta-level?  It's very confusing.”

A3: It is indeed confusing. We will rewrite the example in SMT-LIB syntax only.

Q4: “You mention two data sets, "Concats-Big" and "Concats-Extracts-Small", both of which are not listed in Table 2a.  Where do these data sets come from?”

A4: We grouped Concats-Big and Concats-Small under Concats (and same for Concats-Extracts) in the table for brevity, but that is indeed unclear. We will add them in the table explicitly.

Review5

Q1: “I ran this script [...] but did not see any errors after 30 minutes or so. It would have been nice to say if the StringFuzz tool was able to find any crashing inputs for the string solvers.”

A1: StringFuzz has many options (visible with the --help flag) that may speed up the time to crash. For example “stringfuzzg --random random-ast --meaningful --num-vars 2 --num-asserts 10 --depth 3“ will yield more challenging instances. We discovered errors in Z3str3 with similar scripts, but have not fully explored other solvers.

Review6

Q1: “They didn't manage to build the solver Z3str2 on the VM.”

A1: Indeed, we failed to do it in time for the submission. We apologise.

Q2: “I was surprised to see the checksum for the machine image.”

A2: Indeed, the checksum is invalid when it’s on the VM. It was transferred by mistake. We apologise for the oversight.

[1] http://stringfuzz.dmitryblotsky.com/problems/
[2] http://stringfuzz.dmitryblotsky.com/results/latest/

### 2018-04-07 includes/introduction.tex
Need to push contributions to second page, but other than that it is getting there

@@
 
-\subsubsection{Contributions}
-
+\subsubsection{Contributions}\footnote{All source code, problem suites, and supplementary material
+referenced in this paper are available at the \fuzzer{} website \cite{website}.}
 \begin{enumerate}
@@
         transform and generate \smtfull{} string and regex
-        instances.\footnote{We assume basic
-        familiarity with string solvers and their input
-        language.} Scaling inputs (e.g., long string constants,
+        instances. Scaling inputs (e.g., long string constants,
         deep concatenations) are particularly useful in identifying asymptotic

### 2018-04-07 includes/stringfuzz.tex
Need to push contributions to second page, but other than that it is getting there

@@
 \linesPerX{} lines of code to create a transformer. \fuzzer{} can either be
-installed from source, or from the Python PIP package
-repository.\footnote{The link to the source code will be added after double-blind review.}
+installed from source, or from the Python PIP package repository.
 
@@
             & Randomly swaps non-leaf nodes with leaf nodes.\\
-            \textit{Multiply}\footnote{Satisfiable inputs
-            will produce satisfiable outputs (see Appendix).}
+            \textit{Multiply}\footnote{Can guarantee satisfiable output instances 
+            from satisfiable input instances \cite{website}.}
             & Multiplies integers and repeats strings by N.\\
@@
             & Does nothing (can translate between \smtfull{}).\\
-            \textit{Reverse}\footnote{Input and output
-            instances will be equisatisfiable (see Appendix).}
+            \textit{Reverse}\footnote{Can guarantee input and output
+            instances will be equisatisfiable \cite{website}.}
             & Reverses all string literals and concat arguments.\\
@@
             & Rotates compatible nodes in syntax tree.\\
-            \textit{Translate}\footnotemark[4]
+            \textit{Translate}\footnotemark[6]
             & Permutes the alphabet.\\
@@
 
-where $R_i \in RegEx$, and $Min, Max \in Int$. More simply, the
+\noindent where $R_i \in RegEx$, and $Min, Max \in Int$. More simply, the
 instance is a set of one or more regex constraints on a single
@@
 
-and each $T_i$ is a recursive term of the form:
+\noindent and each $T_i$ is a recursive term of the form:
 \begin{align*}
@@
 
-where $j$ is the specified depth of recursion. Terms at depth 0 are
+\noindent where $j$ is the specified depth of recursion. Terms at depth 0 are
 regex constants. Informally, this form describes a concatenation of

### 2018-04-07 includes/suites.tex
fixed small mistake
Adjusting numbers.
Need to push contributions to second page, but other than that it is getting there

@@
 with \fuzzer{}, and on which we conducted our experimental
-evaluation.\footnote{The link to the repository will be added after
-double-blind review.} Table~\ref{tbl:generated} describes the string
+evaluation. Table~\ref{tbl:generated} describes the string
 and regex instances that were
@@
 Every transformed instance is named according to its
-seed and the transformations it undertook. For example, input
+seed and the transformations it undertook. For example,
 \texttt{z3-regex-1-fuzz-graft.smt2} was transformed by applying
@@
 \begin{table}[t]
-    \caption{Repository of 15,843 \smtfull{} instances.}
+    \caption{Repository of 10,258 \smtfull{} instances.}
     \begin{subtable}{1\textwidth}
@@
                 & Right-heavy, deep tree of concats.
-                & 600 \\
+                & 120 \\
             \textit{Concats-Balanced}
@@
                 & Single concat tree, with character extractions.
-                & 600 \\
+                & 120 \\
             \textit{Lengths}
                 & Single, large length constraint on a variable.
-                & 1,000 \\
+                & 200 \\
             \textit{Lengths-Concats}
                 & Tree of fixed-length concats of variables.
-                & 500 \\
+                & 100 \\
             \textit{Overlaps}
                 & Formula of the form A.X = X.B.
-                & 100 \\
+                & 80 \\
             \textit{Regex}
                 & Complex regex membership test.
-                & 1,200 \\
+                & 120 \\
             \textit{Many-Regexes}
                 & Multiple random regex membership tests.
-                & 600 \\
+                & 40 \\
             \textit{Regex-Deep}
                 & Regex membership test with many nested operators.
-                & 450 \\
+                & 45 \\
             \textit{Regex-Pair}
                 & Test for membership in one regex, but not another.
-                & 600 \\
+                & 40 \\
             \textit{Regex-Lengths}
                 & Regex membership test, and a length constraint.
-                & 600 \\
+                & 40 \\
             \textit{Different-Prefix}
                 & Equality of two deep concats with different prefixes.
-                & 300 \\
+                & 60 \\
             \bottomrule

### 2018-04-11 includes/experiment.tex
Fixing sticking-out words.
Applying recommendations from rebuttal.

@@
 We generated several problem instance suites with \fuzzer{} that made one
-solver perform poorly, but not others. These suites are
-\theSuites{}. Fig.~\ref{fig:cvc-hard} shows the suites that were
+solver perform poorly, but not others.\footnote{Only the
+results that made one solver perform poorly and not others are presented, but
+results for all \fuzzer{} suites are available on the \fuzzer{} website.}
+They are \theSuites{}. Fig.~\ref{fig:cvc-hard} shows the suites that were
 uniquely difficult for \cvc{}. Fig.~\ref{fig:z3str3-hard} shows the

### 2018-04-11 includes/stringfuzz.tex
Applying recommendations from rebuttal.

@@
             & Randomly swaps non-leaf nodes with leaf nodes.\\
-            \textit{Multiply}\footnote{Can guarantee satisfiable output instances 
-            from satisfiable input instances \cite{website}.}
+            \textit{Multiply}\footnote{Can guarantee satisfiable output
+            instances from satisfiable input instances \cite{website}.}
             & Multiplies integers and repeats strings by N.\\
@@
 \subsubsection{Regex Generating Capabilities}
-\fuzzer{} can generate
-and transform instances with regular expression constraints. For example,
-\texttt{stringfuzzg regex} invokes the regex
-generator and produces an instance of the form:
+
+\fuzzer{} can generate and transform instances with regex
+constraints. For example, the command
+``\texttt{stringfuzzg regex -r 2 -d 1 -t 1 -M 3 -X 10}'' produces this instance:
+{\small\begin{verbatim}        (set-logic QF_S)
+        (declare-fun var0 () String)
+        (assert (str.in.re var0 (re.+ (str.to.re "R5"))))
+        (assert (str.in.re var0 (re.+ (str.to.re "!PC"))))
+        (assert (<= 3 (str.len var0)))
+        (assert (<= (str.len var0) 10))
+        (check-sat)\end{verbatim}}
+
+Each instance is a set of one or more regex constraints on a single
+variable, with optional maximum and minimum length constraints. Each regex
+constraint is a concatenation (\texttt{re.++} in SMT-LIB string syntax)
+of regex terms:
 \begin{align*}
-    & \texttt{(assert (str.in.re X}\; R_0\; \texttt{))} \\
-    & \texttt{(assert (str.in.re X}\; R_n\; \texttt{))}* \\
-    & \texttt{(assert (<= Min (str.len X)))}? \\
-    & \texttt{(assert (<= (str.len X)) Max)}?
+    & \texttt{(re.++ T1 (re.++ T2} \; ... \; \texttt{(re.++ Tn-1 Tn )))}
 \end{align*}
 
-\noindent where $R_i \in RegEx$, and $Min, Max \in Int$. More simply, the
-instance is a set of one or more regex constraints on a single
-variable, with optional maximum and minimum length constraints. The
-regex constraints $R$ are each of the form:
+\noindent and each term is recursively defined as any one of: repetition
+(\texttt{re.*}), Kleene star (\texttt{re.+}), union (\texttt{re.union}), or a
+character literal. Nested operators are nested up to a specified depth of
+recursion. Terms at depth 0 are always regex constants.
+
+Intuitively, each instance is a concatenation of regex terms, where each
+term is a random nested regex operator with random arguments
+(up to a specified depth) terminating in a regex literal.
+Below are three example regexes (in regex syntax, not in the SMT-LIB language)
+of depth 2 that can be produced by this scheme:
 \begin{align*}
-    & \texttt{(re.++}\; T_0\; \texttt{(re.++}\; T_1\;
-    \texttt{...}\; \texttt{(re.++}\; T_{n-1}\; T_n\; \texttt{))}
-\end{align*}
-
-\noindent and each $T_i$ is a recursive term of the form:
-\begin{align*}
-    & \texttt{(re.*}\; T_{i_j}\; \texttt{) | (re.+}\; T_{i_j}\;
-    \texttt{) | (re.union}\; T_{i_{j_1}}\; T_{i_{j_2}}\; \texttt{)}
-\end{align*}
-
-\noindent where $j$ is the specified depth of recursion. Terms at depth 0 are
-regex constants. Informally, this form describes a concatenation of
-regex terms, where each term is a random nested regex operator (chosen from
-regex Kleene star, repetition, and union), up to a specified depth,
-terminating in a regex literal. Below are three example regex instances
-(separated by spaces) of depth 2 produced by this scheme:
-\begin{align*}
-    & ((\texttt{a}|\texttt{b})|(\texttt{cc})+)\quad\quad
-    ((\texttt{ddd})*)+\quad\quad ((\texttt{ee})+|(\texttt{fff})*)
+    & ((\texttt{a}|\texttt{b})|(\texttt{cc})+)\quad\quad\quad
+    ((\texttt{ddd})*)+\quad\quad\quad ((\texttt{ee})+|(\texttt{fff})*)
 \end{align*}

### 2018-04-11 includes/suites.tex
Applying recommendations from rebuttal.

@@
             \midrule
-            \textit{Concats}
+            \textit{Concats-\{Small,Big\}}
                 & Right-heavy, deep tree of concats.
@@
                 & 100 \\
-            \textit{Concats-Extracts}
+            \textit{Concats-Extracts-\{Small,Big\}}
                 & Single concat tree, with character extractions.
                 & 120 \\
-            \textit{Lengths}
+            \textit{Lengths-\{Long,Short\}}
                 & Single, large length constraint on a variable.
@@
                 & 100 \\
-            \textit{Overlaps}
+            \textit{Overlaps-\{Small,Big\}}
                 & Formula of the form A.X = X.B.
                 & 80 \\
-            \textit{Regex}
+            \textit{Regex-\{Small,Big\}}
                 & Complex regex membership test.

### 2018-04-12 includes/stringfuzz.tex
Removing redundant text.

@@
 
-\noindent and each term is recursively defined as any one of: repetition
+\noindent and each term \texttt{Ti} is recursively defined as any one of: repetition
 (\texttt{re.*}), Kleene star (\texttt{re.+}), union (\texttt{re.union}), or a
-character literal. Nested operators are nested up to a specified depth of
-recursion. Terms at depth 0 are always regex constants.
-
-Intuitively, each instance is a concatenation of regex terms, where each
-term is a random nested regex operator with random arguments
-(up to a specified depth) terminating in a regex literal.
-Below are three example regexes (in regex syntax, not in the SMT-LIB language)
-of depth 2 that can be produced by this scheme:
+character literal. Nested operators are nested up to a specified (using
+the \texttt{--depth} flag) depth of recursion. Terms at depth 0 are
+regex constants. Below are 3 example regexes (in regex, not SMT-LIB, syntax)
+of depth 2 that can be produced this way:
 \begin{align*}

### 2018-04-16 includes/stringfuzz.tex
Removing some redundant text to make space for shifted Contributions title.

@@
 \end{description}
-We organized \fuzzer{} to be easily extended. As evidence of our success we note
-that while the whole project
-contains \linesInFuzzer{} lines of code, it takes an average of
-\linesPerX{} lines of code to create a transformer. \fuzzer{} can either be
-installed from source, or from the Python PIP package repository.
+We organized \fuzzer{} to be easily extended. To show this, we note that while
+the whole project contains \linesInFuzzer{} lines of code, it takes an
+average of \linesPerX{} lines of code to create a transformer. \fuzzer{} can
+be installed from source, or from the Python PIP package repository.
 

### 2018-04-16 includes/suites.tex
Removing some redundant text to make space for shifted Contributions title.

@@
 with \fuzzer{}, and on which we conducted our experimental
-evaluation. Table~\ref{tbl:generated} describes the string
-and regex instances that were
-generated by \generator{}. Table~\ref{tbl:transformed} lists benchmarks
+evaluation. Table~\ref{tbl:generated} lists instances that were
+generated by \generator{}. Table~\ref{tbl:transformed} lists instances
 derived from existing seed instances by iteratively applying \transformer{}.
@@
 supplied by our industrial collaborators. The \textit{Regex} category is
-seeded by the \usOld{} regular expression test suite~\cite{z3str2-tests}. This
-test suite contains 42 instances dealing with a wide variety of regular
-expressions. Through cumulative transformations we expanded the 42 seeds to 7,551 unique
-instances. Finally, the \textit{Sanitizer} category is obtained from
-five industrial e-mail address and IPv4 sanitizers.
+seeded by the \usOld{} regex test suite~\cite{z3str2-tests}, which contains
+42 instances. Through cumulative transformations we expanded the
+42 seeds to 7,551 unique instances. Finally, the \textit{Sanitizer} category
+is obtained from five industrial e-mail address and IPv4 sanitizers.
 

### 2018-04-16 includes/experiment.tex
Adjusting some text and adding a reference.

--- 2018-02-01 includes/experiment.tex
@@
 We generated several problem instance suites with \fuzzer{} that made one
-solver perform poorly, but not others. These suites are
-\theSuites{}. Fig.~\ref{fig:cvc-hard} shows the suites that were
+solver perform poorly, but not others.\footnote{Only the
+results that made one solver perform poorly and not others are presented, but
+results for all \fuzzer{} suites are available on the \fuzzer{}
+website\cite{website}.}
+They are \theSuites{}. Fig.~\ref{fig:cvc-hard} shows the suites that were
 uniquely difficult for \cvc{}. Fig.~\ref{fig:z3str3-hard} shows the
@@
 as a result of testing with the \fuzzer{} scaling suites
-\textit{Lengths} and \textit{Concats}.
+\textit{Lengths-Long} and \textit{Concats-Big}.
 
@@
 execution traces on the
-instances in the \textit{Concats} suite we discovered a
+instances in the \textit{Concats-Big} suite we discovered a
 potential new heuristic. In particular, \us{} does not

### 2018-04-16 includes/introduction.tex
Removing redundant text.
Removing some redundant text to make space for shifted Contributions title.
Adjusting some text and adding a reference.

@@
 
-\subsubsection{Contributions}\footnote{All source code, problem suites, and supplementary material
-referenced in this paper are available at the \fuzzer{} website \cite{website}.}
+\newpage
+\subsubsection{Contributions}\footnote{All source code, problem suites, and
+supplementary material referenced in this paper are available at the
+\fuzzer{} website \cite{website}.}
 \begin{enumerate}
